### 2012-05-08 paper_turk.tex
first commit

\documentclass{article}

%\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
\usepackage{graphicx}

\graphicspath{{images/}}

\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
%\setlength{\topmargin}{-0.4in}
\setlength{\textheight}{9in}

\title{Turk Experiments for Visual Inference}
\author{Mahbubul Majumder, Heike Hofmann, Dianne Cook\\
        Department of Statistics, Iowa State University}

\begin{document}

\maketitle

\begin {abstract}

It has been found that the visual test, which does not have distributional assumptions, has the power comparable to the classical
tests \cite{Majumder:2011}. To examine the power of visual statistical inference we recruited human subjects from Amazon Mechanical Turk \cite{turk} for evaluating lineups \cite{buja:2009, Majumder:2011}. The Turk website is designed to recruit workers for simple and easy tasks. Even though the task of evaluating lineups is easy, the technical design of the experiment is complex and the tools available to design this from Turk website is just too simple. In this paper we present how we deal with this trouble and conduct our experiment.

\end {abstract}

\section{Introduction}

Amazon Mechanical Turk is a very good resource for recruiting reliable survey participants for visual experiments. The web site is very nice and reliable to collect data. But to design an experiment using their web interface is a pain and often a very time consuming work. On top of that their technical support is not in the expected level. So, to run the turk experiment we felt the necessity for a well customized web site.

\section{Website to Run the Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments. We use  Amazon Mechanical Turk web site to recruit the participants and direct them to our web site to actually participate in the survey. This has allow us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site.

\section{Experimental Design} \label{sec:exp_design}

\subsection{Selecting Parameter of Simulation Experiment} The first consideration for a simulation experiment is to fix the parameters of the model of interest. The very first consideration is the sample size. Other parameters depends on the model of interest. For example we have fixed the parameters in our first Amazon Mechanical Turk experiment as shown in table \ref{tbl:experiment_params}.

\subsection{Sample size estimation} For a given proportion $p$ we want to have margin of error (ME) to be 0.1. Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$ Now from the theoretical power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the sample size required for that specific combinations of parameter. We collect data such that each of the parameter combinations in the table \ref{tbl:experiment_params} has approximately the estimated sample size that we calculated here.

\subsection{Procedure to simulate plots for survey} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from model of interest for prespecified parameters. We call this data set observed data. While the effect of the natural variability of this data set could be contolled by taking the replication of few samples, it is desirable to study whether we can reduce this variability alternatively. The main reason is to minimize the cost. To make sure that the observed data set truly represents model of interest we are considering three approaches. One is Kolomogorov test statistic approach and the other two approaches are quantiles of p values and closeness of estimated parameters to the true parameters. These three approaches are discussed below.\\

{\bf Kolomogorov test statistic approach:} In this approach we simulate 1000 data sets and obtain Kolmogorov test statistic for each set of data as below. $$D_n=\sup_x |F_n(x)-F(x)|$$ where $F_n(x)=\frac1n \sum_{i=1}^n I_{X_i\le x}$ be the empirical distribution function of fitted residuals, $I_{X_i\le x}$ be the indicator function equal to 1 if $X_i\le x$ and equal to 0 otherwise and $F(x)$ be the cumulative function of normal with mean zero(0) and variance $\sigma^2$. We then keep the data set that has minimum value for Kolmogorov test statistic.  For replication purpose we can generate three observed data sets in similar way.\\

{\bf Quantiles of p-value approach:} With any data set we generate there is a p-value associated with testing $H_0: \beta=0$. In this approach we generate 1000 data sets from the model of interest and obtain p-values associated with $H_0: \beta=0$ for each data set after fitting the same model. Then we construct blocks of p-value such as (0.0-$q_{33}$), ($q_{33}$-$q_{66}$), ($q_{66}$-1) where $q_i$ is the $i$th percentile in the distribution of the p-values. We then randomly select three data sets that have corresponding p-values in the above quantile range. As an example the distribution  of p-values in 1000 simulated data sets for $n$=300, $\beta$=3 and $\sigma$=12 is shown in figure \ref{fig:dist_pvalue}.  Notice that if we like to have three replications of plots, we will have observed data sets with smaller p-values as the distribution is highly right skewed as well as the 33th and 66th percentiles of p-values are 0.0101 and 0.077 respectively. So, another option may be to take the mid points of those quantile ranges and pick the data sets that have those p-values.\\

\begin{figure}[hbtp]
   \centering
       \scalebox{.3}{\includegraphics{dist_pvalue.pdf}}
       \caption{Distribution of p-values for $n$=300, $\beta$=3 and $\sigma$=12.}
       \label{fig:dist_pvalue}
\end{figure}

{\bf Closeness of estimated parameters:} When we simulate a data set from the model of interest and again fit the same model with the data set we do not get the parameters estimates same as what we fixed while simulation. It depends on what the standard errors of the parameter estimates are. In our experimental setting we some times have very different estimates for small parameter values(such as one may get estimated value of 0.5 for true $\beta=3$). In this approach we pick the data set that shows most close estimates of parameters compared to true parameter values.\\

All of these three approaches discussed above has some problems. Kolmogorov method does not necessarily make sure that estimated parameters are close to the true parameters. On the other hand closeness of estimated parameters does not make sure that p value is small enough when we should reject the null hypothesis. Only the quantiles approach seems reasonable as it has much control over p-values and it gives similar data sets that has closest parameter estimates. So we used the quantiles of p-value approach in chapter \ref{ch:regression} to obtain three replicated sample of observed data sets for a particular parameter settings.\\

\subsection{Data collection} To collect the survey data we developed a web site that shows a plot to an individual and get feedback from that individual. Each individual is asked to provide feedback for at least 10 different plots. The 10 plots that are shown to an individual are randomly chosen with probability proportional to the number of responses required (the sample size) for that plot.

The information collected from each individual is shown in table \ref{tbl:data_info}. Data received from each individual are automatically saved in a secured mysql server maintained by the department of statistics, Iowa state university.

\begin{table}[hbtp]
\caption{Information Collected from Each Individual}
\centering 
\begin{tabular}{lp{8cm}} 
\hline
Information &  Description \\ %[0.5ex] % inserts table %heading 
\hline
Identification & Nick name or any ID to determine the responses of an Individual \\
Response number & The number of the plot on the lineup plot which the individual thinks the most different than other 19 plots.\\ 
Reason of of choice & Reason why the individual chooses the plot \\
Confidence level & Confidence level of individual choice \\ 
Age group& The age group where the individual belongs \\
Education & The highest level of education completed \\
Gender & Male or female \\
Geographic Location & This information is collected through the ip address of the individual computer \\ 
Time taken & Time taken for each feed back\\
\hline
\end{tabular}
\label{tbl:data_info}
\end{table}

\section{Payment of Turk Worker} Turk workers are usually small payee workers. There several issues related to the payment of their effort. These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.

\subsection{Wage Rate for the Turkers}Amazon Mechanical Turk suggest that each worker gets \$6/hour as wage. Thus we need to estimate how much time a tusk may take to complete and based on that we have to specify the payment for each task. Our experience indicates that a better payment lures more serious workers who usually provide cleaner data which is more reliable. We may study this issue while we do multiple turk experiments.

\subsection{Accepting or Rejecting Payments for Turk Evaluation} In our design we keep a test lineup plot which is very easy to evaluate. The general criteria may be to reject payment when workers do not get that easy test lineup plot. Our experience suggest that there are workers who did not get that test plot but their overall success rate is very high. So depending on only one criteria the payment should not be made. These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.

\section{What do people pick, $R^2$ or p-value?} What do people pick in a lineup plot, p-value or $R^2$? To address this issue we obtain the approximate theoretical relationship between $R^2$ and the power of the classical hypothesis test. Suppose we want to test the significance of the slope ( i.e.,  $H_0: \beta=0$ against $\beta \ne 0$) of a continuous covariate $X$ in  a simple linear regression model setting. Also consider $X \sim N(0,1)$. For a sample of size $n$ this gives us 
\begin{eqnarray*}
Y_i-\bar{Y}& = & \beta_0+\beta_1X_i+\epsilon_i - \beta_0 - \beta_1 \bar{X}- \bar{\epsilon} \\
          & = & \beta_1(X_i-\bar{X})+(\epsilon_i-\bar{\epsilon})
\end{eqnarray*}
Now 
\begin{eqnarray*}
X_i-\bar{X}& = & X_i - \frac1n (X_1 + X_2 + ... + X_i + .....+ X_n) \\
          & = & X_i - \frac1n X_i - \frac1n \sum_{j \neq i}{X_j}\\
          & = & (1-\frac1n)X_i - \frac1n \sum_{j \neq i}{X_j}
\end{eqnarray*}

Thus we have 
\begin{eqnarray*}
E(X_i-\bar{X})^2 & = & (1-\frac1n)EX_i^2 - \left( \frac1n \right )^2 (n-1) EX_j^2 \\
                 & = & (1-\frac1n)^2+ \frac{n-1}{n^2}\\
                 & = & \frac{n-1}{n}
\end{eqnarray*}

Similarly we have

\begin{eqnarray*}
E(\epsilon_i-\bar{\epsilon})^2 & = & (1-\frac1n)E\epsilon_i^2 - \left( \frac1n \right )^2 (n-1) E\epsilon_j^2 \\
                 & = & \left((1-\frac1n)^2+ \frac{n-1}{n^2} \right) \sigma^2 \\
                 & = & \frac{n-1}{n}\sigma^2
\end{eqnarray*}
Finally we have expected total sum of square (SST) as
\begin{eqnarray*}
E\sum_i{(Y_i-\bar{Y})^2} & = & \sum_i E(Y_i-\bar{Y})^2=\sum_i \left [ \beta_1^2 E(X_i-\bar{X})^2 + E(\epsilon_i-\bar{\epsilon})^2 \right] \\
                 & = & \sum_i\left[ \beta_1^2 \frac{n-1}{n}+  \sigma^2 \frac{n-1}{n}\right]\\
                 & = & (n-1)(\sigma^2+\beta_1^2)
\end{eqnarray*}

We know $E(MSE|X) = \sigma^2$ or $E(SSE/n-2)|X = \sigma^2$ which gives the expected residual or error sum of square as $$E \sum_i (Y_i-\hat Y_i)^2=(n-2)\sigma^2$$
Thus we have the expected regression sum of squares $SSR =  (n-1)(\sigma^2+\beta_1^2) - (n-2)\sigma^2 = (n-1) \beta_1^2+\sigma^2$ This gives $$R^2=\frac{(n-1) \beta_1^2+\sigma^2}{ (n-1)(\sigma^2+\beta_1^2)}$$

\begin{figure}[hbtp]
   \centering
       \scalebox{.3}{\includegraphics{scatter_plot_beta_4.pdf}}
       \caption{Scatter plot of data generated for $\beta_0$=6, $\beta_1$=4, sample size $n =300$ and $\sigma = 12$. $R^2$ for this data was obtained as 0.1309 showing that the model could not successfully explain the variation in $Y$. But notice in figure \ref{fig:power_rsq} that power for $\beta$=4 is almost 1. So, Can we conclude that $R^2$ does not have any effect in deciding whether $H_0: \beta_1=0$ should be rejected or not?}
       \label{fig:plot_beta_4}
\end{figure}

\begin{figure}[hbtp]
   \centering
       \scalebox{.35}{\includegraphics{power_300_12.pdf}}
       \caption{Power curve and $R^2$ values for sample size $n =300$ and $\sigma = 12$. Notice that for a small value of $R^2$ (0.1) the power is almost 1.}
       \label{fig:power_rsq}
\end{figure}

\begin{figure}[hbtp]
   \centering
       \scalebox{.35}{\includegraphics{rsquare_contour.pdf}}
       \scalebox{.35}{\includegraphics{rsquare_beta_sigma.pdf}}
       \caption{Contour and surface plots of $R^2$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
       \label{fig:contour_rsq}
\end{figure}

\begin{figure}[hbtp]
   \centering
       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines.pdf}}
       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines1.pdf}}       
       \caption{Relationship of $R^2$ with $\sigma$ and $\beta$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
       \label{fig:rsq}
\end{figure}

\section{Performance} In this section we intend to analyze the performance of the experiments we did using Amazon Mechanical turk. We have feed back data for the similar plots from both turk workers as well as from the people who regularly participates in the graphics group meeting of our department. We consider later participants as more knowledgeable and trained in seeing pattern in statistical plots. We can use these data to evaluate the performance of the general participants from around the world.

\section{Selection Bias} Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did. In this section we intend to analyze to what extent this selection bias has occurred and how we can adjust for this.

\bibliographystyle{plain}
\bibliography{references}

\end{document}

\documentclass{article}
\usepackage{times}
\usepackage{natbib}
%\usepackage{multicol}
%\RequirePackage{natbib}
\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
%\usepackage[dvips]{graphics}

\graphicspath{{images/}}
\usepackage{color}
\newcommand{\blue}[1]{{\color{blue} #1}}
\newcommand{\red}[1]{{\color{red} #1}}

\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.4in}
\setlength{\textheight}{9in}
\evensidemargin \oddsidemargin

\newtheorem{thm}{Theorem}[section]
\newtheorem{dfn}{Definition}[section]
\newtheorem{cor}{Corollary}[thm]
\newtheorem{con}{Conjecture}[thm]
%\setlength{\parindent}{0in}   % for no indent

%\topmargin -0.10in   % when making pdf
%\textheight 9.15in  % when making pdf

\setlength\parindent{0pt}

% Article top matter
\title{Turk Experiments for Visual Inference}
\author{Mahbubul Majumder, Heike Hofmann, Dianne Cook\\
        Department of Statistics, Iowa State University}
%\date{\today}  %\today is replaced with the current date

\begin{document}

\maketitle

\begin {abstract}

It has been found that the visual test, which does not have
distributional assumptions, has the power comparable to the classical
tests [3]. To examine the power of visual statistical inference we
recruited human subjects from Amazon Mechanical Turk \cite{turk}  for
evaluating lineups[1,2]. The Turk website is designed to recruit
workers for simple and easy tasks. Even though the task of evaluating
lineups is easy, the technical design of the experiment is complex and
the tools available to design this from Turk website is just too
simple. In this paper we present how we deal with this trouble and to
conduct our experiment.

Statistical graphics play a crucial role in exploratory data analysis, model checking and diagnosis. Until recently there were no formal visual methods in place for determining statistical significance of findings. This changed, when \citet{buja:2009} conceptually introduced two protocols for formal tests of visual findings. In this paper we take this a step further by comparing the lineup protocol \citep{buja:2009} against classical statistical testing  of the significance of regression model parameters. A human subjects experiment is conducted using simulated data to provide controlled conditions. Results suggest that the lineup protocol provides results equivalent to the uniformly most powerful (UMP) test and for some scenarios yields better power than the UMP test.
\end {abstract}

%\begin{multicols}{2}
%\twocolumn

\section{Introduction}

Any statistical analysis must include some statistical graphics. For exploratory data analysis, statistical graphics play an invaluable role in model checking and diagnostics. Even though we have established mathematical procedures to obtain various statistics, we need to support the results by also producing the relevant plots.

\bibliographystyle{plain}
%\bibliographystyle{asa}
\bibliography{references}

\end{documents}

Any statistical analysis must include some statistical graphics. For exploratory data analysis, statistical graphics play an invaluable role in model checking and diagnostics. Even though we have established mathematical procedures to obtain various statistics, we need to support the results by also producing the relevant plots.

The scientific foundation of graphical methods for data analysis is well established by \cite{cleveland:1984}. In recent years we have seen several major advances in statistical graphics. Modern computing systems like R and SAS ease the production of high quality statistical plots. A grammar of graphics introduced by \cite{wilkinson:1999} presents a structured way to generate specific graphics from data and define connections between disparate types of plots.  \cite{hadley:2009} has implemented a revised version of the grammar of graphics in R, in the package {\tt ggplot2}.   \blue {Graham Wills has implemented the grammar in SPSS, but I'm not sure how to cite this.}

\citet{buja:2009}, following from \cite{gelman:2004}, proposed two protocols that allow the testing of discoveries made from statistical graphics. This work represents a major advance for graphics, because it bridges the gulf between classical statistical inference procedures and exploratory data analysis.

In this paper we compare graphical inference to classical statistical inference for a set of regression type example. We also present results of a human-subject study assessing the performance of individuals on lineup plots \citep{buja:2009} for testing significance of regression parameters.

Section \ref{sec:visual_test} describes the basic ideas of visual inference, Section \ref{sec:regression} applies these ideas to the case of inference for regression analysis. In Section \ref{sec:simulation} we outline the setup for the human-subject study and  and present results.

\begin{table*}[hbtp]
\caption{Comparison of visual inference with existing inference technique}
\centering 
\begin{tabular}{llll} 
\hline
  & Mathematical Inference &  Visual Inference \\ %[0.5ex] % inserts table %heading 
\hline
  Hypothesis & $H_0: \beta=0$ vs $H_1: \beta \ne 0$& $H_0: \beta=0$ vs $H_1: \beta \ne 0$\\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

 Test statistic & $T(y)=\frac{\hat{\beta}}{se(\hat{\beta})}$ & $T(y)=$ \begin{minipage}[h]{1cm} \begin{center} \scalebox{0.45}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} \\

 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

 Null Distribution & $f_{T(y)}(t); $\begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.55}{\includegraphics{stat_mathematical_test.pdf}} \end{center} \end{minipage} & $f_{T(y)}(t); $ \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.19}{\includegraphics{test_category.pdf}} \end{center} \end{minipage} \\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
 Reject $H_0$ if & observed $T$ is extreme & observed plot is identifiable \\
\hline 
\end{tabular}
\label{tbl:compare}
\end{table*}

\section{Visual Statistical Inference} \label{sec:visual_test} 
Visual tests are non-parametric tests of the form $H_0$: the data plot is visually not distinguishable from a null plot vs $H_1$: the data plot is visually distinguishable from a plot generated consistently with $H_0$.

Power of a plot and $p$-value have been derived in Buja and Wickham as ...

for this paper, we want to place the parametric inference of a regression setting into the framework of visual testing:

This section outlines the concepts of visual inference in comparison to the procedures of classical statistical inference. Table \ref{tbl:compare} (derived from \citet{buja:2009}) gives a summarized overview of this comparison.

Let $\theta$ be a population parameter of interest, with $\theta \in \Theta$, the parameter space. 
Any null hypothesis $H_0$ then partitions the parameter space into $\Theta_0$ and $\Theta_0^c$, with $H_0: \theta \in \Theta_0$ versus $H_1: \theta \in \Theta_0^c$.

\blue{Similarly, for any test, we have a rejection region $R$ and, complementary to that, $R^c$,  that partition the space of the test statistic, which is usually a subspace of the real numbers.}
%\subsection{Visual Statistic}

For visual inference, the statistic is -- unlike in the classical hypothesis test -- not a single value, but a graphical representation of the data chosen to display the strength of the parameter of interest, $\theta$. When the alternative hypothesis is true, it is expected that the plot of the observed data, the test statistic, will have visible feature(s) consistent with $\theta \in \Theta_0^c$, and that visual artifacts will not distinguish the test statistic as different when $H_1$ is not true. We will call a plot with this property a {\it visual statistic} for $\theta$. More formally,

\blue{

\begin{dfn} \label{dfn:test}
A \textit{visual test (statistic)} $T_\theta$ is defined as the grammar \citep{wilkinson:1999} of the plot,  consisting of type and specification of aesthetics necessary for complete reproducibility.
\end{dfn}
}

\begin{dfn}\label{dfn:lplot}
A lineup plot is a layout of $m$ visual statistics, consisting of 
\begin{itemize}\itemsep-3pt
\item $m-1$ plots simulated from the model specified by $H_0$  (null plots) and 
\item the test statistic produced by plotting the observed data, possibly arising from $H_1$.
\end{itemize}
\end{dfn}

The $(m-1)$ null plots can be considered to be samples drawn from the sampling distribution of the test statistic assuming that the null hypothesis is true.
If $H_1$ is true, \blue{we expect this to be reflected as a feature in the test statistic, i.e. the plot of the data, that makes it visually distinguishable from the null plots.}
{\em If the test statistic cannot be identified} in the lineup the conclusion is to {\em not reject the null hypothesis.}  A careful visual inspection follows, and the observer is asked to point out the plot most different from the lineup.

Since the lineup plot consists of $m$ plots, the probability of choosing any one of them is $1/m$. Thus we have type-I error probability of $1/m$.

%The lineup plot can be evaluated by one or more individuals. When a single individual identifies the observed graph in the lineup plot we report a $p$-value of at most $1/m$, otherwise the $p$-value is at least $1-\frac 1m$.

 %Notice that when $N=1$, this $p$-value is $\frac1m$.

%\subsection{Power}

For two different visual test statistics of the same observed data, the one  is better, in which a specific pattern is more easily distinguishable to the observer. This should be reflected in the power of the test. We can assess power therefore both empirically based on experimental data and through theoretical considerations.

%Next, we will develop power theoretically and then relate it to the empirical results.
\blue{We will first theoretically define and  derive the power of  a visual test in the setting of a parametric hypothesis test, i.e. we assume a test  of $H_0: \theta = 0$ vs $H_1: \theta \neq 0$ for some real valued parameter vector $\theta$. In a next step we will then relate the theoretical results to our empirical findings.}

\begin{dfn} \label{dfn:power}
For a lineup of $m$ plots the power of \blue{a visual test} $T$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
    \begin{equation*}
      \text{Power}_T(\theta)= 
        \begin{cases} 
              \text{Type-I error}=\frac1m & \text{if $\theta \in \Theta_0$,} \\
              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
        \end{cases}
    \end{equation*}
\end{dfn}

For any single observer, the power of a visual test has a lower limit of $\frac1m$ since the probability that an observer will randomly pick the test statistic under $H_0$ is $\frac1m$.

When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. This leads us to obtain the probability 
\begin{equation}\label{eqn:pvalue}
Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} \left(\frac{1}{m}\right)^k\left(1-\frac 1m\right)^{(K-k)}}
\end{equation}
where $u$ is the observed number of successful evaluations. We use this probability to  define the $p$-value for visual test $T_{\theta}$ as follows:
\begin{dfn} \label{dfn:pval}
The $p$-value associated with the decision of a visual test $T_{\theta}$ is given \blue{as the probability to observe a value at least as extreme as the test statistic $u$, 
where $u$ is the number of successful evaluations of the lineup, which leads us to a $p$-value of $P(U \ge u)$ as given in eqn (\ref{eqn:pvalue}). Since $u$ is a discrete value with boundaries 0 and $K$,
 we can also re-formulate the $p$-value in terms of upper and lower boundaries:
 \begin{equation*}
 \begin{array}{rcll}
 P(U \ge u+1) \le &p\text{-value}& (\le 1), & \text{if }u < K, \text{and in particular for } u=0\\
( 0 \le) &p\text{-value}& \le P(U \ge u-1), & \text{if }u > 1, \text{and in particular for } u=K.\\ 
 \end{array}
 \end{equation*}
 }
\red{HH: Tried to re-write it to answer the question below.
Why is the $p$ value not just $Pr(U \ge u)$ ? (We need to modify this a bit with respect to the rejection region $R$, but there should not be a difference in terms of whether we reject or accept. }

    \begin{equation*}
        \begin{cases} 
              p\text{-value} \le Pr(U \ge u)    & \text{when reject $H_0$,} \\
              p\text{-value} > 1-Pr(U \ge u)  & \text{when fail to reject $H_0$}
        \end{cases}
    \end{equation*}
\end{dfn}

%\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}\\
\red{For the following paragraph, we wanted to get rid of the absolute value of $t$ and instead look at $t \in R$ and $t \in R^c$.}

Suppose $F_{|t|}(.)$ is the distribution function of an absolute value of $t$, the classical test statistic. Suppose the associated test statistic in classical test is observed as  $t_{obs}$ with $p$-value $p_D$. By definition we have

$$p_D=Pr\left(|t| \ge t_{obs} \mid H_0\right)=1-F_{|t|}(t_{obs}) \ \ \Rightarrow \ \  |t_{obs}|=F_{|t|}^{-1}(1-p_D)$$

%Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$, the classical test statistic.
%, with non-centrality parameter $\delta$. 
Then the distribution function of $p$-value $p_D$ under $H_0$ is uniform, since:  
\begin{eqnarray}\label{dist_p}
F{p_D}(p) &=& Pr(p_D \le p)=1-Pr(1-p_D \le 1-p) \nonumber \\
  &=& 1-Pr\left(F_{|t|}^{-1}(1-p_D) \le F_{|t|}^{-1}(1-p) \right) \nonumber \\
  &=& 1-Pr\left(|t_{obs}| \le F_{|t|}^{-1}(1-p)\right) \nonumber \\
  &=&%\left\{ \begin{array}{ll}
          1-F_{|t|}\left( F_{|t|}^{-1}(1-p)\right)=p \mbox{ ; under $H_0$} 
 %         1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
%       \end{array} \right.     
\end{eqnarray}

%Thus the density of $p_D$ is Uniform(0,1)  under $H_0$. As noted by \cite{Ruppert:2007}, under $H_1$ the density of $p_D$ $$f_{p_D}(p_D; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_D);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_D))}$$ derived from equation \ref{dist_p}  is a right skewed distribution.

\blue{Similarly, we will assume that $p_{0,i}$, $i=1, ..., m-1$ are the $p$-values associated with data corresponding to the $m-1$ null plots. Since this data is generated consistently with the null hypothesis,  the $p$-values follow a standard Uniform distribution, $p_{i,0} \sim U[0,1], i= 1, ..., m-1$ (by equation \ref{dist_p}). }

Let us think of a lineup as a head-to-head comparison of the test statistic and $m-1$ null plots. 
%Let the data plot have a $p$-value of $p_D$, and the null plots $p$ values of $p_{0, i}$ with $1 \le i \le m-1$.
We know that for each comparison the probability that the data, on which the plot is based, has the smaller $p$ value is 
\begin{eqnarray*}
P(p_D < p_{0,i}) &=& 1 - P(p_{i,0} \le p_D) = 1- \int_0^1  P(p_{i,0} \le p_D \mid p_D=t) f_{p_D}(t) dt =  \\
&=& 1 - \int_0^1 F_{p_{0,i}}(t) f_{p_D}(t) dt = 1 - \int_0^1 t f_{p_D}(t) dt = 1 - E[p_D],
\end{eqnarray*}
which, in particular, is independent of $p_{0,i}$ for all $i$.

Let us make the assumption that an onlooker is able to identify  the chart corresponding to the data with the smallest $p$-value. Further we will assume that all onlookers  have the same ability in identifying the data plot.

With that, we define $X$  as the number of null plots in a lineup, for which the $p$-value $p_{0,i}$ is smaller than $p_D$.

Then $X \sim B_{m-1, E[p_D]}$, and the probability that an onlooker will pick the data plot in a given lineup is 
\[
P(X=0) = \left(1 - E[p_D] \right)^{m-1} = P(p_D \le p_0), \ \ \ \text{ where } p_0 = \min_{1 \le i \le m-1}  \ p_{0,i}.
\]

%\red{pull the results for $P(p_D < p_{i,0})$ and $P(p_D < p_0)$ to the front, including the figure on $1/m$ versus power. These results are independent of the regression setting - they don't make any assumptions in terms of regression.}

Figure \ref{fig:pval_power} gives an overview of the probability of picking the data plot for lineups of different size: as $m$ increases we have an increased probability to observe a more highly structured null plot by chance. We see that for a $p$-value $p_D$ of about 0.15 for the data plot the signal in the plot is so weak, that we cannot distinguish the data plot from null plots in a lineup of size $m=20$. \red{The following sentence should be moved back} This pattern is also seen in our experiments as shown in figure \ref{fig:pval_pcorrect}.

Even under $H_1$ we expect some observers to pick a null plot with a probability that depends on the strength of the signal in our data plot. 
Reversely, we will now make use of the number of observers who do not pick the data plot in a lineup to infer the strength of the signal in the test statistic.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.5in]{images/powerplot.pdf} 
   \caption{Comparison of probabilities to pick the data plot for different size lineups $m$ and different values for data plot strength $p_D$. The grey line shows probability of picking the data plot under $H_0$. }
   \label{fig:pval_power}
\end{figure}

Now assume that the same lineup plot is evaluated by $K$ independent observers. W.l.o.g. let the last plot be the data plot and plots 1 through $m-1$ the null plots. Let $n_i$ be the number of observers who picked plot $i$ as the plot with the structure least consistent with the null hypothesis, corresponding to random variable $N_i$.  Then  $(N_1, N_2, ..., N_m) \sim$ Mult$_{\pi_1, ..., \pi_m}$ with $\sum_i \pi_i = 1$ and $\sum_{k=1}^{m} n_k = K$. We can estimate $\pi_i$ as $\widehat{\pi_i} = n_i/K$.

For the distribution of $N_m$, %the number of times out of $K$ that observers picked the last plot to show the structure least consistent with the null hypothesis, 
we get
\[
N_m\sim \left \{ 
\begin{array}{ll}
B_{K, (1-E[p_D])^{m-1}} & \text { under } H_1\\
B_{K, 1/m} & \text { under } H_0
\end{array}
\right .
\]

By matching the expected values, we therefore get an expression for the $p$-value in the data under $H_1$  as:
\begin{equation}\label{eqn:power_estimate}
{E[p_D]} = 1- \left(\frac{E[N_m]}{K}\right)^{1/(m-1)}.
\end{equation}

\blue{Note that the right hand side of equation (\ref{eqn:power_estimate}) is independent of the parameter $\theta$, but just based on the lineup evaluation by independent observers. While this allows us to compute this value independently of the parametric setting, it also means that onlookers might pick out the data plot for a reason not related to the value of $\theta$.

%Picking out the data plot is still a measure of how different the data plot is compared to the null plots, and therefore is a test statistic of the visual test.

%This allows us to compute this value independently of the parametric setting. We therefore define the {\it signal strength} of a  visual test as the following:
%
%\begin{dfn} \label{dfn:signal}
%The {\it signal strength} $\sigma_T$ of a visual test is defined as the probability to identify the data plot.
%\end{dfn}
%
%In a lineup of size $m$, evaluated by $K$ independent observers,  we can estimate the signal strength of the test as
%\[
%\sigma_T^{m-1} = \frac{n_m}{K}.
%\]
%
%In a parametric setting, signal strength of a test coincides with the power of the test.
}

\red{We need to comment on how this ties in to the rest of the paper: this is a theoretical consideration based on the assumption that observers are able to spot the plot with the smallest/a small $p$-value. $p$ value of data plot and $p$ values from null are negatively correlated (if one is low, the other has to be higher. We need to address this.}
\red{HH: should we re-run some of the lineups with different null plots?}

\blue{
\paragraph{Subject-specific power}
Probability to reject null hypothesis is power. This is intricately related to the probability to identify the data plot from the lineup. We need to address the problematic of individual specific abilities in identifying the data plot
}. 
\red{HH: need to cite some literature from cognitive science here}

\blue{Let $X_{j\ell} \sim B_{1, \pi_{j\ell}}$ be the random variable, with $X_{j\ell}= 1$, if  subject $j$ correctly identifies the data plot from lineup $\ell$, and 0 otherwise.
We can model $\pi_{j\ell}$ with a logistic regression with subject specific random effects as:
\[
\text{logit } \pi_{j\ell} = X_\ell \beta + Z u_j,  
\]
where $X_\ell$ is a matrix of fixed effects with parameter vector $\beta$ corresponding to lineup $\ell$ and $u \sim MVN(0, \sigma_u I)$  is a vector of random variables $j = 1, ..., N_\ell$ for each of $N_\ell$ subjects presented with lineup $\ell$.
}

Theoretical power for the regression parameters is derived in the next section.
\section{Inference for a Regression Model} \label{sec:regression}

Consider a linear regression model 
\begin{equation}\label{multi} Y_i = \beta_0 + \beta_1 X_{i1} + \beta_1 X_{i2} + \beta_3 X_{i1}X_{i2} + ... + \epsilon_i 
\end{equation}
where $\epsilon_i \stackrel{iid}{ \sim } N(0,\sigma^2)$, $i=1,2, .., n$. The covariates ($X_j, j=1,..,p$) can be continuous or discrete.

Suppose $X_k$ is a categorical variable with two levels, and we test the hypothesis $H_0:\beta_k=0$ vs $H_1: \beta_k \ne 0$. If the responses for the two levels of the categorical variable $X_k$ in the model are significantly different and we fit the null model to the observed data, the resulting residual plot shows two groups of residuals. To test this we generate side-by-side boxplots of the residuals conditioned on the two levels of $X_k$, as the test statistic. If $\beta_k\ne 0$ the boxplots show a vertical displacement.

In a regression setting, there is a multitude of established graphics that help with the evaluation and diagnostics of a model \citep{cook:99}. Table \ref{tbl:stat_multiple} shows an overview of some commonly used charts and their corresponding hypothesis tests. Note that some charts can be associated with several different testing situations. In our paper, we pick the examples for situation 2 and 3 as candidates.

A lineup including the test statistic  for a binary $X_k$ is shown in Figure \ref{fig:test_category}. The 19 null plots are generated  by simulating residuals from $N(0,\hat{\sigma}^2)$. The test statistic, the plot containing the observed data, is randomly placed among these null plots. If the test statistic is identifiable the null hypothesis is rejected. % with a $p$-value of at most 0.05.

\begin{figure}[hbt]
%\begin{figurehere}
   \centering
       \scalebox{0.95}{\includegraphics{test_category.pdf}}
       \caption{Lineup plot ($m=20$) for testing $H_0: \beta_k=0$. When the alternative hypothesis is true the plot of the observed data should show a vertical displacement between box plots. Which plot has the biggest vertical displacement between the boxplots?}
       \label{fig:test_category}
\end{figure}
%\end{figurehere}

\begin{table*}[hbtp] 
\caption{Test Statistics for Testing Hypothesis Related to Model $Y_i = \beta_0 + \beta_1 X_{i1} + \beta_1 X_{i2} + \beta_3 X_{i1}X_{i2} + ... + \epsilon_i  $ } 
\centering 
\begin{tabular}{m{0.5cm}m{3cm}m{2.5cm}m{2.6cm}m{5.5cm}} 
\hline\hline 
Case & Null Hypothesis & Statistic & Test Statistic & Description \\ [0.5ex] % inserts table %heading 
\hline 
1 & $H_0: \beta_0=0$ & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot with least square line overlaid. For lineup plot, we simulate data from fitted null model. \\ 
2 & $H_0: \beta_k=0$ & Residual plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_bet_p.pdf}} \end{center} \end{minipage} & Residual vs $X_k$ plots. For lineup plot, we simulate data from normal with mean 0 variance $\hat{\sigma}^2$. \\ 
3 & $H_0: \beta_k=0$ (for categorical $X_k$) & Box plots of residuals & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.45}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} & Box plot of residuals grouped by category of $X_k$. For lineup plot, we simulate data from normal with mean 0 variance $\hat{\sigma}^2$. \\
4 & $H_0: \beta_k=0$ (interaction with categorical $X_k$) & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.11}{\includegraphics{stat_interection.pdf}} \end{center} \end{minipage} & Scatter plot with least square lines of each category overlaid. For lineup plot, we simulate data from fitted null model.\\[1ex] % [1ex] adds vertical space 
5 & $H_0: X$ Linear & Residual Plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_nonlinear.pdf}} \end{center} \end{minipage} & Residual vs predictor plots with loess smoother overlaid. For lineup plot, we simulate residual data from normal with mean 0 variance $\hat{\sigma}^2$. \\ 
6 & $H_0: \sigma^2=\sigma^2_0$ & Box plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.15}{\includegraphics{stat_sigma_box.pdf}} \end{center} \end{minipage} & Box plot of standardized residual divided by  $\sigma^2_0$. For lineup plot, we simulate data from standard normal. \\ 				
7 & $H_0: \rho_{X,Y|Z}=\rho$ & Scatter Plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot of Residuals obtained by fitting partial regression. For lineup plot, we simulate data (mean 0 and variance 1) with specific correlation $\rho$. \\ 
8 & $H_0:$ Model Fits & Histogram & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.1}{\includegraphics{stat_goodness_simple.pdf}} \end{center} \end{minipage} & Histogram of the response data. For lineup plot, we simulate data from fitted model. \\[1ex] % [1ex] adds vertical space 
9 & Special case $p=1$ $H_0: \rho_{X,Y} =\rho$ & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot with least square line overlaid For lineup plot, we simulate data with correlation $\rho$.\\			
\hline 
\end{tabular} 
\label{tbl:stat_multiple} 
\end{table*}

%\subsection{Expected power}

% Di: This is specific for the regression model
%Consider the hypothesis test $H_0: \beta_k=0$ against $H_1: \beta_k \ne 0$ in model \ref{multi}.
%%Now consider estimating the power of the visual test. 
%%Suppose $F_{|t|}(.)$ is the distribution function of an absolute value of $t$. For the regression slope parameter $\beta$ suppose the associated test statistic in classical test be $t_{obs}$ with $p$-value $p_D$. By definition we have 
%%
%%$$p_D=Pr(|t| \ge t_{obs}| H_0)=1-F_{|t|}(t_{obs}) \Rightarrow |t_{obs}|=F_{|t|}^{-1}(1-p_D)$$
%%
%%\red{HH: the following paragraph should probably move up, but I'm not sure how to change it appropriately. Mahbub, could you take care of that?}
%%Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$ distribution with non-centrality parameter $\delta$. Thus the distribution function of $p-value$ be  
%%\begin{eqnarray}\label{dist_p}
%%F{p_D}(p) &=& Pr(p_D \le p)=1-Pr(1-p_D \le 1-p) \nonumber \\
%%  &=& 1-Pr(F_{|t|}^{-1}(1-p_D) \le F_{|t|}^{-1}(1-p) ) \nonumber \\
%%  &=& 1-Pr(|t_{obs}| \le F_{|t|}^{-1}(1-p)) \nonumber \\
%%  &=&\left\{ \begin{array}{ll}
%%          1-F_{|t|}( F_{|t|}^{-1}(1-p))=p &\mbox{ ; under $H_0$} \\
%%          1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
%%       \end{array} \right.     
%%\end{eqnarray}
%%
%%Thus the density of $p_D$ is Uniform(0,1)  under $H_0$. As noted by \cite{Ruppert:2007}, under $H_1$ the density $$f_{p_D}(p_D; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_D);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_D))}$$ derived from equation \ref{dist_p}  is a right skewed distribution.  
%In a lineup plot we simulate $m-1$ residual data sets from null model where each of these $m-1$ null data sets produces a corresponding $p$-value $p_{0,i}$ and $p_{0,i} \sim \text{Uniform}(0,1)$ for $i = 1, ..., m-1$. Suppose  $p_0=\min_i(p_{0,i})$. Thus $p_0 \sim \text{Beta}(1,m-1)$.

Under the assumption that an observer is able to pick the plot with the smallest $p$-value from a lineup plot,  this leads to the decision to reject $H_0$ when $p_{B} < p_0$. Thus we have the expected power as

\begin{equation}\label{power_exp} 
   Power(\beta)=Pr(p_{B} < p_0)  \quad \text{for}  \quad \beta \ne 0
\end{equation}

Figure \ref{fig:power_expected} shows the power of the uniformly most powerful test (UMP) in comparison to the expected power of the visual test obtained from equation \eqref{power_exp}. Notice that the expected power of the visual test is almost as good as the power of UMP test. In fact, the only loss we experience stems from comparing the test statistic to only a discrete number of  $m-1$ samples from the null distribution.

%Theorem \ref{thm:power} helps to compute the expected power of visual inference.
%\begin{thm}\label{thm:power}
% Equation \ref{power_exp}  yields expected power of visual inference as Power($\beta$) = $E(1-p_D)^{m-1}$ .
%\end{thm}
% 
%{ \em proof}
%
%Since $p_0 \sim \text{Beta}(1,m-1)$,  for $t \in (0,1)$ we have the distribution function of $p_0$ be
%\begin{eqnarray*}
%F{p_0}(t) &=& (m-1) \int_0^t{(1-p_0)^{(m-2)}dp_0} \\
%  &=&  -(m-1) \int_1^{1-t}{x^{(m-2)}dx}\\
%  &=& \left[ x^{m-1}\right]^1_{1-t}\\
%  &=&1-(1-t)^{m-1} \rightarrow 1 \quad \text{as} \quad m \rightarrow \infty
%\end{eqnarray*}
%
%% verified this computation from http://www.wolframalpha.com using command int (m-1)*(1-p)^(m-2) dp, p=0,t
%
%Thus expected power in equation \ref{power_exp} be
%\begin{eqnarray*}
% Pr(p_{B} < p_0) &=& 1- Pr( p_0 \le p_{B} ) \\
%  &=& 1- \int_{0}^{1}{Pr( p_0 \le p_{B} |p_{B} =t) f_{p_{B} }(t)dt } \\
%  &=& 1-  \int_{0}^{1}{F{p_0}(t) f_{p_{B} }(t)dt } \\
%  &=& E(1-p_D)^{m-1}   \\
%%  & \rightarrow &1-  \int_{0}^{1}{ f_{p_{B} }(t)dt }  = F_{p_D}(0) \quad \text{as} \quad m \rightarrow \infty
%\end{eqnarray*}
%
%
\begin{figure}[hbtp]
   \centering
       \scalebox{.65}{\includegraphics{power_expected.pdf}}
       \caption{Expected power of visual test  and the power of UMP test for sample size $n =100$ and $\sigma = 12$.}
       \label{fig:power_expected}
\end{figure}

% \pagebreak

% -------- Heike's writeup added here

%\subsection{Some Power Considerations}

%\subsection{Expected number of choices}
%Since $X$ has a binomial distribution, we can have a look at the number of plots among the null plots that we would expect to be picked over the data plot:
%\[
%E[X] = (m-1)(1-E[p_D]).
%\]
%With an increase of the lineup size $m$ the number of null plots with a potentially stronger signal than the data plot grows linearly.
%This should allow us to infer some of the signal strength $p_D$ as
%\begin{equation} \label{plot_signal}
%E[p_D] = 1 - E[X]/(m-1),
%\end{equation}
%i.e. by averaging over the number of plots with  a stronger signal than the data plot we can evaluate signal strength of the plot even in the case where the data plot is not being picked by the observer.
%

\subsection{Estimating Power from Lineups}

We estimate the empirical power from responses on a specific lineup plot  generated with known values of sample size ($n$), variance ($\sigma^2$) and regression parameter ($\beta$) in model \ref{multi}. Suppose, we have responses from $N$ independent observers with $u$ identifications of the observed plot. This gives an estimated power of
\begin{equation}\label{power_est} Power(\beta)=\frac{u}{N} \hspace{1cm} 0 \le u \le N \end{equation}

Suppose each of $N$ independent observers gives evaluations on multiple lineup plots and responses are associated with binary random variable $Y_{ij}$. Let $Y_{ij} = 1$, if subject $j$ correctly identifies the test statistic on lineup $i$, and 0 otherwise.
We model $\pi_{ij} = E(Y_{ij})$ as  a mixed effects logistic regression

\begin{equation}
g(\pi_{ij}) = X_{ij}B  + Z_{ij} \tau_j 
\label{mixed} 
\end{equation}
%
where $\tau_j$ is random effects coefficient vector of length $q$ for subject $j$,  $\tau_j  \sim  MVN(0,\Sigma)$ with variance covariance matrix $\Sigma$, $Z_{ij}$ is the $i$th row vector of random effects covariates for subject $j$, $B$ is a vector of coefficient of length $p$, the number of fixed effect covariates being used, $X_{ij}$ is the $i$th row vector of the fixed effects covariates for subject $j$ and logit link function $g(\pi)=\log(\pi) - \log(1-\pi); 0 \le \pi \le 1$. The covariates could be demographic information of people such as age, gender, education level etc. as well as sample size ($n$), regression parameter ($\beta$) and variance ($\sigma^2$) of model \ref{multi}.

From model \ref{mixed} we obtain %$\pi=Pr(Y=1|X_1, X_2, ..., X_p)$, 
the power of the underlying testing procedure as a population average %by ignoring the random effect part. 
%Thus we have the overall probability of success ($\pi$ or power) 
for specified sample size ($n$) and  variance ($\sigma$)  as

\begin{equation}\label{eqn:power} 
Power(\beta) = \pi=Pr(Y=1|\beta, n, \sigma) 
\end{equation}

\section{Simulation Experiment} \label{sec:simulation}

\subsection{Experiment with a discrete covariate}

The experiment is designed to study the ability of human observers to detect the effect of a single variable $X_2$ (corresponding to parameter $\beta_2$) in a two variable ($p=2$) regression model (Equation \eqref{multi}). Data is simulated for different values of $\beta_2 (=0, 1, 3, 5, 7, 8, 10, 16)$, with two sample sizes ($n=100, 300$) and two standard deviations of the error ($\sigma=5, 12$). The set of $\beta_2$ values was chosen so that estimates of the power should produce reasonable power curves, comparable to the theoretical UMP test. We fixed the values of $\beta_0 = 5$,  $\beta_1=15$ and values for $X_1$ were generated as a random sample from a Poisson(30) distribution. Data sets with different combinations of $\beta_2$,  $n$ and $\sigma$ were generated with frequencies shown in Table \ref{tbl:experiment_params}. Three replicates of each level were generated. These produced 60 different ``observed data sets''.

\begin{table}[hbtp]
\caption{Values of parameters considered for three survey experiments} % title name of the table
\centering
% centering table
\begin{tabular}{c c l l l}
% creating 10 columns
\hline\hline

% inserting double-line
& & \multicolumn{3}{c}{values for slope ($\beta$)} \\
 \cline{3-5}

\raisebox{1.5ex}  {Sample size ($n$)} &   \raisebox{1.5ex} {$\sigma$} &  \multicolumn{1}{c} {Experiment 1}  & \multicolumn{1}{c} {Experiment 2}  & \multicolumn{1}{c} {Experiment 3}
\\ [0.5ex]
\hline
% inserts single-line

% Entering 1st row
&  5 & 0, 1,  3, 5, 8  & 0.25, 0.75, 1.25, 1.75, 2.75 & 0.1, 0.4, 0.75, 1.25, 1.5, 2.25\\[-1ex]
\raisebox{1.5ex}{100} &12
& 1, 3, 8, 10, 16  & 0.5, 1.5, 3.5, 4.5, 6 &\\[1ex]

% Entering 2rd row
&  5 & 0, 1, 2, 3, 5  & 0.1, 0.4, 0.7, 1, 1.5&\\[-1ex]
\raisebox{1.5ex}{300} & 12
& 1, 3, 5, 7, 10  & 0, 0.8, 1.75, 2.3, 3.5 &\\[1ex]
% [1ex] adds vertical space
\hline
% inserts single-line
\end{tabular}
\label{tbl:experiment_params}
\end{table}

For added control, to ensure a signal in the simulated observed data a blocking structure was used to filter data sets. A 1000 sets were generated for each parameter combination and the traditional $t$-statistic and $p$-value associated with $H_0: \beta_2=0$ were calculated. The 3 replicates were drawn from each of three blocks of $p$-values: (0.0-$q_{33}$), ($q_{33}$-$q_{66}$), ($q_{66}$-1) where $q_i$ is the $i$th percentile in the distribution of the $p$-values. Additional control was applied to the 19 null plots. Because the distribution of these $p$-values should follow a Uniform(0,1) distribution, data sets were binned on this range by $p$-value, and a data set was randomly selected from each bin.

\subsection{Experiment with a continuous covariate}

This experiment is designed for the same regression model (Equation \eqref{multi}) with $p=1$ and covariate $X_1$ being continuous. Data is simulated with two sample sizes ($n=100, 300$) and two standard deviations of the error ($\sigma=5, 12$). The different values for slope parameter that are used to generate data are shown in Table \ref{tbl:experiment_params}. We arbitrarily fix $\beta_0 = 6$ while generating observed data. For each combination of parameter, we generate at least three different observed data sets constituting a total of 65 lineups.

\subsection{Experiment with contaminated data}

The first two simulation experiments are based on normal error model which satisfies the conditions for uniformly most powerful (UMP) test. To study how the proposed visual inference work for a scenario where the data are not really coming from a normal model we design a contaminated data experiment. To generate the contaminated data set of size $n=100$ we used the following model

\[
  Y_i = \left\{
  \begin{array}{l l}
    5+\beta X_i + \epsilon_i  & \quad  X_i \sim N(0,1) \quad \text{ $i$ =1,...,85}\\
    15+ \eta_i & \quad X_i \sim N(\mu,1/3) \quad  i=86,...,n\\
  \end{array} \right.
\]
where $\epsilon_i \stackrel{iid}\sim N(0,\sigma)$, $\eta_i \stackrel{iid}\sim N(0,\sigma/3)$ and $\mu = -1.75$. One such plot of the contaminated data for $\sigma$=5 and $\beta$=5 is shown in figure \ref{fig:cont_dat}. For this experiment we only consider sample size $n=100$ and error standard deviation $\sigma=5$.

For this experiment we generate five replications of observed data sets for each slope value shown in table \ref{tbl:experiment_params}. This produces 30 lineups.

\begin{figure}[hbt]
%\begin{figurehere}
   \centering
       \scalebox{0.4}{\includegraphics{contaminated_data.pdf}}
       \caption{Scatterplot of a simulated contaminated data set generated such that a simple linear model produce a slope almost negligible, ie, if we fit model (Equation \eqref{multi}) with $p=1$  to this data, the resulting estimate of $\beta_1$ would not be statistically significant.
}
       \label{fig:cont_dat}
\end{figure}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{power_observed.pdf}}
       \caption{Observed power of visual test from equation \eqref{power_est} with pointwise 95\% confidence limits and the power of UMP test for sample size $n= 100,300$ and $\sigma = 12,5$ as per experiment 1.}
       \label{fig:power_observed}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{power_loess_exp1.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100,300$ and $\sigma = 12,5$ as per experiment 1.}
       \label{fig:power_loess1}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{power_loess_exp2.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100,300$ and $\sigma = 12,5$ as per experiment 2.}
       \label{fig:power_loess2}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.4}{\includegraphics{power_loess_exp3.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3. Notice that for experiment 3, power does not seem to depend on the parameter $\beta$. Di/Heike, I am not sure how I can relate this to demonstrate the power of visual inference when normal conditions are not met. Does this really test our hypothesis $H_0: \beta=0$ or some other hypothesis about the existence of cluster in the data?}
       \label{fig:power_loess3}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{power_diff_exp.pdf}}
       \caption{Difference of Observed power from UMP test power obtained in three experiments for sample size $n= 100,300$ and $\sigma = 12,5$ and values of slope parameter $\beta$ as shown in table \ref{tbl:experiment_params}.}
       \label{fig:power_diff_exp}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{power_observed_exp3.pdf}}
       \caption{Observed power of visual test from equation \eqref{power_est} with pointwise 95\% confidence limits and the power of UMP test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3. }
       \label{fig:power_observed_exp3}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_percent_correct.pdf}}
       \caption{Percentage of correct responses decreases rapidly with the increase of p-value. After p-value exceeds 1.5 it is very unlikely to identify the observed plot. The theoretical justification of this is shown in figure \ref{fig:pval_power}}
       \label{fig:pval_pcorrect}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_plot_signal.pdf}}
       \caption{p-value vs plot signal strength. The solid line represents 45 degree line which represents the equity shown in equation \eqref{plot_signal}}
       \label{fig:pval_plot_signal}
\end{figure*}

Participants for all the experiments were recruited through \cite{turk} Amazon's Mechanical Turk. Each participant was shown a sequence of 10 lineup plots. Participants are asked to select the plot with the biggest vertical difference, give a reason for their choice, and determine a level of  confidence for their decision. Gender, age, education and geographic location of each participant are also collected.
 In total, 3629 lineups were evaluated by 324 people coming from many different locations across the globe.  The results of the experiment are summarized in Figure \ref{fig:power_observed} which shows the observed power from the survey data calculated using equation \eqref{power_est} along with 95\% confidence interval calculated using Fisher's exact method.

\begin{figure}[hbtp]
   \centering
       \scalebox{0.40}{\includegraphics{power_model.pdf}}
       \caption{Estimated power curve from equation \eqref{eqn:power} along with 95\% confidence interval for sample size $n$ = 100 and $\sigma$ = 12.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown for comparison.}
       \label{fig:power_model}
\end{figure}

We fit model \eqref{mixed} to the survey data obtained from the simulation experiment. The estimated overall power curve obtained from equation \eqref{eqn:power} is shown in Figure \ref{fig:power_model}. Model \ref{mixed} also gives the subject specific power curves shown in Figure \ref{fig:power_subject}. The plot includes 20 randomly selected subject-specific power curves. Notice that the power curve estimated for one subject is above the UMP test power curve.

\begin{figure}[hbtp]
   \centering
       \scalebox{0.45}{\includegraphics{power_subject.pdf}}
       \caption{Estimated subject specific power curve from model \ref{mixed} for sample size $n$ = 100 and $\sigma$ = 12.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown for comparison.}
       \label{fig:power_subject}
\end{figure}

\section{Conclusions}

The purpose of this paper has been to examine the effectiveness of visual inference methods in direct comparison to existing inference methods. We need to be clear that this is not the purpose of visual inference generally: visual methods should not be seen as competitors to traditional inference.  The purpose here, is to  establish properties and  efficacy of visual testing procedures in order to use them in situations where traditional tests cannot be used. For this experiment the effect of $\beta_2$ was examined using side-by-side boxplots. Future experiments will be conducted to compare other regression parameters as described in Table \ref{tbl:stat_multiple} and assess sensitivity of power to modeling conditions.

\paragraph{Acknowledgement:}

This work was funded by National Science Foundation grant DMS 1007697.

%\bibliographystyle{plain}
%\bibliographystyle{plainnat}
\bibliographystyle{asa}
%\bibliographystyle{ieeetr}
\bibliography{references}

%\end{multicols}

\end{document}  %End of document.

\begin {abstract} 
Statistical graphics play a crucial role in exploratory data analysis, model checking and diagnosis. Until recently there were no formal visual methods in place for determining statistical significance of findings. This changed, when Buja et al.(2009) conceptually introduced two protocols for formal tests of visual findings. In this paper we take this a step further by comparing the lineup protocol (Buja et al.2009) against classical statistical testing  of the significance of regression model parameters. A human subjects experiment is conducted using simulated data to provide controlled conditions. Results suggest that the lineup protocol provides results equivalent to the uniformly most powerful (UMP) test and for some scenarios yields better power than the UMP test.
\end {abstract}

\end{document}

### 2012-05-08 R_codes/turk_data.R
first commit

@@ -1,0 +1,33 @@
+# Codes to obtain data from mysql database for turk experiments
+# Last updated by Mahbub on Mar 21, 2012
+
+library(ggplot2)
+library(plyr)
+
+ip.details <- read.csv("../data/ip_detais.csv",header=T)
+
+# plotting the ip locations in the world map
+
+ip.details$x <- as.numeric(ip.details$longitude)
+ip.details$y <- as.numeric(ip.details$latitude)
+
+library(maps)
+map.dat <- as.data.frame(map("world",ylim=c(-45,70), plot=FALSE)[c("x","y")])
+
+qplot( longitude,latitude,  geom="point", data=ip.details)
+
+ggplot() +
+  geom_path(aes(x,y, colour=factor("B")), data=map.dat) +
+  geom_point(aes(x,y ,  colour=factor("A")), data=ip.details, alpha=.3) +
+  opts(legend.position="none")
+
+ggsave("../images/turker_location.pdf", width=8, height=3)
+
+country.cnt <- ddply(ip.details,.(country_name), nrow)
+country.cnt <- country.cnt[order(country.cnt$V1),]
+
+qplot(country_name, V1, geom="bar",data=country.cnt) + coord_flip()
+
+
+#============ end getting data ============
+

### 2012-08-18 paper_turk.tex
reorganize section
update introduction

@@
 \usepackage{graphicx}
+\usepackage{url}
 
@@
 %\setlength{\topmargin}{-0.4in}
-\setlength{\textheight}{9in}
-
-\title{Turk Experiments for Visual Inference}
+\setlength{\textheight}{8in}
+
+\title{Designing Turk Experiments for Visual Statistical Inference}
 \author{Mahbubul Majumder, Heike Hofmann, Dianne Cook\\
@@
 
-It has been found that the visual test, which does not have distributional assumptions, has the power comparable to the classical
-tests \cite{Majumder:2011}.
+It has been found that the visual test, which does not have distributional assumptions, has the power comparable to the conventional tests \cite{Majumder:2011}.
 To examine the power of visual statistical inference we recruited human subjects from Amazon Mechanical Turk \cite{turk} for evaluating lineups \cite{buja:2009, Majumder:2011}.
@@
 
-Amazon Mechanical Turk is a very good resource for recruiting reliable survey participants for visual experiments.
-The web site is very nice and reliable to collect data.
-But to design an experiment using their web interface is a pain and often a very time consuming work.
-On top of that their technical support is not in the expected level.
+We have seen some advancement in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have introduced formal methods for testing the significance of findings using lineup protocols.
+The power of visual statistical inference or lineup protocol is studied by Majumder \cite{Majumder:2011} and it is revealed that power could be as good as conventional test.
+But where the conventional test does not exists, visual inference could be only inferential procedure without compromising a lot in power.
+The effect of different graphical design while selecting visual test statistic is studied by Heike \cite{heike:2012}.
+
+Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{Majumder:2011},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation.
+One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{Majumder:2011}.
+It is better to get observers as diverse as possible without being much concerned about the observers formal training about statistical graphics.
+
+Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments.
+The web site is very convenient and reliable to collect simple experiment data.
+But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work.
 So, to run the turk experiment we felt the necessity for a well customized web site.
-
-\section{Website to Run the Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.
-We use  Amazon Mechanical Turk web site to recruit the participants and direct them to our web site to actually participate in the survey.
-This has allow us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site.
+The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}.
+The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site.
+This facilitates getting data directly in a local server.
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_work_flow.pdf}}
+       \caption{Amazon Mechanical Turk workflow and data collection.}
+       \label{fig:turk_work_flow}
+\end{figure}
 
@@
 So we used the quantiles of p-value approach in chapter \ref{ch:regression} to obtain three replicated sample of observed data sets for a particular parameter settings.\\
+
+\section{Website to Run the Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.
+We use  Amazon Mechanical Turk web site to recruit the participants and direct them to our web site to actually participate in the survey.
+This has allow us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site.
 
@@
 
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_web.png}}
+       \caption{A sample data collection form. Lineups are presented at random for evaluations by the turk workers.}
+       \label{fig:turk_web}
+\end{figure}
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_web_feedback.png}}
+       \caption{The turk workers are given feedbacks whether their evaluation for each lineup was correct or not.
+This works as an incentive for the worker to work more enthusiastically.
+To ensure the payment, the turk workers have to provide some information using this form.}
+       \label{fig:turk_web_feedback}
+\end{figure}
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_database_design.pdf}}
+       \caption{Database design for Turk experiment data collection.
+The same database can be used for multiple turk experiments by keeping experiment information in picture details table which contains information about the lineups.}
+       \label{fig:turk_database_design}
+\end{figure}
+
 \section{Payment of Turk Worker} Turk workers are usually small payee workers.
@@
 
-\section{Selection Bias} Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did.
+\section{Quality of Turk Data}
+
+\subsection{Data Cleaning}
+
+\subsection{Diversity in the Data}
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.5}{\includegraphics{turker_country.pdf}}
+       \scalebox{.5}{\includegraphics{turker_location.pdf}}       
+       \caption{The location of turk workers on the world map shows the geographical diversity of turk workers even though most of the workers come from India and United States.}
+       \label{fig:rsq}
+\end{figure}
+
+\subsection{Selection Bias} Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did.
 In this section we intend to analyze to what extent this selection bias has occurred and how we can adjust for this.
+
+\section{Conclusion}
 

### 2012-08-22 paper_turk.tex
worked on introduction

@@
 
-It has been found that the visual test, which does not have distributional assumptions, has the power comparable to the conventional tests \cite{Majumder:2011}.
+It has been found that the visual statistical inference \cite{buja:2009}, which does not have distributional assumptions, has the power comparable to the conventional tests \cite{Majumder:2011}.
 To examine the power of visual statistical inference we recruited human subjects from Amazon Mechanical Turk \cite{turk} for evaluating lineups \cite{buja:2009, Majumder:2011}.
@@
 Even though the task of evaluating lineups is easy, the technical design of the experiment is complex and the tools available to design this from Turk website is just too simple.
-In this paper we present how we deal with this trouble and conduct our experiment.
+In this paper we present an alternative way to conduct the survey by designing a separate web site and getting turk worker do their job from this web site.
+We also present the simulation experiment design to estimate the power of visual statistical inference.
 
@@
 But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work.
-So, to run the turk experiment we felt the necessity for a well customized web site.
+So, to run the turk experiment we felt the necessity for a well customized web site where the lineups presented to the observers could be easily controlled according to the experimental design.
 The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}.
@@
 This facilitates getting data directly in a local server.
+
+As shown in figure \ref{fig:turk_work_flow} turk workers have to visit the experimental web site and give their consent to participate the survey as per IRB requirement.
+In the experimental web, there is a option for observers to try some sample lineups to get familiar with the experiment.
+Once the observers start evaluating the lineups they are sequentially shown a specific number of lineups and at the end they are given a code as a proof for their tusk completion.
+The payment of the turk worker is processed if they post the code they got from experimental web site.
+The observers are also asked to provide some demographic information about them to make sure that the code is generated.
 

### 2013-02-01 paper_turk.tex
data collection information added

@@
 Only the quantiles approach seems reasonable as it has much control over p-values and it gives similar data sets that has closest parameter estimates.
-So we used the quantiles of p-value approach in chapter \ref{ch:regression} to obtain three replicated sample of observed data sets for a particular parameter settings.\\
+So we used the quantiles of p-value approach in section \ref{sec:simulate_plot} to obtain three replicated sample of observed data sets for a particular parameter settings.\\
 
 \section{Website to Run the Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.
+PHP scripting language is used and embedded with HTML for designing the web site.
+Javascript is used for validating the input data and producing warning message.
 We use  Amazon Mechanical Turk web site to recruit the participants and direct them to our web site to actually participate in the survey.
-This has allow us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site.
+This has allowed us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site to transfer data to our server.
 
@@
 
+\subsection{Data collection sequence} Once turk users are directed to our web site, they can see the detailed explanation on how they can perform the task of evaluation.
+Some simple examples are displayed along with correct responses.
+The users have options to try some test lineups before going for the actual experiment.
+But before that they have to provide the informed consent as per IRB requirement.
+The flow chart for this is shown in Figure \ref{fig:turk_data_flow}
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_data_flow.png}}
+       \caption{Data collection work flow. Turk worker can try some test lineups before going to the live experiment after providing informed consent.}
+       \label{fig:turk_data_flow}
+\end{figure}
+
+Two web forms are designed to collect information from the turk users.
+The first form shown in Figure \ref{fig:turk_web} collects feedback information about a single lineup.
+The information collected through this form is all about the lineup that includes plot number selected, reasons for selection and the confidence level of the selection.
+Each turk user is identified by the nick name which is mainly the turk ID.
+
+Each turk user is shown some specific number of lineups for evaluation.
+These lineups are randomly selected from a pool of lineups designed for evaluations.
+The algorithm for how the lineups should be selected to show and what would be the order of display is implemented in the form shown in Figure \ref{fig:turk_web}.
+Also there is a check for invalid information which is implemented using javascript.
+If users try to go forward without giving any feedback they are not allowed to do that showing a warning message.
+
 \begin{figure}[hbtp]
@@
 \end{figure}
+
+After the evaluation is recorded on a lineup through form shown in Figure \ref{fig:turk_web} another form shown in Figure \ref{fig:turk_web_feedback} is used to give feedback to the turk users whether they correctly identifies the true plot and how many evaluations are recorded from the users.
+This form is also used to collect demographic and educational information about the user.
+After the required number of evaluations are obtained from each turk user, a pass code is given as a proof of the completion of the task which then later used for payment purpose.
 
@@
 \end{figure}
+
+\subsection{Database design} The design of the database to store the collected data is shown in Figure \ref{fig:turk_database_design}.
+It is designed such a way that data from many different experiments can be stored in the same database.
+In total five separate tables are used.
+Table turk\_worker contains static information about each turk worker.
+The location information of each turk worker is stored in ip\_detals table.
+The information in this table is collected later based on the ip address of each turk worker.
+Table picture\_delais contains the static information about each lineup.
+Table feedback is a dynamic table that grows with the number of feedbacks from each turk user.
+The multiple activities of each turk user are recorded in turk\_activity table.
+This table also contains the codes provided to the user once they finish the experiment.
+For our web site we used MySQL database located on a local server.
 

### 2013-04-18 paper_turk.tex
turk payment information updated

@@
 One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{Majumder:2011}.
-It is better to get observers as diverse as possible without being much concerned about the observers formal training about statistical graphics.
+It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.
 
 Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments.
+This is the place where people come to work online and get paid.
 The web site is very convenient and reliable to collect simple experiment data.
@@
 These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.
+
+\begin{table}[hbtp]
+\caption{Number of task submitted by the turk workers, number of task got rejected and total task completion time for each of the different experiment indicate the performance of turk workers.
+Majority of the tasks are rejected for boxplot experiment and the payment per task was the lowest for this experiment.}
+\centering 
+\begin{tabular}{clccccc} 
+\hline
+Experiment &  Plot & Submitted & Rejected & Duration & Pay/Task \\ %[0.5ex] % inserts table %heading 
+\hline
+1 & Boxplot & 406 & 106 & 527340 & 0.5\\
+2 & Scatterplot & 359 & 9 & 153660 & 1\\
+3 & Contaminated plot & 219 & 19 & 454200 & 1\\
+4 & Polar vs Cartesian & 110 & 10 & 41940 &1\\
+5 & Hist vs density & 234 & 37 & 149640 & 1\\
+6 & Violine vs boxplot & 417 & 17 & 381120 &1 \\
+7 & Group separation & 106 & 6 & 18540 &1\\
+8 & Sine Illusion & 101 & 1 & 282180 &1\\
+\hline
+\end{tabular}
+\label{tbl:worker_performance}
+\end{table}
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.6}{\includegraphics{rejected_task.pdf}}
+       \caption{Percentage of rejected task for various experimental plot type.}
+       \label{fig:rejected_task}
+\end{figure}
 

### 2013-04-18 R/turk_paper.R

@@ -1,33 +1,200 @@
-# Codes to obtain data from mysql database for turk experiments
-# Last updated by Mahbub on Mar 21, 2012
+# Complete R code for turk paper
 
 library(ggplot2)
 library(plyr)
 
-ip.details <- read.csv("../data/ip_detais.csv",header=T)
+# Turk experiment data summary
+
+turk.dat <- read.csv("../data/turk_summary.csv",header=T)
+turk.dat$percent_rejected <- with(turk.dat, rejected*100/submitted)
+
+ggplot(turk.dat, aes(x = factor(plot, levels=plot[order(percent_rejected)]), y=percent_rejected))+
+  geom_bar(stat="identity") + xlab("Experimental plot type") +
+  coord_flip() + ylab("Percentage of rejected task")
+
 
 # plotting the ip locations in the world map
+
+ip.details <- read.csv("../data/ip_detais.csv",header=T)
 
 ip.details$x <- as.numeric(ip.details$longitude)
 ip.details$y <- as.numeric(ip.details$latitude)
 
 library(maps)
 map.dat <- as.data.frame(map("world",ylim=c(-45,70), plot=FALSE)[c("x","y")])
+map.dat <- map_data("world")
 
 qplot( longitude,latitude,  geom="point", data=ip.details)
 
 ggplot() +
-  geom_path(aes(x,y, colour=factor("B")), data=map.dat) +
-  geom_point(aes(x,y ,  colour=factor("A")), data=ip.details, alpha=.3) +
-  opts(legend.position="none")
-
-ggsave("../images/turker_location.pdf", width=8, height=3)
+  geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) +
+  geom_point(aes(x,y, colour=factor("A")), data=ip.details, alpha=.6) +
+  theme(legend.position="none") + xlab("Longitude") +ylab("Latitude")
+ggsave("../images/turker_location.pdf", width=8, height=4)
 
 country.cnt <- ddply(ip.details,.(country_name), nrow)
-country.cnt <- country.cnt[order(country.cnt$V1),]
+country.cnt <- country.cnt[order(country.cnt$V1, decreasing=T),]
+cnt <- rbind(country.cnt[1:2,],data.frame(country_name="rest of the world", V1=sum(country.cnt[-c(1:2),2])))
+qplot(country_name,V1, geom="bar", data=cnt, stat="identity") + 
[…]

### 2013-06-02 paper_turk.tex
MTurk figure

@@
 It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.
+
+Figure \ref{fig:amazon_task} displays an example of such a task taken from their web site.
+In this task a worker just has to select from a pool of options and submit the task.
+The instructions are usually accompany the task and they are very simple and easy to follow.
+
+\begin{figure}[htbp] 
+   \centering
+   \includegraphics[width=5in]{amazon_task.pdf} 
+   \caption{An example of amazon mechanical turk task.
+Tasks are usually very simple and designed for human evaluations.
+With each task, simple instructions are given for workers to follow.
+The workers first accept the task before submitting their response.}
+   \label{fig:amazon_task}
+\end{figure}
 

### 2013-06-02 R/turk_paper.R

@@ -11,7 +11,7 @@ turk.dat$percent_rejected <- with(turk.dat, rejected*100/submitted)
 ggplot(turk.dat, aes(x = factor(plot, levels=plot[order(percent_rejected)]), y=percent_rejected))+
   geom_bar(stat="identity") + xlab("Experimental plot type") +
   coord_flip() + ylab("Percentage of rejected task")
-
+ggsave("../images/rejected_task.pdf", width=6, height=4)
 
 # plotting the ip locations in the world map
 

### 2013-06-10 paper_turk.tex
Abstract
abstract and introduction modified

--- 2013-02-01 paper_turk.tex
@@
 
-It has been found that the visual statistical inference \cite{buja:2009}, which does not have distributional assumptions, has the power comparable to the conventional tests \cite{Majumder:2011}.
-To examine the power of visual statistical inference we recruited human subjects from Amazon Mechanical Turk \cite{turk} for evaluating lineups \cite{buja:2009, Majumder:2011}.
-The Turk website is designed to recruit workers for simple and easy tasks.
-Even though the task of evaluating lineups is easy, the technical design of the experiment is complex and the tools available to design this from Turk website is just too simple.
-In this paper we present an alternative way to conduct the survey by designing a separate web site and getting turk worker do their job from this web site.
-We also present the simulation experiment design to estimate the power of visual statistical inference.
+Human observers are needed to evaluate lineups that are used to test the significance of findings using statistical graphics.
+One good option is to recruit people from online workplace like Amazon Mechanical Turk (MTurk).
+It has the facilities to design online task that could serve the purpose of evaluation of lineups.
+But the MTurk website is designed to recruit workers for simple and easy tasks.
+Even though the task of evaluating lineups is easy, the technical design of the underlying experiment may be complex and the tools available to design this from MTurk website is just too simple.
+In this paper we present an alternative way to conduct the survey on lineups by designing a separate web site and getting turk worker do their job from this web site.
+The web site is now hosted and has been in use.
+Multiple experiments are already done through this web site.
+It turns out to be a very efficient way of getting lineups being evaluated by online observers.
+Getting results from this web site is very convenient and secure.
+This paper also describes how to design MTurk experiments to evaluate lineups.
 
@@
 
-We have seen some advancement in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have introduced formal methods for testing the significance of findings using lineup protocols.
-The power of visual statistical inference or lineup protocol is studied by Majumder \cite{Majumder:2011} and it is revealed that power could be as good as conventional test.
-But where the conventional test does not exists, visual inference could be only inferential procedure without compromising a lot in power.
-The effect of different graphical design while selecting visual test statistic is studied by Heike \cite{heike:2012}.
+There have been some advancement in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols.
+The power of visual statistical inference or lineup protocol is studied by Majumder \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better.
+But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.
+
+In visual statistical inference the test statistics is a plot of the observed data.
+This plot is placed randomly in a layout of plots called lineup.
+The rest of the plots in the lineups are generated from the model specified by the null hypothesis.
+The lineup is evaluated by human observer.
+If the observed plot is identified in the lineup, the null hypothesis is rejected.
+
+%The effect of different graphical design while selecting visual test statistic is studied by Heike \cite{heike:2012}.
 
 Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{Majumder:2011},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation.
-One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{Majumder:2011}.
-It is better to get observers as diverse as possible without being much concerned about the observers formal training about statistical graphics.
+One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}.
+It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.
+
+There are some reasons a researcher needs to evaluate a lineup.
+One is to assess the power of the visual test.
+The another reason would be to make decision based on the lineup.
+Other reasons could be to present the results of the conventional test with visual tools such as lineup.
+
+\subsection{Amazon Mechanical Turk (MTurk)}
 
 Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments.
+This is the place where people come to work online and get paid.
 The web site is very convenient and reliable to collect simple experiment data.
@@
 This facilitates getting data directly in a local server.
+
+Figure \ref{fig:amazon_task} displays an example of such a task taken from their web site.
+In this task a worker just has to select from a pool of options and submit the task.
+The instructions are usually accompany the task and they are very simple and easy to follow.
+
+\begin{figure}[htbp] 
+   \centering
+   \includegraphics[width=5in]{amazon_task.pdf} 
+   \caption{An example of amazon mechanical turk task.
+Tasks are usually very simple and designed for human evaluations.
+With each task, simple instructions are given for workers to follow.
+The workers first accept the task before submitting their response.}
+   \label{fig:amazon_task}
+\end{figure}
 
@@
 These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.
+
+\begin{table}[hbtp]
+\caption{Amazon mechanical turk experiments and their properties. Duration in hours per 100 tasks show the popularity of some tasks compared to others.}
+\centering
+\begin{tabular}{rlrrrrrrr}
+  \hline
+& Experiment& \multicolumn{2}{c}{ Total Task}& Average & \multicolumn{2}{c}{Duration (hour)} & Payment & Pay rate\\
+\cline{3-4} \cline{6-7}
+Serial & description & submitted & rejected & time(min) & Actual & 100 task& \$/task & \$/hour\\ 
+  \hline
+1 & Boxplot & 406 & 106 & 10.68 & 146.48 & 36.08 & 0.50 & 2.81 \\ 
+  2 & Scatterplot & 359 &   9 & 10.80 & 42.68 & 11.89 & 1.00 & 5.58 \\ 
+  3 & Contaminated plot & 219 &  19 & 13.53 & 126.17 & 57.61 & 1.00 & 2.22 \\ 
+  4 & Polar vs Cartesian & 110 &  10 & 20.65 & 11.65 & 10.59 & 1.00 & 2.91 \\ 
+  5 & Hist vs density & 234 &  37 & 17.85 & 41.57 & 17.76 & 1.00 & 3.36 \\ 
+  6 & Violin vs boxplot & 417 &  17 & 17.95 & 105.87 & 25.39 & 1.00 & 3.34 \\ 
+  7 & Group separation & 106 &   6 & 16.13 & 5.15 & 4.86 & 1.00 & 3.72 \\ 
+  8 & Sine Illusion & 101 &   1 & 16.52 & 78.38 & 77.60 & 1.00 & 3.63 \\ 
+  9 & Gene expression & 103 &   3 & 12.47 & 11.27 & 10.94 & 0.50 & 2.41 \\ 
+  10 & Test normality & 406 &   6 & 22.70 & 74.35 & 18.31 & 1.00 & 2.64 \\ 
+   \hline
+\end{tabular}
+\label{tbl:mturk}
+\end{table}
+
+\begin{figure}[htbp] 
+   \centering
+   \includegraphics[width=3in]{rejected_task.pdf}
+      \includegraphics[width=3in]{task_duration.pdf} 
+   \caption{Percentage of rejected tasks and duration of each experiment in hour per 100 tasks for each of the 10 experiments.
+Most of the tasks got rejected for box plot experiment.
+Even though the sine illusion experiment took longest to finish the rejection rate is lowest for this experiment.}
+   \label{fig:task_duration}
+\end{figure}
 

### 2013-06-10 paper_turk.tex
references updated

@@
 
-Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{Majumder:2011},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation.
+Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{majumder:2013},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation.
 One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}.

### 2013-06-10 paper_turk.tex
Amazon description

@@
 \end{figure}
+
+Human observers were recruited to evaluate the experimental lineups through Amazon Mechanical Turk \cite{turk} or MTurk Web site.
+It is an online work place where people from around the world can perform some tasks and get paid.
+Usually tasks are very simple and no specialized training is required.
+Being a human is the main requirement.
+Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters need.
+The tasks are designed such that it does not take much time to complete.
+Humans are still better than computers in performing these types of tasks.
+The the amount of money paid for each task is very small as well.
+
+It is very fast, cheap and reliable to recruit people from MTurk.
+Thats why it is getting very popular among the researchers who perform human subject experiment.
+The another benefit is that a very diverse pool of subjects can be recruited which is otherwise very hard to obtain for a study.
+The researchers can easily filter the workers based on their experimental design, such as recruiting people only from a specific geographical location or a group of people who satisfy certain criteria etc.
+The recruiter can decide who they pay or not.
+Workers have to satisfy the task requirement to ensure payment.
+But at the end it is the recruiter who has the final say.
+Usually recruiters pay promptly after the task has been done properly and thats why MTurk is very popular among the online job seeker.
+At any point of time thousands of tasks are available for the thousands of workers around the world.
+
+Because of its convenience it is getting popular for scientific research study as well.
+In comparison with a lab study \cite{suri:2010} perform the same study using MTurk and demonstrate that their study results are as good as the lab study results even though MTurk study required less time and cost while provided more convenience.
+\cite{majumder:2013} recruited people from MTurk for their simulation study in estimating the power of visual statistical inference.
+They have done numerous pilot studies in lab before doing actual MTurk study and found similar results.
+\cite{mason:2012} explains various features of MTurk and describes how it can be used as part of human behavioral study.
+
+We designed and developed a web site which enables to display the lineups to the observers as per experimental design.
+The MTurk workers were redirected to the web site and the data were collected, stored automatically into a local database server.
+Demographic informations such as age group, gender and education levels were also collected.
+The time taken for each evaluation is computed based on the time the plot was shown and the time the feedback was received.
+The location of the observer is determined by the ip address of the observer.
 

### 2013-06-12 paper_turk.tex
abstarct and introduction

@@
-\documentclass{article}
+\documentclass[11pt]{article}
 
@@
 \usepackage{url}
+\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}
 
@@
 
+\tableofcontents
+
 \maketitle
@@
 One good option is to recruit people from online workplace like Amazon Mechanical Turk (MTurk).
-It has the facilities to design online task that could serve the purpose of evaluation of lineups.
-But the MTurk website is designed to recruit workers for simple and easy tasks.
-Even though the task of evaluating lineups is easy, the technical design of the underlying experiment may be complex and the tools available to design this from MTurk website is just too simple.
-In this paper we present an alternative way to conduct the survey on lineups by designing a separate web site and getting turk worker do their job from this web site.
-The web site is now hosted and has been in use.
-Multiple experiments are already done through this web site.
-It turns out to be a very efficient way of getting lineups being evaluated by online observers.
+It has the facilities to create online task that would allow people to evaluate lineups and get paid.
+MTurk is designed for simple and easy tasks.
+The technical design of the underlying experiment for visual inference may be complex and the tools available to design this from MTurk is just too simple.
+In this paper we present an alternative way to conduct the survey on lineups by designing a separate web application and getting turk worker do their job from this web site.
+The web site is now hosted and has been in use and multiple experiments were already done.
+It turns out to be a very efficient way of getting lineups evaluated by online observers.
 Getting results from this web site is very convenient and secure.
-This paper also describes how to design MTurk experiments to evaluate lineups.
+This paper also describes how to design MTurk experiments.
 
@@
 
-There have been some advancement in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols.
-The power of visual statistical inference or lineup protocol is studied by Majumder \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better.
-But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.
-
+There have been some advancements in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols.
 In visual statistical inference the test statistics is a plot of the observed data.
@@
 The rest of the plots in the lineups are generated from the model specified by the null hypothesis.
-The lineup is evaluated by human observer.
-If the observed plot is identified in the lineup, the null hypothesis is rejected.
+A human observer is then asked to evaluate the lineup.
+If the observer detects the actual plot in the lineup, the null hypothesis is rejected.
+
+The power of visual test is studied by Majumder \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better.
+But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.
+
+These developments open up a whole new area of statistical research where lineups need to be evaluated by human observer.
+There are some reasons a researcher needs to evaluate lineups.
+One is to assess the power of the visual test \cite{heike:2012} for different visual test statistics.
+The another reason would be to make decision based on the lineup, i.e., to use lineup protocol in practical application \cite{niladri:2012}.
+Other reasons could be to present the results of the conventional test with visual tools such as lineup.
 
@@
 
-Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{majumder:2013},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation.
+The power of visual test can be obtained theoretically \cite{majumder:2013} under some conditions.
+In general it is hard to obtain explicitly with a mathematical formula since it is very much dependent on individual observation.
 One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}.
 It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.
-
-There are some reasons a researcher needs to evaluate a lineup.
-One is to assess the power of the visual test.
-The another reason would be to make decision based on the lineup.
-Other reasons could be to present the results of the conventional test with visual tools such as lineup.
 
@@
 
-\begin{figure}[hbtp]
+\begin{figure}[htbp]
    \centering
@@
 
-\section{Experimental Design} \label{sec:exp_design}
+\section{Experimental Design} \label{sec:turk_exp}
 
@@
 
-\section{Website to Run the Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.
+\section{Web Application for Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.
 PHP scripting language is used and embedded with HTML for designing the web site.
@@
 
-\section{Payment of Turk Worker} Turk workers are usually small payee workers.
+\section{Managing Turk Task} Turk workers are usually small payee workers.
 There several issues related to the payment of their effort.
@@
 \end{document}
-
-\documentclass{article}
-\usepackage{times}
-\usepackage{natbib}
-%\usepackage{multicol}
-%\RequirePackage{natbib}
-\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
-%\usepackage[dvips]{graphics}
-
-\graphicspath{{images/}}
-\usepackage{color}
-\newcommand{\blue}[1]{{\color{blue} #1}}
-\newcommand{\red}[1]{{\color{red} #1}}
-
-\setlength{\oddsidemargin}{0in}
-\setlength{\evensidemargin}{0in}
-\setlength{\textwidth}{6.5in}
-\setlength{\topmargin}{-0.4in}
-\setlength{\textheight}{9in}
-\evensidemargin \oddsidemargin
-
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{dfn}{Definition}[section]
-\newtheorem{cor}{Corollary}[thm]
-\newtheorem{con}{Conjecture}[thm]
-%\setlength{\parindent}{0in}   % for no indent
-
-%\topmargin -0.10in   % when making pdf
-%\textheight 9.15in  % when making pdf
-
-\setlength\parindent{0pt}
-
-% Article top matter
-\title{Turk Experiments for Visual Inference}
-\author{Mahbubul Majumder, Heike Hofmann, Dianne Cook\\
-        Department of Statistics, Iowa State University}
-%\date{\today}  %\today is replaced with the current date
-
-\begin{document}
-
-\maketitle
-
-\begin {abstract}
-
-It has been found that the visual test, which does not have
-distributional assumptions, has the power comparable to the classical
-tests [3]. To examine the power of visual statistical inference we
-recruited human subjects from Amazon Mechanical Turk \cite{turk}  for
-evaluating lineups[1,2]. The Turk website is designed to recruit
-workers for simple and easy tasks. Even though the task of evaluating
-lineups is easy, the technical design of the experiment is complex and
-the tools available to design this from Turk website is just too
-simple. In this paper we present how we deal with this trouble and to
-conduct our experiment.
-
-Statistical graphics play a crucial role in exploratory data analysis, model checking and diagnosis.
-Until recently there were no formal visual methods in place for determining statistical significance of findings.
-This changed, when \citet{buja:2009} conceptually introduced two protocols for formal tests of visual findings.
-In this paper we take this a step further by comparing the lineup protocol \citep{buja:2009} against classical statistical testing  of the significance of regression model parameters.
-A human subjects experiment is conducted using simulated data to provide controlled conditions.
-Results suggest that the lineup protocol provides results equivalent to the uniformly most powerful (UMP) test and for some scenarios yields better power than the UMP test.
-\end {abstract}
-
-%\begin{multicols}{2}
-%\twocolumn
-
-\section{Introduction}
-
-Any statistical analysis must include some statistical graphics.
-For exploratory data analysis, statistical graphics play an invaluable role in model checking and diagnostics.
-Even though we have established mathematical procedures to obtain various statistics, we need to support the results by also producing the relevant plots.
-
-\bibliographystyle{plain}
-%\bibliographystyle{asa}
-\bibliography{references}
-
-\end{documents}
-
-Any statistical analysis must include some statistical graphics.
-For exploratory data analysis, statistical graphics play an invaluable role in model checking and diagnostics.
-Even though we have established mathematical procedures to obtain various statistics, we need to support the results by also producing the relevant plots.
-
-The scientific foundation of graphical methods for data analysis is well established by \cite{cleveland:1984}.
-In recent years we have seen several major advances in statistical graphics.
-Modern computing systems like R and SAS ease the production of high quality statistical plots.
-A grammar of graphics introduced by \cite{wilkinson:1999} presents a structured way to generate specific graphics from data and define connections between disparate types of plots.
-\cite{hadley:2009} has implemented a revised version of the grammar of graphics in R, in the package {\tt ggplot2}.
-\blue {Graham Wills has implemented the grammar in SPSS, but I'm not sure how to cite this.}
-
-\citet{buja:2009}, following from \cite{gelman:2004}, proposed two protocols that allow the testing of discoveries made from statistical graphics.
-This work represents a major advance for graphics, because it bridges the gulf between classical statistical inference procedures and exploratory data analysis.
-
-In this paper we compare graphical inference to classical statistical inference for a set of regression type example.
-We also present results of a human-subject study assessing the performance of individuals on lineup plots \citep{buja:2009} for testing significance of regression parameters.
-
-Section \ref{sec:visual_test} describes the basic ideas of visual inference, Section \ref{sec:regression} applies these ideas to the case of inference for regression analysis.
-In Section \ref{sec:simulation} we outline the setup for the human-subject study and  and present results.
-
-\begin{table*}[hbtp]
-\caption{Comparison of visual inference with existing inference technique}
-\centering 
-\begin{tabular}{llll} 
-\hline
-  & Mathematical Inference &  Visual Inference \\ %[0.5ex] % inserts table %heading 
-\hline
-  Hypothesis & $H_0: \beta=0$ vs $H_1: \beta \ne 0$& $H_0: \beta=0$ vs $H_1: \beta \ne 0$\\
- & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
-
- Test statistic & $T(y)=\frac{\hat{\beta}}{se(\hat{\beta})}$ & $T(y)=$ \begin{minipage}[h]{1cm} \begin{center} \scalebox{0.45}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} \\
-
- & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
-
- Null Distribution & $f_{T(y)}(t); $\begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.55}{\includegraphics{stat_mathematical_test.pdf}} \end{center} \end{minipage} & $f_{T(y)}(t); $ \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.19}{\includegraphics{test_category.pdf}} \end{center} \end{minipage} \\
- & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
- Reject $H_0$ if & observed $T$ is extreme & observed plot is identifiable \\
-\hline 
-\end{tabular}
-\label{tbl:compare}
-\end{table*}
-
-\section{Visual Statistical Inference} \label{sec:visual_test} 
-Visual tests are non-parametric tests of the form $H_0$: the data plot is visually not distinguishable from a null plot vs $H_1$: the data plot is visually distinguishable from a plot generated consistently with $H_0$.
-
-Power of a plot and $p$-value have been derived in Buja and Wickham as ...
-
-for this paper, we want to place the parametric inference of a regression setting into the framework of visual testing:
-
-This section outlines the concepts of visual inference in comparison to the procedures of classical statistical inference.
-Table \ref{tbl:compare} (derived from \citet{buja:2009}) gives a summarized overview of this comparison.
-
-Let $\theta$ be a population parameter of interest, with $\theta \in \Theta$, the parameter space. 
-Any null hypothesis $H_0$ then partitions the parameter space into $\Theta_0$ and $\Theta_0^c$, with $H_0: \theta \in \Theta_0$ versus $H_1: \theta \in \Theta_0^c$.
-
-\blue{Similarly, for any test, we have a rejection region $R$ and, complementary to that, $R^c$,  that partition the space of the test statistic, which is usually a subspace of the real numbers.}
-%\subsection{Visual Statistic}
-
-For visual inference, the statistic is -- unlike in the classical hypothesis test -- not a single value, but a graphical representation of the data chosen to display the strength of the parameter of interest, $\theta$.
-When the alternative hypothesis is true, it is expected that the plot of the observed data, the test statistic, will have visible feature(s) consistent with $\theta \in \Theta_0^c$, and that visual artifacts will not distinguish the test statistic as different when $H_1$ is not true.
-We will call a plot with this property a {\it visual statistic} for $\theta$.
-More formally,
-
-\blue{
-
-\begin{dfn} \label{dfn:test}
-A \textit{visual test (statistic)} $T_\theta$ is defined as the grammar \citep{wilkinson:1999} of the plot,  consisting of type and specification of aesthetics necessary for complete reproducibility.
-\end{dfn}
-}
-
-\begin{dfn}\label{dfn:lplot}
-A lineup plot is a layout of $m$ visual statistics, consisting of 
-\begin{itemize}\itemsep-3pt
-\item $m-1$ plots simulated from the model specified by $H_0$  (null plots) and 
-\item the test statistic produced by plotting the observed data, possibly arising from $H_1$.
-\end{itemize}
-\end{dfn}
-
-The $(m-1)$ null plots can be considered to be samples drawn from the sampling distribution of the test statistic assuming that the null hypothesis is true.
-If $H_1$ is true, \blue{we expect this to be reflected as a feature in the test statistic, i.e. the plot of the data, that makes it visually distinguishable from the null plots.}
-{\em If the test statistic cannot be identified} in the lineup the conclusion is to {\em not reject the null hypothesis.}  A careful visual inspection follows, and the observer is asked to point out the plot most different from the lineup.
-
-Since the lineup plot consists of $m$ plots, the probability of choosing any one of them is $1/m$. Thus we have type-I error probability of $1/m$.
-
-%The lineup plot can be evaluated by one or more individuals.
-When a single individual identifies the observed graph in the lineup plot we report a $p$-value of at most $1/m$, otherwise the $p$-value is at least $1-\frac 1m$.
-
- %Notice that when $N=1$, this $p$-value is $\frac1m$.
-
-%\subsection{Power}
-
-For two different visual test statistics of the same observed data, the one  is better, in which a specific pattern is more easily distinguishable to the observer.
-This should be reflected in the power of the test.
-We can assess power therefore both empirically based on experimental data and through theoretical considerations.
-
-%Next, we will develop power theoretically and then relate it to the empirical results.
-\blue{We will first theoretically define and  derive the power of  a visual test in the setting of a parametric hypothesis test, i.e.
-we assume a test  of $H_0: \theta = 0$ vs $H_1: \theta \neq 0$ for some real valued parameter vector $\theta$.
-In a next step we will then relate the theoretical results to our empirical findings.}
-
-\begin{dfn} \label{dfn:power}
-For a lineup of $m$ plots the power of \blue{a visual test} $T$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
-    \begin{equation*}
-      \text{Power}_T(\theta)= 
-        \begin{cases} 
-              \text{Type-I error}=\frac1m & \text{if $\theta \in \Theta_0$,} \\
-              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
-        \end{cases}
-    \end{equation*}
-\end{dfn}
-
-For any single observer, the power of a visual test has a lower limit of $\frac1m$ since the probability that an observer will randomly pick the test statistic under $H_0$ is $\frac1m$.
-
-When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. This leads us to obtain the probability 
-\begin{equation}\label{eqn:pvalue}
-Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} \left(\frac{1}{m}\right)^k\left(1-\frac 1m\right)^{(K-k)}}
-\end{equation}
-where $u$ is the observed number of successful evaluations. We use this probability to  define the $p$-value for visual test $T_{\theta}$ as follows:
-\begin{dfn} \label{dfn:pval}
-The $p$-value associated with the decision of a visual test $T_{\theta}$ is given \blue{as the probability to observe a value at least as extreme as the test statistic $u$, 
-where $u$ is the number of successful evaluations of the lineup, which leads us to a $p$-value of $P(U \ge u)$ as given in eqn (\ref{eqn:pvalue}).
-Since $u$ is a discrete value with boundaries 0 and $K$,
- we can also re-formulate the $p$-value in terms of upper and lower boundaries:
- \begin{equation*}
- \begin{array}{rcll}
- P(U \ge u+1) \le &p\text{-value}& (\le 1), & \text{if }u < K, \text{and in particular for } u=0\\
-( 0 \le) &p\text{-value}& \le P(U \ge u-1), & \text{if }u > 1, \text{and in particular for } u=K.\\ 
- \end{array}
- \end{equation*}
- }
-\red{HH: Tried to re-write it to answer the question below.
-Why is the $p$ value not just $Pr(U \ge u)$ ? (We need to modify this a bit with respect to the rejection region $R$, but there should not be a difference in terms of whether we reject or accept. }
-
-    \begin{equation*}
-        \begin{cases} 
-              p\text{-value} \le Pr(U \ge u)    & \text{when reject $H_0$,} \\
-              p\text{-value} > 1-Pr(U \ge u)  & \text{when fail to reject $H_0$}
-        \end{cases}
-    \end{equation*}
-\end{dfn}
-
-%\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}\\
-\red{For the following paragraph, we wanted to get rid of the absolute value of $t$ and instead look at $t \in R$ and $t \in R^c$.}
-
-Suppose $F_{|t|}(.)$ is the distribution function of an absolute value of $t$, the classical test statistic.
-Suppose the associated test statistic in classical test is observed as  $t_{obs}$ with $p$-value $p_D$.
-By definition we have
-
-$$p_D=Pr\left(|t| \ge t_{obs} \mid H_0\right)=1-F_{|t|}(t_{obs}) \ \ \Rightarrow \ \  |t_{obs}|=F_{|t|}^{-1}(1-p_D)$$
-
-%Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$, the classical test statistic.
-%, with non-centrality parameter $\delta$. 
-Then the distribution function of $p$-value $p_D$ under $H_0$ is uniform, since:  
-\begin{eqnarray}\label{dist_p}
-F{p_D}(p) &=& Pr(p_D \le p)=1-Pr(1-p_D \le 1-p) \nonumber \\
-  &=& 1-Pr\left(F_{|t|}^{-1}(1-p_D) \le F_{|t|}^{-1}(1-p) \right) \nonumber \\
-  &=& 1-Pr\left(|t_{obs}| \le F_{|t|}^{-1}(1-p)\right) \nonumber \\
-  &=&%\left\{ \begin{array}{ll}
-          1-F_{|t|}\left( F_{|t|}^{-1}(1-p)\right)=p \mbox{ ; under $H_0$} 
- %         1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
-%       \end{array} \right.     
-\end{eqnarray}
-
-%Thus the density of $p_D$ is Uniform(0,1)  under $H_0$.
-As noted by \cite{Ruppert:2007}, under $H_1$ the density of $p_D$ $$f_{p_D}(p_D; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_D);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_D))}$$ derived from equation \ref{dist_p}  is a right skewed distribution.
-
-\blue{Similarly, we will assume that $p_{0,i}$, $i=1, ..., m-1$ are the $p$-values associated with data corresponding to the $m-1$ null plots.
-Since this data is generated consistently with the null hypothesis,  the $p$-values follow a standard Uniform distribution, $p_{i,0} \sim U[0,1], i= 1, ..., m-1$ (by equation \ref{dist_p}).
-}
-
-Let us think of a lineup as a head-to-head comparison of the test statistic and $m-1$ null plots. 
-%Let the data plot have a $p$-value of $p_D$, and the null plots $p$ values of $p_{0, i}$ with $1 \le i \le m-1$.
-We know that for each comparison the probability that the data, on which the plot is based, has the smaller $p$ value is 
-\begin{eqnarray*}
-P(p_D < p_{0,i}) &=& 1 - P(p_{i,0} \le p_D) = 1- \int_0^1  P(p_{i,0} \le p_D \mid p_D=t) f_{p_D}(t) dt =  \\
-&=& 1 - \int_0^1 F_{p_{0,i}}(t) f_{p_D}(t) dt = 1 - \int_0^1 t f_{p_D}(t) dt = 1 - E[p_D],
-\end{eqnarray*}
-which, in particular, is independent of $p_{0,i}$ for all $i$.
-
-Let us make the assumption that an onlooker is able to identify  the chart corresponding to the data with the smallest $p$-value.
-Further we will assume that all onlookers  have the same ability in identifying the data plot.
-
-With that, we define $X$  as the number of null plots in a lineup, for which the $p$-value $p_{0,i}$ is smaller than $p_D$.
-
-Then $X \sim B_{m-1, E[p_D]}$, and the probability that an onlooker will pick the data plot in a given lineup is 
-\[
-P(X=0) = \left(1 - E[p_D] \right)^{m-1} = P(p_D \le p_0), \ \ \ \text{ where } p_0 = \min_{1 \le i \le m-1}  \ p_{0,i}.
-\]
-
-%\red{pull the results for $P(p_D < p_{i,0})$ and $P(p_D < p_0)$ to the front, including the figure on $1/m$ versus power.
-These results are independent of the regression setting - they don't make any assumptions in terms of regression.}
-
-Figure \ref{fig:pval_power} gives an overview of the probability of picking the data plot for lineups of different size: as $m$ increases we have an increased probability to observe a more highly structured null plot by chance.
-We see that for a $p$-value $p_D$ of about 0.15 for the data plot the signal in the plot is so weak, that we cannot distinguish the data plot from null plots in a lineup of size $m=20$.
-\red{The following sentence should be moved back} This pattern is also seen in our experiments as shown in figure \ref{fig:pval_pcorrect}.
-
-Even under $H_1$ we expect some observers to pick a null plot with a probability that depends on the strength of the signal in our data plot. 
-Reversely, we will now make use of the number of observers who do not pick the data plot in a lineup to infer the strength of the signal in the test statistic.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.5in]{images/powerplot.pdf} 
-   \caption{Comparison of probabilities to pick the data plot for different size lineups $m$ and different values for data plot strength $p_D$.
-The grey line shows probability of picking the data plot under $H_0$.
-}
-   \label{fig:pval_power}
-\end{figure}
-
-Now assume that the same lineup plot is evaluated by $K$ independent observers.
-W.l.o.g.
-let the last plot be the data plot and plots 1 through $m-1$ the null plots.
-Let $n_i$ be the number of observers who picked plot $i$ as the plot with the structure least consistent with the null hypothesis, corresponding to random variable $N_i$.
-Then  $(N_1, N_2, ..., N_m) \sim$ Mult$_{\pi_1, ..., \pi_m}$ with $\sum_i \pi_i = 1$ and $\sum_{k=1}^{m} n_k = K$.
-We can estimate $\pi_i$ as $\widehat{\pi_i} = n_i/K$.
-
-For the distribution of $N_m$, %the number of times out of $K$ that observers picked the last plot to show the structure least consistent with the null hypothesis, 
-we get
-\[
-N_m\sim \left \{ 
-\begin{array}{ll}
-B_{K, (1-E[p_D])^{m-1}} & \text { under } H_1\\
-B_{K, 1/m} & \text { under } H_0
-\end{array}
-\right .
-\]
-
-By matching the expected values, we therefore get an expression for the $p$-value in the data under $H_1$  as:
-\begin{equation}\label{eqn:power_estimate}
-{E[p_D]} = 1- \left(\frac{E[N_m]}{K}\right)^{1/(m-1)}.
-\end{equation}
-
-\blue{Note that the right hand side of equation (\ref{eqn:power_estimate}) is independent of the parameter $\theta$, but just based on the lineup evaluation by independent observers.
-While this allows us to compute this value independently of the parametric setting, it also means that onlookers might pick out the data plot for a reason not related to the value of $\theta$.
-
-%Picking out the data plot is still a measure of how different the data plot is compared to the null plots, and therefore is a test statistic of the visual test.
-
-%This allows us to compute this value independently of the parametric setting. We therefore define the {\it signal strength} of a  visual test as the following:
-%
-%\begin{dfn} \label{dfn:signal}
-%The {\it signal strength} $\sigma_T$ of a visual test is defined as the probability to identify the data plot.
-%\end{dfn}
-%
-%In a lineup of size $m$, evaluated by $K$ independent observers,  we can estimate the signal strength of the test as
-%\[
-%\sigma_T^{m-1} = \frac{n_m}{K}.
-%\]
-%
-%In a parametric setting, signal strength of a test coincides with the power of the test.
-}
-
-\red{We need to comment on how this ties in to the rest of the paper: this is a theoretical consideration based on the assumption that observers are able to spot the plot with the smallest/a small $p$-value.
-$p$ value of data plot and $p$ values from null are negatively correlated (if one is low, the other has to be higher.
-We need to address this.}
-\red{HH: should we re-run some of the lineups with different null plots?}
-
-\blue{
-\paragraph{Subject-specific power}
-Probability to reject null hypothesis is power.
-This is intricately related to the probability to identify the data plot from the lineup.
-We need to address the problematic of individual specific abilities in identifying the data plot
-}. 
-\red{HH: need to cite some literature from cognitive science here}
-
-\blue{Let $X_{j\ell} \sim B_{1, \pi_{j\ell}}$ be the random variable, with $X_{j\ell}= 1$, if  subject $j$ correctly identifies the data plot from lineup $\ell$, and 0 otherwise.
-We can model $\pi_{j\ell}$ with a logistic regression with subject specific random effects as:
-\[
-\text{logit } \pi_{j\ell} = X_\ell \beta + Z u_j,  
-\]
-where $X_\ell$ is a matrix of fixed effects with parameter vector $\beta$ corresponding to lineup $\ell$ and $u \sim MVN(0, \sigma_u I)$  is a vector of random variables $j = 1, ..., N_\ell$ for each of $N_\ell$ subjects presented with lineup $\ell$.
-}
-
-Theoretical power for the regression parameters is derived in the next section.
-\section{Inference for a Regression Model} \label{sec:regression}
-
-Consider a linear regression model 
-\begin{equation}\label{multi} Y_i = \beta_0 + \beta_1 X_{i1} + \beta_1 X_{i2} + \beta_3 X_{i1}X_{i2} + ... + \epsilon_i 
-\end{equation}
-where $\epsilon_i \stackrel{iid}{ \sim } N(0,\sigma^2)$, $i=1,2, .., n$. The covariates ($X_j, j=1,..,p$) can be continuous or discrete.
-
-Suppose $X_k$ is a categorical variable with two levels, and we test the hypothesis $H_0:\beta_k=0$ vs $H_1: \beta_k \ne 0$.
-If the responses for the two levels of the categorical variable $X_k$ in the model are significantly different and we fit the null model to the observed data, the resulting residual plot shows two groups of residuals.
-To test this we generate side-by-side boxplots of the residuals conditioned on the two levels of $X_k$, as the test statistic.
-If $\beta_k\ne 0$ the boxplots show a vertical displacement.
-
-In a regression setting, there is a multitude of established graphics that help with the evaluation and diagnostics of a model \citep{cook:99}.
-Table \ref{tbl:stat_multiple} shows an overview of some commonly used charts and their corresponding hypothesis tests.
-Note that some charts can be associated with several different testing situations.
-In our paper, we pick the examples for situation 2 and 3 as candidates.
-
-A lineup including the test statistic  for a binary $X_k$ is shown in Figure \ref{fig:test_category}.
-The 19 null plots are generated  by simulating residuals from $N(0,\hat{\sigma}^2)$.
-The test statistic, the plot containing the observed data, is randomly placed among these null plots.
-If the test statistic is identifiable the null hypothesis is rejected.
-% with a $p$-value of at most 0.05.
-
-\begin{figure}[hbt]
-%\begin{figurehere}
-   \centering
-       \scalebox{0.95}{\includegraphics{test_category.pdf}}
-       \caption{Lineup plot ($m=20$) for testing $H_0: \beta_k=0$.
-When the alternative hypothesis is true the plot of the observed data should show a vertical displacement between box plots.
-Which plot has the biggest vertical displacement between the boxplots?}
-       \label{fig:test_category}
-\end{figure}
-%\end{figurehere}
-
-\begin{table*}[hbtp] 
-\caption{Test Statistics for Testing Hypothesis Related to Model $Y_i = \beta_0 + \beta_1 X_{i1} + \beta_1 X_{i2} + \beta_3 X_{i1}X_{i2} + ... + \epsilon_i  $ } 
-\centering 
-\begin{tabular}{m{0.5cm}m{3cm}m{2.5cm}m{2.6cm}m{5.5cm}} 
-\hline\hline 
-Case & Null Hypothesis & Statistic & Test Statistic & Description \\ [0.5ex] % inserts table %heading 
-\hline 
-1 & $H_0: \beta_0=0$ & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot with least square line overlaid.
-For lineup plot, we simulate data from fitted null model.
-\\
-2 & $H_0: \beta_k=0$ & Residual plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_bet_p.pdf}} \end{center} \end{minipage} & Residual vs $X_k$ plots.
-For lineup plot, we simulate data from normal with mean 0 variance $\hat{\sigma}^2$.
-\\
-3 & $H_0: \beta_k=0$ (for categorical $X_k$) & Box plots of residuals & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.45}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} & Box plot of residuals grouped by category of $X_k$.
-For lineup plot, we simulate data from normal with mean 0 variance $\hat{\sigma}^2$.
-\\
-4 & $H_0: \beta_k=0$ (interaction with categorical $X_k$) & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.11}{\includegraphics{stat_interection.pdf}} \end{center} \end{minipage} & Scatter plot with least square lines of each category overlaid.
-For lineup plot, we simulate data from fitted null model.\\[1ex] % [1ex] adds vertical space
-5 & $H_0: X$ Linear & Residual Plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_nonlinear.pdf}} \end{center} \end{minipage} & Residual vs predictor plots with loess smoother overlaid.
-For lineup plot, we simulate residual data from normal with mean 0 variance $\hat{\sigma}^2$.
-\\
-6 & $H_0: \sigma^2=\sigma^2_0$ & Box plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.15}{\includegraphics{stat_sigma_box.pdf}} \end{center} \end{minipage} & Box plot of standardized residual divided by  $\sigma^2_0$.
-For lineup plot, we simulate data from standard normal.
-\\
-7 & $H_0: \rho_{X,Y|Z}=\rho$ & Scatter Plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot of Residuals obtained by fitting partial regression.
-For lineup plot, we simulate data (mean 0 and variance 1) with specific correlation $\rho$.
-\\
-8 & $H_0:$ Model Fits & Histogram & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.1}{\includegraphics{stat_goodness_simple.pdf}} \end{center} \end{minipage} & Histogram of the response data.
-For lineup plot, we simulate data from fitted model.
-\\[1ex] % [1ex] adds vertical space
-9 & Special case $p=1$ $H_0: \rho_{X,Y} =\rho$ & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot with least square line overlaid For lineup plot, we simulate data with correlation $\rho$.\\
-\hline 
-\end{tabular} 
-\label{tbl:stat_multiple} 
-\end{table*}
-
-%\subsection{Expected power}
-
-% Di: This is specific for the regression model
-%Consider the hypothesis test $H_0: \beta_k=0$ against $H_1: \beta_k \ne 0$ in model \ref{multi}.
-%%Now consider estimating the power of the visual test. 
-%%Suppose $F_{|t|}(.)$ is the distribution function of an absolute value of $t$.
-For the regression slope parameter $\beta$ suppose the associated test statistic in classical test be $t_{obs}$ with $p$-value $p_D$.
-By definition we have
-%%
-%%$$p_D=Pr(|t| \ge t_{obs}| H_0)=1-F_{|t|}(t_{obs}) \Rightarrow |t_{obs}|=F_{|t|}^{-1}(1-p_D)$$
-%%
-%%\red{HH: the following paragraph should probably move up, but I'm not sure how to change it appropriately. Mahbub, could you take care of that?}
-%%Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$ distribution with non-centrality parameter $\delta$. Thus the distribution function of $p-value$ be  
-%%\begin{eqnarray}\label{dist_p}
-%%F{p_D}(p) &=& Pr(p_D \le p)=1-Pr(1-p_D \le 1-p) \nonumber \\
-%%  &=& 1-Pr(F_{|t|}^{-1}(1-p_D) \le F_{|t|}^{-1}(1-p) ) \nonumber \\
-%%  &=& 1-Pr(|t_{obs}| \le F_{|t|}^{-1}(1-p)) \nonumber \\
-%%  &=&\left\{ \begin{array}{ll}
-%%          1-F_{|t|}( F_{|t|}^{-1}(1-p))=p &\mbox{ ; under $H_0$} \\
-%%          1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
-%%       \end{array} \right.     
-%%\end{eqnarray}
-%%
-%%Thus the density of $p_D$ is Uniform(0,1)  under $H_0$.
-As noted by \cite{Ruppert:2007}, under $H_1$ the density $$f_{p_D}(p_D; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_D);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_D))}$$ derived from equation \ref{dist_p}  is a right skewed distribution.
-%In a lineup plot we simulate $m-1$ residual data sets from null model where each of these $m-1$ null data sets produces a corresponding $p$-value $p_{0,i}$ and $p_{0,i} \sim \text{Uniform}(0,1)$ for $i = 1, ..., m-1$.
-Suppose  $p_0=\min_i(p_{0,i})$.
-Thus $p_0 \sim \text{Beta}(1,m-1)$.
-
-Under the assumption that an observer is able to pick the plot with the smallest $p$-value from a lineup plot,  this leads to the decision to reject $H_0$ when $p_{B} < p_0$.
-Thus we have the expected power as
-
-\begin{equation}\label{power_exp} 
-   Power(\beta)=Pr(p_{B} < p_0)  \quad \text{for}  \quad \beta \ne 0
-\end{equation}
-
-Figure \ref{fig:power_expected} shows the power of the uniformly most powerful test (UMP) in comparison to the expected power of the visual test obtained from equation \eqref{power_exp}.
-Notice that the expected power of the visual test is almost as good as the power of UMP test.
-In fact, the only loss we experience stems from comparing the test statistic to only a discrete number of  $m-1$ samples from the null distribution.
-
-%Theorem \ref{thm:power} helps to compute the expected power of visual inference.
-%\begin{thm}\label{thm:power}
-% Equation \ref{power_exp}  yields expected power of visual inference as Power($\beta$) = $E(1-p_D)^{m-1}$ .
-%\end{thm}
-% 
-%{ \em proof}
-%
-%Since $p_0 \sim \text{Beta}(1,m-1)$,  for $t \in (0,1)$ we have the distribution function of $p_0$ be
-%\begin{eqnarray*}
-%F{p_0}(t) &=& (m-1) \int_0^t{(1-p_0)^{(m-2)}dp_0} \\
-%  &=&  -(m-1) \int_1^{1-t}{x^{(m-2)}dx}\\
-%  &=& \left[ x^{m-1}\right]^1_{1-t}\\
-%  &=&1-(1-t)^{m-1} \rightarrow 1 \quad \text{as} \quad m \rightarrow \infty
-%\end{eqnarray*}
-%
-%% verified this computation from http://www.wolframalpha.com using command int (m-1)*(1-p)^(m-2) dp, p=0,t
-%
-%Thus expected power in equation \ref{power_exp} be
-%\begin{eqnarray*}
-% Pr(p_{B} < p_0) &=& 1- Pr( p_0 \le p_{B} ) \\
-%  &=& 1- \int_{0}^{1}{Pr( p_0 \le p_{B} |p_{B} =t) f_{p_{B} }(t)dt } \\
-%  &=& 1-  \int_{0}^{1}{F{p_0}(t) f_{p_{B} }(t)dt } \\
-%  &=& E(1-p_D)^{m-1}   \\
-%%  & \rightarrow &1-  \int_{0}^{1}{ f_{p_{B} }(t)dt }  = F_{p_D}(0) \quad \text{as} \quad m \rightarrow \infty
-%\end{eqnarray*}
-%
-%
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.65}{\includegraphics{power_expected.pdf}}
-       \caption{Expected power of visual test  and the power of UMP test for sample size $n =100$ and $\sigma = 12$.}
-       \label{fig:power_expected}
-\end{figure}
-
-% \pagebreak
-
-% -------- Heike's writeup added here
-
-%\subsection{Some Power Considerations}
-
-%\subsection{Expected number of choices}
-%Since $X$ has a binomial distribution, we can have a look at the number of plots among the null plots that we would expect to be picked over the data plot:
-%\[
-%E[X] = (m-1)(1-E[p_D]).
-%\]
-%With an increase of the lineup size $m$ the number of null plots with a potentially stronger signal than the data plot grows linearly.
-%This should allow us to infer some of the signal strength $p_D$ as
-%\begin{equation} \label{plot_signal}
-%E[p_D] = 1 - E[X]/(m-1),
-%\end{equation}
-%i.e.
-by averaging over the number of plots with  a stronger signal than the data plot we can evaluate signal strength of the plot even in the case where the data plot is not being picked by the observer.
-%
-
-\subsection{Estimating Power from Lineups}
-
-We estimate the empirical power from responses on a specific lineup plot  generated with known values of sample size ($n$), variance ($\sigma^2$) and regression parameter ($\beta$) in model \ref{multi}.
-Suppose, we have responses from $N$ independent observers with $u$ identifications of the observed plot.
-This gives an estimated power of
-\begin{equation}\label{power_est} Power(\beta)=\frac{u}{N} \hspace{1cm} 0 \le u \le N \end{equation}
-
-Suppose each of $N$ independent observers gives evaluations on multiple lineup plots and responses are associated with binary random variable $Y_{ij}$.
-Let $Y_{ij} = 1$, if subject $j$ correctly identifies the test statistic on lineup $i$, and 0 otherwise.
-We model $\pi_{ij} = E(Y_{ij})$ as  a mixed effects logistic regression
-
-\begin{equation}
-g(\pi_{ij}) = X_{ij}B  + Z_{ij} \tau_j 
-\label{mixed} 
-\end{equation}
-%
-where $\tau_j$ is random effects coefficient vector of length $q$ for subject $j$,  $\tau_j  \sim  MVN(0,\Sigma)$ with variance covariance matrix $\Sigma$, $Z_{ij}$ is the $i$th row vector of random effects covariates for subject $j$, $B$ is a vector of coefficient of length $p$, the number of fixed effect covariates being used, $X_{ij}$ is the $i$th row vector of the fixed effects covariates for subject $j$ and logit link function $g(\pi)=\log(\pi) - \log(1-\pi); 0 \le \pi \le 1$.
-The covariates could be demographic information of people such as age, gender, education level etc.
-as well as sample size ($n$), regression parameter ($\beta$) and variance ($\sigma^2$) of model \ref{multi}.
-
-From model \ref{mixed} we obtain %$\pi=Pr(Y=1|X_1, X_2, ..., X_p)$, 
-the power of the underlying testing procedure as a population average %by ignoring the random effect part. 
-%Thus we have the overall probability of success ($\pi$ or power) 
-for specified sample size ($n$) and  variance ($\sigma$)  as
-
-\begin{equation}\label{eqn:power} 
-Power(\beta) = \pi=Pr(Y=1|\beta, n, \sigma) 
-\end{equation}
-
-\section{Simulation Experiment} \label{sec:simulation}
-
-\subsection{Experiment with a discrete covariate}
-
-The experiment is designed to study the ability of human observers to detect the effect of a single variable $X_2$ (corresponding to parameter $\beta_2$) in a two variable ($p=2$) regression model (Equation \eqref{multi}).
-Data is simulated for different values of $\beta_2 (=0, 1, 3, 5, 7, 8, 10, 16)$, with two sample sizes ($n=100, 300$) and two standard deviations of the error ($\sigma=5, 12$).
-The set of $\beta_2$ values was chosen so that estimates of the power should produce reasonable power curves, comparable to the theoretical UMP test.
-We fixed the values of $\beta_0 = 5$,  $\beta_1=15$ and values for $X_1$ were generated as a random sample from a Poisson(30) distribution.
-Data sets with different combinations of $\beta_2$,  $n$ and $\sigma$ were generated with frequencies shown in Table \ref{tbl:experiment_params}.
-Three replicates of each level were generated.
-These produced 60 different ``observed data sets''.
-
-\begin{table}[hbtp]
-\caption{Values of parameters considered for three survey experiments} % title name of the table
-\centering
-% centering table
-\begin{tabular}{c c l l l}
-% creating 10 columns
-\hline\hline
-
-% inserting double-line
-& & \multicolumn{3}{c}{values for slope ($\beta$)} \\
- \cline{3-5}
-
-\raisebox{1.5ex}  {Sample size ($n$)} &   \raisebox{1.5ex} {$\sigma$} &  \multicolumn{1}{c} {Experiment 1}  & \multicolumn{1}{c} {Experiment 2}  & \multicolumn{1}{c} {Experiment 3}
-\\ [0.5ex]
-\hline
-% inserts single-line
-
-% Entering 1st row
-&  5 & 0, 1,  3, 5, 8  & 0.25, 0.75, 1.25, 1.75, 2.75 & 0.1, 0.4, 0.75, 1.25, 1.5, 2.25\\[-1ex]
-\raisebox{1.5ex}{100} &12
-& 1, 3, 8, 10, 16  & 0.5, 1.5, 3.5, 4.5, 6 &\\[1ex]
-
-% Entering 2rd row
-&  5 & 0, 1, 2, 3, 5  & 0.1, 0.4, 0.7, 1, 1.5&\\[-1ex]
-\raisebox{1.5ex}{300} & 12
-& 1, 3, 5, 7, 10  & 0, 0.8, 1.75, 2.3, 3.5 &\\[1ex]
-% [1ex] adds vertical space
-\hline
-% inserts single-line
-\end{tabular}
-\label{tbl:experiment_params}
-\end{table}
-
-For added control, to ensure a signal in the simulated observed data a blocking structure was used to filter data sets.
-A 1000 sets were generated for each parameter combination and the traditional $t$-statistic and $p$-value associated with $H_0: \beta_2=0$ were calculated.
-The 3 replicates were drawn from each of three blocks of $p$-values: (0.0-$q_{33}$), ($q_{33}$-$q_{66}$), ($q_{66}$-1) where $q_i$ is the $i$th percentile in the distribution of the $p$-values.
-Additional control was applied to the 19 null plots.
-Because the distribution of these $p$-values should follow a Uniform(0,1) distribution, data sets were binned on this range by $p$-value, and a data set was randomly selected from each bin.
-
-\subsection{Experiment with a continuous covariate}
-
-This experiment is designed for the same regression model (Equation \eqref{multi}) with $p=1$ and covariate $X_1$ being continuous.
-Data is simulated with two sample sizes ($n=100, 300$) and two standard deviations of the error ($\sigma=5, 12$).
-The different values for slope parameter that are used to generate data are shown in Table \ref{tbl:experiment_params}.
-We arbitrarily fix $\beta_0 = 6$ while generating observed data.
-For each combination of parameter, we generate at least three different observed data sets constituting a total of 65 lineups.
-
-\subsection{Experiment with contaminated data}
-
-The first two simulation experiments are based on normal error model which satisfies the conditions for uniformly most powerful (UMP) test.
-To study how the proposed visual inference work for a scenario where the data are not really coming from a normal model we design a contaminated data experiment.
-To generate the contaminated data set of size $n=100$ we used the following model
-
-\[
-  Y_i = \left\{
-  \begin{array}{l l}
-    5+\beta X_i + \epsilon_i  & \quad  X_i \sim N(0,1) \quad \text{ $i$ =1,...,85}\\
-    15+ \eta_i & \quad X_i \sim N(\mu,1/3) \quad  i=86,...,n\\
-  \end{array} \right.
-\]
-where $\epsilon_i \stackrel{iid}\sim N(0,\sigma)$, $\eta_i \stackrel{iid}\sim N(0,\sigma/3)$ and $\mu = -1.75$.
-One such plot of the contaminated data for $\sigma$=5 and $\beta$=5 is shown in figure \ref{fig:cont_dat}.
-For this experiment we only consider sample size $n=100$ and error standard deviation $\sigma=5$.
-
-For this experiment we generate five replications of observed data sets for each slope value shown in table \ref{tbl:experiment_params}. This produces 30 lineups.
-
-\begin{figure}[hbt]
-%\begin{figurehere}
-   \centering
-       \scalebox{0.4}{\includegraphics{contaminated_data.pdf}}
-       \caption{Scatterplot of a simulated contaminated data set generated such that a simple linear model produce a slope almost negligible, ie, if we fit model (Equation \eqref{multi}) with $p=1$  to this data, the resulting estimate of $\beta_1$ would not be statistically significant.
-}
-       \label{fig:cont_dat}
-\end{figure}
-
-\begin{figure*}[hbtp]
-   \centering
-       \scalebox{0.6}{\includegraphics{power_observed.pdf}}
-       \caption{Observed power of visual test from equation \eqref{power_est} with pointwise 95\% confidence limits and the power of UMP test for sample size $n= 100,300$ and $\sigma = 12,5$ as per experiment 1.}
-       \label{fig:power_observed}
-\end{figure*}
-
-\begin{figure*}[hbtp]
-   \centering
-       \scalebox{0.7}{\includegraphics{power_loess_exp1.pdf}}
-       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100,300$ and $\sigma = 12,5$ as per experiment 1.}
-       \label{fig:power_loess1}
-\end{figure*}
-
-\begin{figure*}[hbtp]
-   \centering
-       \scalebox{0.7}{\includegraphics{power_loess_exp2.pdf}}
-       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100,300$ and $\sigma = 12,5$ as per experiment 2.}
-       \label{fig:power_loess2}
-\end{figure*}
-
-\begin{figure*}[hbtp]
-   \centering
-       \scalebox{0.4}{\includegraphics{power_loess_exp3.pdf}}
-       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3.
-Notice that for experiment 3, power does not seem to depend on the parameter $\beta$.
-Di/Heike, I am not sure how I can relate this to demonstrate the power of visual inference when normal conditions are not met.
-Does this really test our hypothesis $H_0: \beta=0$ or some other hypothesis about the existence of cluster in the data?}
-       \label{fig:power_loess3}
-\end{figure*}
-
-\begin{figure*}[hbtp]
-   \centering
-       \scalebox{0.7}{\includegraphics{power_diff_exp.pdf}}
-       \caption{Difference of Observed power from UMP test power obtained in three experiments for sample size $n= 100,300$ and $\sigma = 12,5$ and values of slope parameter $\beta$ as shown in table \ref{tbl:experiment_params}.}
-       \label{fig:power_diff_exp}
-\end{figure*}
-
-\begin{figure*}[hbtp]
-   \centering
-       \scalebox{0.6}{\includegraphics{power_observed_exp3.pdf}}
-       \caption{Observed power of visual test from equation \eqref{power_est} with pointwise 95\% confidence limits and the power of UMP test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3.
-}
-       \label{fig:power_observed_exp3}
-\end{figure*}
-
-\begin{figure*}[hbtp]
-   \centering
-       \scalebox{0.6}{\includegraphics{p_val_percent_correct.pdf}}
-       \caption{Percentage of correct responses decreases rapidly with the increase of p-value.
-After p-value exceeds 1.5 it is very unlikely to identify the observed plot.
-The theoretical justification of this is shown in figure \ref{fig:pval_power}}
-       \label{fig:pval_pcorrect}
-\end{figure*}
-
-\begin{figure*}[hbtp]
-   \centering
-       \scalebox{0.6}{\includegraphics{p_val_plot_signal.pdf}}
-       \caption{p-value vs plot signal strength. The solid line represents 45 degree line which represents the equity shown in equation \eqref{plot_signal}}
-       \label{fig:pval_plot_signal}
-\end{figure*}
-
-Participants for all the experiments were recruited through \cite{turk} Amazon's Mechanical Turk.
-Each participant was shown a sequence of 10 lineup plots.
-Participants are asked to select the plot with the biggest vertical difference, give a reason for their choice, and determine a level of  confidence for their decision.
-Gender, age, education and geographic location of each participant are also collected.
- In total, 3629 lineups were evaluated by 324 people coming from many different locations across the globe.
-The results of the experiment are summarized in Figure \ref{fig:power_observed} which shows the observed power from the survey data calculated using equation \eqref{power_est} along with 95\% confidence interval calculated using Fisher's exact method.
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{0.40}{\includegraphics{power_model.pdf}}
-       \caption{Estimated power curve from equation \eqref{eqn:power} along with 95\% confidence interval for sample size $n$ = 100 and $\sigma$ = 12.
-The corresponding power curve for Uniformly Most powerful (UMP) test is shown for comparison.}
-       \label{fig:power_model}
-\end{figure}
-
-We fit model \eqref{mixed} to the survey data obtained from the simulation experiment.
-The estimated overall power curve obtained from equation \eqref{eqn:power} is shown in Figure \ref{fig:power_model}.
-Model \ref{mixed} also gives the subject specific power curves shown in Figure \ref{fig:power_subject}.
-The plot includes 20 randomly selected subject-specific power curves.
-Notice that the power curve estimated for one subject is above the UMP test power curve.
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{0.45}{\includegraphics{power_subject.pdf}}
-       \caption{Estimated subject specific power curve from model \ref{mixed} for sample size $n$ = 100 and $\sigma$ = 12.
-The corresponding power curve for Uniformly Most powerful (UMP) test is shown for comparison.}
-       \label{fig:power_subject}
-\end{figure}
-
-\section{Conclusions}
-
-The purpose of this paper has been to examine the effectiveness of visual inference methods in direct comparison to existing inference methods.
-We need to be clear that this is not the purpose of visual inference generally: visual methods should not be seen as competitors to traditional inference.
-The purpose here, is to  establish properties and  efficacy of visual testing procedures in order to use them in situations where traditional tests cannot be used.
-For this experiment the effect of $\beta_2$ was examined using side-by-side boxplots.
-Future experiments will be conducted to compare other regression parameters as described in Table \ref{tbl:stat_multiple} and assess sensitivity of power to modeling conditions.
-
-\paragraph{Acknowledgement:}
-
-This work was funded by National Science Foundation grant DMS 1007697.
-
-%\bibliographystyle{plain}
-%\bibliographystyle{plainnat}
-\bibliographystyle{asa}
-%\bibliographystyle{ieeetr}
-\bibliography{references}
-
-%\end{multicols}
-
-\end{document}  %End of document.
-
-\begin {abstract} 
-Statistical graphics play a crucial role in exploratory data analysis, model checking and diagnosis.
-Until recently there were no formal visual methods in place for determining statistical significance of findings.
-This changed, when Buja et al.(2009) conceptually introduced two protocols for formal tests of visual findings.
-In this paper we take this a step further by comparing the lineup protocol (Buja et al.2009) against classical statistical testing  of the significance of regression model parameters.
-A human subjects experiment is conducted using simulated data to provide controlled conditions.
-Results suggest that the lineup protocol provides results equivalent to the uniformly most powerful (UMP) test and for some scenarios yields better power than the UMP test.
-\end {abstract}
-
-\end{document}

### 2013-06-12 paper_turk.tex
reorganizing the paper

@@
 
+\subsection{Test and Training Lineup} How many test lineup?
+
+How to setup training, randomized or sequential selection of lineup for training.
+
+Example lineup on the homepage should be of size three or four so that more than one lineup can be placed on the homepage.
+
+\subsection{Planing the Turk Task}
+Question to ask
+
+Whether reasoning would be collected or not
+
+Multiple or single response
+
+Test plot added or not
+
+Training needed or not
+
+Feedback given after every evaluation or not
+
+How many lineups to show
+
+Are the lineups randomly selected?
+
 \section{Web Application for Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.
@@
 This has allowed us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site to transfer data to our server.
+
+\subsection{Form Design}
+
+\subsection{Database design} The design of the database to store the collected data is shown in Figure \ref{fig:turk_database_design}.
+It is designed such a way that data from many different experiments can be stored in the same database.
+In total five separate tables are used.
+Table turk\_worker contains static information about each turk worker.
+The location information of each turk worker is stored in ip\_detals table.
+The information in this table is collected later based on the ip address of each turk worker.
+Table picture\_delais contains the static information about each lineup.
+Table feedback is a dynamic table that grows with the number of feedbacks from each turk user.
+The multiple activities of each turk user are recorded in turk\_activity table.
+This table also contains the codes provided to the user once they finish the experiment.
+For our web site we used MySQL database located on a local server.
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_database_design.pdf}}
+       \caption{Database design for Turk experiment data collection.
+The same database can be used for multiple turk experiments by keeping experiment information in picture details table which contains information about the lineups.}
+       \label{fig:turk_database_design}
+\end{figure}
 
@@
 
-\subsection{Database design} The design of the database to store the collected data is shown in Figure \ref{fig:turk_database_design}.
-It is designed such a way that data from many different experiments can be stored in the same database.
-In total five separate tables are used.
-Table turk\_worker contains static information about each turk worker.
-The location information of each turk worker is stored in ip\_detals table.
-The information in this table is collected later based on the ip address of each turk worker.
-Table picture\_delais contains the static information about each lineup.
-Table feedback is a dynamic table that grows with the number of feedbacks from each turk user.
-The multiple activities of each turk user are recorded in turk\_activity table.
-This table also contains the codes provided to the user once they finish the experiment.
-For our web site we used MySQL database located on a local server.
+\subsection{Data Security and Validity} Consideration to avoid hacking
 
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.4}{\includegraphics{turk_database_design.pdf}}
-       \caption{Database design for Turk experiment data collection.
-The same database can be used for multiple turk experiments by keeping experiment information in picture details table which contains information about the lineups.}
-       \label{fig:turk_database_design}
-\end{figure}
+Check for invalid input
+
+Control for missing imput
 
@@
 These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.
+
+\subsection{Creating Task for Lineup Evaluation} Task description, number of people to recruit, time allowed to finish the task, specify the qualification needed, setting the duration of the task, offering the pay per task.
+
+\subsection{Accepting or Rejecting the Task} In our design we keep a test lineup plot which is very easy to evaluate.
+The general criteria may be to reject payment when workers do not get that easy test lineup plot.
+Our experience suggest that there are workers who did not get that test plot but their overall success rate is very high.
+So depending on only one criteria the payment should not be made.
+These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.
+
+\subsection{Processing Payment}Amazon Mechanical Turk suggest that each worker gets \$6/hour as wage.
+Thus we need to estimate how much time a tusk may take to complete and based on that we have to specify the payment for each task.
+Our experience indicates that a better payment lures more serious workers who usually provide cleaner data which is more reliable.
+We may study this issue while we do multiple turk experiments.
+
+\subsection{Managing Worker} pay bonus, appreciate worker by sending email, block worker etc.
+
+\section{Turk Data Quality}
+
+In this section we intend to analyze the performance of the experiments we did using Amazon Mechanical turk.
+We have feed back data for the similar plots from both turk workers as well as from the people who regularly participates in the graphics group meeting of our department.
+We consider later participants as more knowledgeable and trained in seeing pattern in statistical plots.
+We can use these data to evaluate the performance of the general participants from around the world.
 
@@
 
-\subsection{Wage Rate for the Turkers}Amazon Mechanical Turk suggest that each worker gets \$6/hour as wage.
-Thus we need to estimate how much time a tusk may take to complete and based on that we have to specify the payment for each task.
-Our experience indicates that a better payment lures more serious workers who usually provide cleaner data which is more reliable.
-We may study this issue while we do multiple turk experiments.
+\subsection{Data Cleaning}
 
-\subsection{Accepting or Rejecting Payments for Turk Evaluation} In our design we keep a test lineup plot which is very easy to evaluate.
-The general criteria may be to reject payment when workers do not get that easy test lineup plot.
-Our experience suggest that there are workers who did not get that test plot but their overall success rate is very high.
-So depending on only one criteria the payment should not be made.
-These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.
+\subsection{Diversity in the Data}
 
-\section{What do people pick, $R^2$ or p-value?} What do people pick in a lineup plot, p-value or $R^2$?
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.5}{\includegraphics{turker_country.pdf}}
+       \scalebox{.5}{\includegraphics{turker_location.pdf}}       
+       \caption{The location of turk workers on the world map shows the geographical diversity of turk workers even though most of the workers come from India and United States.}
+       \label{fig:rsq}
+\end{figure}
+
+\subsection{Selection Bias} Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did.
+In this section we intend to analyze to what extent this selection bias has occurred and how we can adjust for this.
+
+Time of the task may recruit from a specific geographical location
+
+Setting up qualification may allow certain workers to do the task
+
+Payment amount may affect the duration of the experiment which may avoid diversity in the geographical locations.
+
+\section{Conclusion}
+
+\section{Appendix: What do Turk Workers Pick, $R^2$ or $p$-value?} What do people pick in a lineup plot, p-value or $R^2$?
 To address this issue we obtain the approximate theoretical relationship between $R^2$ and the power of the classical hypothesis test.
@@
 
-\section{Performance} In this section we intend to analyze the performance of the experiments we did using Amazon Mechanical turk.
-We have feed back data for the similar plots from both turk workers as well as from the people who regularly participates in the graphics group meeting of our department.
-We consider later participants as more knowledgeable and trained in seeing pattern in statistical plots.
-We can use these data to evaluate the performance of the general participants from around the world.
-
-\section{Quality of Turk Data}
-
-\subsection{Data Cleaning}
-
-\subsection{Diversity in the Data}
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.5}{\includegraphics{turker_country.pdf}}
-       \scalebox{.5}{\includegraphics{turker_location.pdf}}       
-       \caption{The location of turk workers on the world map shows the geographical diversity of turk workers even though most of the workers come from India and United States.}
-       \label{fig:rsq}
-\end{figure}
-
-\subsection{Selection Bias} Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did.
-In this section we intend to analyze to what extent this selection bias has occurred and how we can adjust for this.
-
-\section{Conclusion}
-
 \bibliographystyle{plain}

### 2013-06-12 paper_turk.tex
conclusion started

@@
    \centering
-       \scalebox{.4}{\includegraphics{turk_web.png}}
-       \caption{A sample data collection form. Lineups are presented at random for evaluations by the turk workers.}
+       \scalebox{.4}{\includegraphics{turk_web.pdf}}
+       \caption{A sample data collection form.
+Lineups are presented at random for evaluations by the turk workers.
+Scalable Vector Graphics (SVG) is used so that observer can click on the lineup to pick certain plot.}
        \label{fig:turk_web}
@@
 
-\section{Conclusion}
+\section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated.
+The proposed online application design provides flexibility to control how the multiple lineups would be presented to a observer.
+It also gives added benefit to record timing of the evaluations.
+Scalable Vector Graphics (SVG) is used so that observer can click on the lineup to pick certain plot.
+This also made the multiple plot selection from a lineup easier and convenient.
+Multiple online experiments are done using this web application and result suggests that the application worked as planned.
+
+The web application is designed such a way that it still produces simple task for the worker who are used to doing so from MTurk.
+But it gives many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement.
 

### 2013-06-12 paper_turk.tex
updated introduction

@@
 \usepackage{url}
+\RequirePackage{natbib}
 \usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}
@@
 
-The power of visual test is studied by Majumder \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better.
+The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better.
 But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.
@@
 There are some reasons a researcher needs to evaluate lineups.
-One is to assess the power of the visual test \cite{heike:2012} for different visual test statistics.
-The another reason would be to make decision based on the lineup, i.e., to use lineup protocol in practical application \cite{niladri:2012}.
+One is to assess the power of the visual test \citep{heike:2012} for different visual test statistics.
+The another reason would be to make decision based on the lineup, i.e., to use lineup protocol in practical application \citep{niladri:2012}.
 Other reasons could be to present the results of the conventional test with visual tools such as lineup.
@@
 
-The power of visual test can be obtained theoretically \cite{majumder:2013} under some conditions.
+The power of visual test can be obtained theoretically under some assumptions on individual behavior which was evident from experimental studies \citep{majumder:2013}.
 In general it is hard to obtain explicitly with a mathematical formula since it is very much dependent on individual observation.
-One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}.
-It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.
+One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation.
+Individual differences in the abilities of correct evaluations of lineup were observed.
+But Observer's education levels do not seem to have significant effect on performances.
+Thus it is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.
+
+This poses a new challenge to researcher to recruit people from a diverse pool of population.
+Cost, time, data accuracies and convenience are some of the issues that need to be dealt with.
+Moreover, those who need to make statistical decision based on lineup plot will need a system that could provide an easy solution to this challenge.
+This paper provides a complete solution to this by presenting plans for experimental design, developing an web application to recruit people from Amazon Mechanical Turk (MTurk) web site and providing detailed task management while doing an experiment through MTurk.
 
@@
 \cite{mason:2012} explains various features of MTurk and describes how it can be used as part of human behavioral study.
+
+\subsection{Getting Turk Workforce}
 
@@
 But it gives many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement.
+The design of this application allows recruiting people from any source not necessarily just from MTurk.
+Also once the application is hosted, any number of experiments can be done through this without changing the core of this application.
+
+The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their need and run the MTurk experiments as part of their research that involves lineups.
+This would save lot of time which researcher can use focusing on their actual research.
+This would also help lineup protocol to be used frequently since it would provide an ease of its use in making inferential decisions.
+
+We also intend to set up a web application for public use where researcher can put their lineup for online evaluation.
+The observer could be recruited from MTurk or any other source including local lab participants.
 
@@
 
-\bibliographystyle{plain}
+%\bibliographystyle{plain}
+\bibliographystyle{asa}
 \bibliography{references}

### 2013-06-12 paper_turk.tex
lineup added to introduction

@@
 The rest of the plots in the lineups are generated from the model specified by the null hypothesis.
-A human observer is then asked to evaluate the lineup.
+A human observer is asked to evaluate the lineup.
 If the observer detects the actual plot in the lineup, the null hypothesis is rejected.
 
-The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better.
+A lineup is shown in Figure~\ref{fig:lineup_turk} where the observed scatterplot is displayed with a least square line overlaid.
+Can you find which of these plots show the steepest slope?
+The rest of the plots or the null plots are generated based on the hypothesis that the slope is zero.
+If the observed scatterplot is detected that indicates that observed plot is different from null plot and hence the null hypothesis is rejected.
+
+\begin{figure}[htbp] 
+   \centering
+   \includegraphics[width=6.5in]{plot_turk2_100_450_12_3.png} 
+   \caption{A lineup of 20 plots. Which of these plots shows the steepest slope?.}
+   \label{fig:lineup_turk}
+\end{figure}
+
+The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and in some scenerios even better.
 But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.
@@
 This poses a new challenge to researcher to recruit people from a diverse pool of population.
-Cost, time, data accuracies and convenience are some of the issues that need to be dealt with.
+Cost, time, data qualities and convenience are some of the issues that need to be dealt with.
 Moreover, those who need to make statistical decision based on lineup plot will need a system that could provide an easy solution to this challenge.
@@
 
+Human observers were recruited to evaluate the experimental lineups through
+
 \subsection{Amazon Mechanical Turk (MTurk)}
 
-Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments.
-This is the place where people come to work online and get paid.
-The web site is very convenient and reliable to collect simple experiment data.
-But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work.
-So, to run the turk experiment we felt the necessity for a well customized web site where the lineups presented to the observers could be easily controlled according to the experimental design.
-The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}.
-The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site.
-This facilitates getting data directly in a local server.
-
-Figure \ref{fig:amazon_task} displays an example of such a task taken from their web site.
-In this task a worker just has to select from a pool of options and submit the task.
-The instructions are usually accompany the task and they are very simple and easy to follow.
+\cite{turk} Mechanical Turk  or MTurk is an online work place where people from around the world can perform some tasks and get paid.
+Usually tasks are very simple and no specialized training is required.
+Being a human is the main requirement.
+Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters' need.
+The tasks are designed such that it does not take much time to complete.
+Humans are still better than computers in performing these types of tasks.
+The the amount of money paid for each task is very small as well.
+Figure~\ref{fig:amazon_task} shows an MTurk task where an observer is asked to select from some given options based on a picture.
 
@@
 \end{figure}
-
-Human observers were recruited to evaluate the experimental lineups through Amazon Mechanical Turk \cite{turk} or MTurk Web site.
-It is an online work place where people from around the world can perform some tasks and get paid.
-Usually tasks are very simple and no specialized training is required.
-Being a human is the main requirement.
-Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters need.
-The tasks are designed such that it does not take much time to complete.
-Humans are still better than computers in performing these types of tasks.
-The the amount of money paid for each task is very small as well.
 
@@
 Because of its convenience it is getting popular for scientific research study as well.
-In comparison with a lab study \cite{suri:2010} perform the same study using MTurk and demonstrate that their study results are as good as the lab study results even though MTurk study required less time and cost while provided more convenience.
+In comparison with a lab study \cite{suri:2010} performed the same study using MTurk and demonstrated that their study results are as good as the lab study results even though MTurk study required less time and cost while provided more convenience.
 \cite{majumder:2013} recruited people from MTurk for their simulation study in estimating the power of visual statistical inference.
@@
 \cite{mason:2012} explains various features of MTurk and describes how it can be used as part of human behavioral study.
+
+Figure \ref{fig:amazon_task} shows how simple an MTurk task could be.
+It is possible to get a lineup evaluated by creating such a simple task.
+We just need to replace the picture in Figure \ref{fig:amazon_task} with the lineup in Figure \ref{fig:lineup_turk} and change the answering options.
+But some times we may need more than one lineups to be evaluated by an observer.
+There could be many lineups from which a small number lineups needs to be shown to an observer.
+All these could be done by creating a web application.
+For additional control we plan to separate this application from MTurk system.
+The following section discuss this in details.
+
+%Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments.
+This is the place where people come to work online and get paid.
+The web site is very convenient and reliable to collect simple experiment data.
+But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work.
+So, to run the turk experiment we felt the necessity for a well customized web site where the lineups presented to the observers could be easily controlled according to the experimental design.
+The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}.
+The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site.
+This facilitates getting data directly in a local server.
+
+%Figure \ref{fig:amazon_task} displays an example of such a task taken from their web site.
+In this task a worker just has to select from a pool of options and submit the task.
+The instructions are usually accompany the task and they are very simple and easy to follow.
 

### 2013-06-12 paper_turk.tex
paper layout

@@
 There could be many lineups from which a small number lineups needs to be shown to an observer.
+It is convenient if the lineup is clickable so that selection of plot can be made by mouse click.
 All these could be done by creating a web application.
@@
 \end{figure}
+
+This paper is organized as follows.
+Section \ref{sec:turk_exp} presents the details description of an experiment and things to consider before a turk experiment.
+Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not possible through MTurk.
+Section \ref{sec:turk_task} describes how to create a MTurk task, mange workers and process payments.
+Finally Section \ref{sec:turk_data} presents some data obtained from various experiments done through the proposed web application and discusses about the quality of the data.
 
@@
 
-\section{Web Application for Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.
+\section{Web Application for Turk Experiment} \label{sec:web_application}
+
+We developed a web site to run the Amazon Mechanical Turk experiments.
 PHP scripting language is used and embedded with HTML for designing the web site.
@@
 
-\section{Managing Turk Task} Turk workers are usually small payee workers.
+\section{Managing Turk Task}\label{sec:turk_task}
+
+Turk workers are usually small payee workers.
 There several issues related to the payment of their effort.
@@
 
-\section{Turk Data Quality}
+\section{Turk Data Quality} \label{sec:turk_data}
 

### 2013-06-13 paper_turk.tex
introduction completed

@@
 \setlength{\textwidth}{6.5in}
-%\setlength{\topmargin}{-0.4in}
-\setlength{\textheight}{8in}
+\setlength{\topmargin}{-0.3in}
+\setlength{\textheight}{8.8in}
+
+%\setlength{\evensidemargin}{0.25 in}
+%\setlength{\textwidth}{6.2 in}           % allow for a little sloppiness (6.3)
+%\setlength{\topmargin}{-.30 in}           % top margin to header (was -.35)
+%\setlength{\textheight}{8.8 in}
 
@@
    \includegraphics[width=6.5in]{plot_turk2_100_450_12_3.png} 
-   \caption{A lineup of 20 plots. Which of these plots shows the steepest slope?.}
+   \caption{A lineup of 20 scatter plots with least square line overlaid. Which of these plots shows the steepest slope?.}
    \label{fig:lineup_turk}
@@
 Cost, time, data qualities and convenience are some of the issues that need to be dealt with.
-Moreover, those who need to make statistical decision based on lineup plot will need a system that could provide an easy solution to this challenge.
+Moreover, those who need to make statistical decision based on lineup plot will need a system that can provide an easy solution to this challenge.
 This paper provides a complete solution to this by presenting plans for experimental design, developing an web application to recruit people from Amazon Mechanical Turk (MTurk) web site and providing detailed task management while doing an experiment through MTurk.
@@
 It is very fast, cheap and reliable to recruit people from MTurk.
+It allows distributing works to the thousands of workers around the world.
 Thats why it is getting very popular among the researchers who perform human subject experiment.
@@
 Usually recruiters pay promptly after the task has been done properly and thats why MTurk is very popular among the online job seeker.
-At any point of time thousands of tasks are available for the thousands of workers around the world.
 
@@
 But some times we may need more than one lineups to be evaluated by an observer.
-There could be many lineups from which a small number lineups needs to be shown to an observer.
-It is convenient if the lineup is clickable so that selection of plot can be made by mouse click.
-All these could be done by creating a web application.
-For additional control we plan to separate this application from MTurk system.
-The following section discuss this in details.
+We may need to show a random sample of lineups from a pool of many lineups automatically.
+The questions the observer would answer while examining the lineup can be different based on different lineup.
+Moreover, It is convenient if the lineup is clickable so that selection of plot can be made by mouse click.
+All these are done by creating a web application.
+The following section discusses this in details.
 
@@
 
-We designed and developed a web site which enables to display the lineups to the observers as per experimental design.
-The MTurk workers were redirected to the web site and the data were collected, stored automatically into a local database server.
-Demographic informations such as age group, gender and education levels were also collected.
-The time taken for each evaluation is computed based on the time the plot was shown and the time the feedback was received.
-The location of the observer is determined by the ip address of the observer.
+There are two options to run the web application; one is to run it inside MTurk system using their API and the other is to develop a new web site.
+For additional control we picked the second option and planned to separate this application from MTurk system and designed our own web site to run the application.
+It enables to display the lineups to the observers with a lot of flexibilities.
+As an added benefit the data can be directly saved in a local database server instead of getting it from MTurk.
 
-As shown in figure \ref{fig:turk_work_flow} turk workers have to visit the experimental web site and give their consent to participate the survey as per IRB requirement.
-In the experimental web, there is a option for observers to try some sample lineups to get familiar with the experiment.
-Once the observers start evaluating the lineups they are sequentially shown a specific number of lineups and at the end they are given a code as a proof for their tusk completion.
-The payment of the turk worker is processed if they post the code they got from experimental web site.
-The observers are also asked to provide some demographic information about them to make sure that the code is generated.
+Figure \ref{fig:turk_work_flow} shows how the plan works.
+First an MTurk task is created for the workers to see and decide whether they want to do the task based on the parameters like payment amount, estimated time the task may take to finish, how hard the task seems to be etc.
+Workers are informed that the task has to be done outside the MTurk system from another web site.
+Once the workers accept the task they are redirected to our web site where multiple lineups are shown for evaluations.
+After the required number of evaluations has been received, a code is generated which the workers has to submit back in MTurk system to complete the task.
+The code is matched with the code in our database to process payment through MTurk system.
 
@@
        \scalebox{.4}{\includegraphics{turk_work_flow.pdf}}
-       \caption{Amazon Mechanical Turk workflow and data collection.}
+       \caption{Amazon Mechanical Turk workflow shows how data are collected through turk experiment web and payment is processed through MTurk system.}
        \label{fig:turk_work_flow}
@@
 
-This paper is organized as follows.
-Section \ref{sec:turk_exp} presents the details description of an experiment and things to consider before a turk experiment.
+This paper is organized the way a researcher may work with lineup and get feedback data from the observer.
+Section \ref{sec:turk_exp} presents the details description of an experiment with lineups and things to consider before a turk task.
 Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not possible through MTurk.
-Section \ref{sec:turk_task} describes how to create a MTurk task, mange workers and process payments.
+Section \ref{sec:turk_task} describes how to create an MTurk task, mange workers and process payments.
 Finally Section \ref{sec:turk_data} presents some data obtained from various experiments done through the proposed web application and discusses about the quality of the data.
 
-\section{Experimental Design} \label{sec:turk_exp}
+\section{Experiment Design} \label{sec:turk_exp}
 
@@
 \subsection{Form Design}
-
-\subsection{Database design} The design of the database to store the collected data is shown in Figure \ref{fig:turk_database_design}.
-It is designed such a way that data from many different experiments can be stored in the same database.
-In total five separate tables are used.
-Table turk\_worker contains static information about each turk worker.
-The location information of each turk worker is stored in ip\_detals table.
-The information in this table is collected later based on the ip address of each turk worker.
-Table picture\_delais contains the static information about each lineup.
-Table feedback is a dynamic table that grows with the number of feedbacks from each turk user.
-The multiple activities of each turk user are recorded in turk\_activity table.
-This table also contains the codes provided to the user once they finish the experiment.
-For our web site we used MySQL database located on a local server.
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.4}{\includegraphics{turk_database_design.pdf}}
-       \caption{Database design for Turk experiment data collection.
-The same database can be used for multiple turk experiments by keeping experiment information in picture details table which contains information about the lineups.}
-       \label{fig:turk_database_design}
-\end{figure}
-
-\subsection{Data collection} To collect the survey data we developed a web site that shows a plot to an individual and get feedback from that individual.
-Each individual is asked to provide feedback for at least 10 different plots.
-The 10 plots that are shown to an individual are randomly chosen with probability proportional to the number of responses required (the sample size) for that plot.
-
-The information collected from each individual is shown in table \ref{tbl:data_info}.
-Data received from each individual are automatically saved in a secured mysql server maintained by the department of statistics, Iowa state university.
-
-\begin{table}[hbtp]
-\caption{Information Collected from Each Individual}
-\centering 
-\begin{tabular}{lp{8cm}} 
-\hline
-Information &  Description \\ %[0.5ex] % inserts table %heading 
-\hline
-Identification & Nick name or any ID to determine the responses of an Individual \\
-Response number & The number of the plot on the lineup plot which the individual thinks the most different than other 19 plots.\\ 
-Reason of of choice & Reason why the individual chooses the plot \\
-Confidence level & Confidence level of individual choice \\ 
-Age group& The age group where the individual belongs \\
-Education & The highest level of education completed \\
-Gender & Male or female \\
-Geographic Location & This information is collected through the ip address of the individual computer \\ 
-Time taken & Time taken for each feed back\\
-\hline
-\end{tabular}
-\label{tbl:data_info}
-\end{table}
-
-\subsection{Data collection sequence} Once turk users are directed to our web site, they can see the detailed explanation on how they can perform the task of evaluation.
-Some simple examples are displayed along with correct responses.
-The users have options to try some test lineups before going for the actual experiment.
-But before that they have to provide the informed consent as per IRB requirement.
-The flow chart for this is shown in Figure \ref{fig:turk_data_flow}
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.4}{\includegraphics{turk_data_flow.png}}
-       \caption{Data collection work flow. Turk worker can try some test lineups before going to the live experiment after providing informed consent.}
-       \label{fig:turk_data_flow}
-\end{figure}
-
 Two web forms are designed to collect information from the turk users.
@@
        \label{fig:turk_web_feedback}
+\end{figure}
+
+\subsection{Database design} The design of the database to store the collected data is shown in Figure \ref{fig:turk_database_design}.
+It is designed such a way that data from many different experiments can be stored in the same database.
+In total five separate tables are used.
+Table turk\_worker contains static information about each turk worker.
+The location information of each turk worker is stored in ip\_detals table.
+The information in this table is collected later based on the ip address of each turk worker.
+Table picture\_delais contains the static information about each lineup.
+Table feedback is a dynamic table that grows with the number of feedbacks from each turk user.
+The multiple activities of each turk user are recorded in turk\_activity table.
+This table also contains the codes provided to the user once they finish the experiment.
+For our web site we used MySQL database located on a local server.
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_database_design.pdf}}
+       \caption{Database design for Turk experiment data collection.
+The same database can be used for multiple turk experiments by keeping experiment information in picture details table which contains information about the lineups.}
+       \label{fig:turk_database_design}
+\end{figure}
+
+\subsection{Data collection} To collect the survey data we developed a web site that shows a plot to an individual and get feedback from that individual.
+Each individual is asked to provide feedback for at least 10 different plots.
+The 10 plots that are shown to an individual are randomly chosen with probability proportional to the number of responses required (the sample size) for that plot.
+
+The MTurk workers were redirected to the web site and the data were collected, stored automatically into a local database server.
+Demographic informations such as age group, gender and education levels were also collected.
+The time taken for each evaluation is computed based on the time the plot was shown and the time the feedback was received.
+The location of the observer is determined by the ip address of the observer.
+
+Figure \ref{fig:turk_work_flow} turk workers have to visit the experimental web site and give their consent to participate the survey as per IRB requirement.
+In the experimental web, there is a option for observers to try some sample lineups to get familiar with the experiment.
+Once the observers start evaluating the lineups they are sequentially shown a specific number of lineups and at the end they are given a code as a proof for their tusk completion.
+The payment of the turk worker is processed if they post the code they got from experimental web site.
+The observers are also asked to provide some demographic information about them to make sure that the code is generated.
+
+The information collected from each individual is shown in Table \ref{tbl:data_info}.
+Data received from each individual are automatically saved in a secured mysql server maintained by the department of statistics, Iowa state university.
+
+\begin{table}[hbtp]
+\caption{Information Collected from Each Individual}
+\centering 
+\begin{tabular}{lp{8cm}} 
+\hline
+Information &  Description \\ %[0.5ex] % inserts table %heading 
+\hline
+Identification & Nick name or any ID to determine the responses of an Individual \\
+Response number & The number of the plot on the lineup plot which the individual thinks the most different than other 19 plots.\\ 
+Reason of of choice & Reason why the individual chooses the plot \\
+Confidence level & Confidence level of individual choice \\ 
+Age group& The age group where the individual belongs \\
+Education & The highest level of education completed \\
+Gender & Male or female \\
+Geographic Location & This information is collected through the ip address of the individual computer \\ 
+Time taken & Time taken for each response\\
+\hline
+\end{tabular}
+\label{tbl:data_info}
+\end{table}
+
+\subsection{Data collection sequence} Once turk users are directed to our web site, they can see the detailed explanation on how they can perform the task of evaluation.
+Some simple examples are displayed along with correct responses.
+The users have options to try some test lineups before going for the actual experiment.
+But before that they have to provide the informed consent as per IRB requirement.
+The flow chart for this is shown in Figure \ref{fig:turk_data_flow}
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_data_flow.png}}
+       \caption{Data collection work flow. Turk worker can try some test lineups before going to the live experiment after providing informed consent.}
+       \label{fig:turk_data_flow}
 \end{figure}
@@
 \centering
+\scalebox{0.9}{
 \begin{tabular}{rlrrrrrrr}
@@
 \end{tabular}
+}
 \label{tbl:mturk}

### 2013-06-13 paper_turk.tex
reference updated

@@
 The technical design of the underlying experiment for visual inference may be complex and the tools available to design this from MTurk is just too simple.
-In this paper we present an alternative way to conduct the survey on lineups by designing a separate web application and getting turk worker do their job from this web site.
-The web site is now hosted and has been in use and multiple experiments were already done.
+In this paper we describe how to design MTurk experiments, present an alternative way to conduct the survey on lineups by designing a separate web application and getting turk worker do their job from this web site.
+The web site is now hosted on the Iowa State University public domain and has been in use for multiple experiments \citep{majumder:turk}.
 It turns out to be a very efficient way of getting lineups evaluated by online observers.
 Getting results from this web site is very convenient and secure.
-This paper also describes how to design MTurk experiments.
 
@@
 Cost, time, data qualities and convenience are some of the issues that need to be dealt with.
-Moreover, those who need to make statistical decision based on lineup plot will need a system that can provide an easy solution to this challenge.
-This paper provides a complete solution to this by presenting plans for experimental design, developing an web application to recruit people from Amazon Mechanical Turk (MTurk) web site and providing detailed task management while doing an experiment through MTurk.
-
-Human observers were recruited to evaluate the experimental lineups through
+Fortunately, we can use the services of Amazon Mechanical Turk web site for this.
 
@@
 
-This paper is organized the way a researcher may work with lineup and get feedback data from the observer.
+MTurk will provide workers who are used to doing simple task.
+Thus, for lineups to be evaluated a simple task needs to be created through MTurk.
+But People who need to make statistical decision based on lineup will need a system that can provide an easy solution to this challenge.
+This paper provides a complete solution to this.
+This paper is organized the way a researcher may work with lineup and like to get feedback data from the observer.
 Section \ref{sec:turk_exp} presents the details description of an experiment with lineups and things to consider before a turk task.
@@
 Section \ref{sec:turk_task} describes how to create an MTurk task, mange workers and process payments.
-Finally Section \ref{sec:turk_data} presents some data obtained from various experiments done through the proposed web application and discusses about the quality of the data.
+Finally Section \ref{sec:turk_data} presents some data obtained from various experiments done through the web application and discusses about the quality of the data.
 
@@
 
-\subsection{Selecting Parameter of Simulation Experiment} The first consideration for a simulation experiment is to fix the parameters of the model of interest.
+If a lineup is already created from observed data, the web application presented in Section \ref{sec:web_application} can be used to evaluate it.
+In this scenario we do not need to design an experiment.
+This section will be useful when a simulation experiment is needed to examine different plot types as test statistics and compare the power of visual test \citep{majumder:2013}.
+To examine the effectiveness of certain plots in displaying the data one might want to design an experiment with lineup \citep{heike:2012}.
+In any cases, two major considerations are choice of parameters to simulate lineup and number of people needed to be recruited to evaluate a lineup.
+
+\subsection{Selecting Parameter to Simulate Lineup} The first consideration for a simulation experiment is to fix the parameters of the model of interest.
 The very first consideration is the sample size.
@@
 
-\subsection{Sample size estimation} For a given proportion $p$ we want to have margin of error (ME) to be 0.1.
-Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$ Now from the theoretical power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the sample size required for that specific combinations of parameter.
-We collect data such that each of the parameter combinations in the table \ref{tbl:experiment_params} has approximately the estimated sample size that we calculated here.
-
-\subsection{Procedure to simulate plots for survey} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from model of interest for prespecified parameters.
+\subsection{Procedure to Simulate Data Plot} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from model of interest for prespecified parameters.
 We call this data set observed data.
@@
 
+\subsection{Sample size estimation} For a given proportion $p$ we want to have margin of error (ME) to be 0.1.
+Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$ Now from the theoretical power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the sample size required for that specific combinations of parameter.
+We collect data such that each of the parameter combinations in the table \ref{tbl:experiment_params} has approximately the estimated sample size that we calculated here.
+
 \subsection{Test and Training Lineup} How many test lineup?
@@
 
-We developed a web site to run the Amazon Mechanical Turk experiments.
+A web site is developed to get lineups evaluated by human observers \citep{majumder:turk}.
+It provides all the features needed for a simulation experiment with lineups but yet remains simple for the online workers.
+This section describes the technical details of the site.
+
+The web application is built using server side scripting language PHP embedded in HTML.
+JavaScript is used to control the client side work flow such as preventing missing information, showing messages etc.
+MySQL database is used to store data for dynamic presentation of lineup and recording observer feedbacks.
+The application also records the ip address of the observer's machine and the time of each display of lineup and its evaluation.
+
+%We developed a web site to run the Amazon Mechanical Turk experiments.
 PHP scripting language is used and embedded with HTML for designing the web site.
@@
 \subsection{Form Design}
-Two web forms are designed to collect information from the turk users.
+
+Designing a data collection form is very critical in turk experiments.
+As we see from Figure \ref{fig:amazon_task} that a turk task needs to be as simple as possible.
+This is what the turk workers are prepared for.
+Making a complex form may turn out bad and jeopardize the whole purpose of the experiment.
+
+Keeping these in mind, two web forms are designed to collect information from the turk workers.
 The first form shown in Figure \ref{fig:turk_web} collects feedback information about a single lineup.
@@
 Each turk user is identified by the nick name which is mainly the turk ID.
-
-Each turk user is shown some specific number of lineups for evaluation.
-These lineups are randomly selected from a pool of lineups designed for evaluations.
-The algorithm for how the lineups should be selected to show and what would be the order of display is implemented in the form shown in Figure \ref{fig:turk_web}.
-Also there is a check for invalid information which is implemented using javascript.
-If users try to go forward without giving any feedback they are not allowed to do that showing a warning message.
+It looks simple and it is indeed simple for the turk worker to provide feedback using this form.
+But it is not simple in design as all the information on this form are coming from database including the question on top of the lineup.
+This dynamic page provides a lot of features in customizing how one may want to display the lineup.
 
@@
 Lineups are presented at random for evaluations by the turk workers.
-Scalable Vector Graphics (SVG) is used so that observer can click on the lineup to pick certain plot.}
+Scalable Vector Graphics (SVG) is used so that observer can click on the lineup to pick certain plot.
+Once a plot is selected it gets shaded and the number appears in the choice text box.}
        \label{fig:turk_web}
@@
 
-After the evaluation is recorded on a lineup through form shown in Figure \ref{fig:turk_web} another form shown in Figure \ref{fig:turk_web_feedback} is used to give feedback to the turk users whether they correctly identifies the true plot and how many evaluations are recorded from the users.
-This form is also used to collect demographic and educational information about the user.
-After the required number of evaluations are obtained from each turk user, a pass code is given as a proof of the completion of the task which then later used for payment purpose.
+One of the nice features of the form in Figure \ref{fig:turk_web} is the use of Scalable Vector Graphics (SVG) for lineup which enables an observer to give feedback with the ease of just a mouse click.
+If the observer changes mind he or she can click the plot again and deselect it.
+If needed multiple selection of plots can be allowed, order of selection and deselection can be recorded with time taken for each action.
+Thats what we meant by saying it is complex in design.
+
+It is possible to let workers see the statistics of their total feedbacks with number of correct evaluations.
+This feature can be opted out easily if not necessary.
+The worker has to provide their turk ID and for next evaluation they don't have to type it again.
+This allows the worker give feedback using only mouse click.
+Thats what we meant by saying it is simple for turk worker.
+
+Once the data is submitted a feedback can be provided whether their choice was correct or wrong.
+This feature can also be opted out easily if not needed.
+The design of the feedback form is shown in Figure \ref{fig:turk_web_feedback}.
+This form is also used to collect demographic and educational information about the worker.
+After the required number of evaluations are obtained, a pass code is given as a proof of the completion of the task which is used for payment purpose later.
 
@@
 
+Each worker is shown some specific number of lineups for evaluation.
+These lineups are randomly selected from a pool of lineups designed for evaluations.
+The algorithm for how the lineups should be selected to show and what would be the order of display is implemented in the form shown in Figure \ref{fig:turk_web}.
+Also there is a check for invalid or missing information which is implemented using javascript.
+If users try to go forward without giving any feedback they are not allowed to do that showing a warning message.
+
+%After the evaluation is recorded on a lineup through form shown in Figure \ref{fig:turk_web} another form shown in Figure \ref{fig:turk_web_feedback} is used to give feedback to the turk users whether they correctly identifies the true plot and how many evaluations are recorded from the users.
+
 \subsection{Database design} The design of the database to store the collected data is shown in Figure \ref{fig:turk_database_design}.
@@
 Table picture\_delais contains the static information about each lineup.
-Table feedback is a dynamic table that grows with the number of feedbacks from each turk user.
-The multiple activities of each turk user are recorded in turk\_activity table.
-This table also contains the codes provided to the user once they finish the experiment.
-For our web site we used MySQL database located on a local server.
+Table feedback is a dynamic table that grows with the number of feedbacks from each turk worker.
+The multiple activities of the worker are recorded in turk\_activity table.
+This table also contains the codes provided to the workers once they finish the experiment.
+For the implementation of the web application we used MySQL database located on a local server.
 
@@
        \scalebox{.4}{\includegraphics{turk_database_design.pdf}}
-       \caption{Database design for Turk experiment data collection.
-The same database can be used for multiple turk experiments by keeping experiment information in picture details table which contains information about the lineups.}
+       \caption{Relational database design for MTurk experiment data collection.
+The same database can be used for multiple turk experiments by keeping experiment information in picture\_details table which contains information about the lineups.}
        \label{fig:turk_database_design}
@@
 
-\subsection{Data collection} To collect the survey data we developed a web site that shows a plot to an individual and get feedback from that individual.
+\subsection{Data collection}
+
+The homepage of the web displays detailed explanation on how they can perform the task of evaluating the lineups.
+Several examples with possible answers are provided.
+It is possible to customize how the workers will proceed from the home page.
+There are two options; one is to allow them to continue the task where no trial is needed.
+The second option is to force them to try some lineup before joining the actual experiment.
+The trial feedbacks are not recorded.
+As per the requirement of Institutional Review Board (IRB) the workers need to provide the informed consent.
+For this they have to read and agree with specific IRB approved informed consent.
+The flow chart for this data collection sequence is shown in Figure \ref{fig:turk_data_flow}.
+
+\begin{figure}[hbtp]
+   \centering
+       \scalebox{.4}{\includegraphics{turk_data_flow.png}}
+       \caption{Data collection work flow shows that workers can try some test lineups before going to the live experiment after providing informed consent.
+This design gives the flexibility to make the trial mandatory, if needed, so that without having enough correct trial evaluations the actual participation can be prevented.}
+       \label{fig:turk_data_flow}
+\end{figure}
+
+%To collect the survey data we developed a web site that shows a plot to an individual and get feedback from that individual.
 Each individual is asked to provide feedback for at least 10 different plots.
@@
 
-The MTurk workers were redirected to the web site and the data were collected, stored automatically into a local database server.
+%The MTurk workers were redirected to the web site and the data were collected, stored automatically into a local database server.
 Demographic informations such as age group, gender and education levels were also collected.
@@
 
-Figure \ref{fig:turk_work_flow} turk workers have to visit the experimental web site and give their consent to participate the survey as per IRB requirement.
+%Figure \ref{fig:turk_work_flow} turk workers have to visit the experimental web site and give their consent to participate the survey as per IRB requirement.
 In the experimental web, there is a option for observers to try some sample lineups to get familiar with the experiment.
@@
 
-\subsection{Data collection sequence} Once turk users are directed to our web site, they can see the detailed explanation on how they can perform the task of evaluation.
-Some simple examples are displayed along with correct responses.
-The users have options to try some test lineups before going for the actual experiment.
-But before that they have to provide the informed consent as per IRB requirement.
-The flow chart for this is shown in Figure \ref{fig:turk_data_flow}
+%\subsection{Data collection sequence}
 
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.4}{\includegraphics{turk_data_flow.png}}
-       \caption{Data collection work flow. Turk worker can try some test lineups before going to the live experiment after providing informed consent.}
-       \label{fig:turk_data_flow}
-\end{figure}
+\subsection{Data Security and Validity}
 
-\subsection{Data Security and Validity} Consideration to avoid hacking
+Some cautious attempts are taken to add security to the data.
+Server side scripting language PHP is used to connect to database and access or save data.
+For transferring data from one form to another PHP session variables are used.
+Cookies are avoided carefully so that no important informations are saved in the cookies.
 
-Check for invalid input
-
-Control for missing imput
+To prevent missing information and invalid input JavaScripts are used.
+For controlling some flow of the work such as showing various messages, JavaScripts are used as well.
+Careful consideration are made so that no important informations are stored in the java variable or function that could easily be revealed.
 
@@
 \section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated.
-The proposed online application design provides flexibility to control how the multiple lineups would be presented to a observer.
-It also gives added benefit to record timing of the evaluations.
-Scalable Vector Graphics (SVG) is used so that observer can click on the lineup to pick certain plot.
+The online application design provides flexibility to control how the multiple lineups would be presented to an observer.
+Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot.
 This also made the multiple plot selection from a lineup easier and convenient.
@@
 
-The web application is designed such a way that it still produces simple task for the worker who are used to doing so from MTurk.
-But it gives many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement.
+One of the main features of the web application is that it produces simple task for the worker who are used to doing so from MTurk but still provides many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement.
 The design of this application allows recruiting people from any source not necessarily just from MTurk.
-Also once the application is hosted, any number of experiments can be done through this without changing the core of this application.
+The web application is now hosted on Iowa State University public domain \citep{majumder:turk} and any number of experiments can be done through this web site without changing the core of this application.
 
@@
 This would save lot of time which researcher can use focusing on their actual research.
-This would also help lineup protocol to be used frequently since it would provide an ease of its use in making inferential decisions.
+This will also help lineup protocol to be used frequently since it will provide an ease of its use in making inferential decisions.
 
 We also intend to set up a web application for public use where researcher can put their lineup for online evaluation.
-The observer could be recruited from MTurk or any other source including local lab participants.
+The observer can be recruited from MTurk or any other source including local lab participants.
 

### 2013-06-14 paper_turk.tex
some writing plans added

@@
 
-\subsection{Data Cleaning}
+\subsection{Data Cleaning} Some suggestion about data cleaning based on experimental evidence. What to expect from turk data.
 
-\subsection{Diversity in the Data}
+\subsection{Diversity in the Data} Demographics, geographical locations, academic diversity
 
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.5}{\includegraphics{turker_country.pdf}}
-       \scalebox{.5}{\includegraphics{turker_location.pdf}}       
-       \caption{The location of turk workers on the world map shows the geographical diversity of turk workers even though most of the workers come from India and United States.}
-       \label{fig:rsq}
-\end{figure}
+%\begin{figure}[hbtp]
+%   \centering
+%       \scalebox{.5}{\includegraphics{turker_country.pdf}}
+%       \scalebox{.5}{\includegraphics{turker_location.pdf}}       
+%       \caption{The location of turk workers on the world map shows the geographical diversity of turk workers even though most of the workers come from India and United States.}
+%       \label{fig:rsq}
+%\end{figure}
 
@@
 
-\section{Appendix: What do Turk Workers Pick, $R^2$ or $p$-value?} What do people pick in a lineup plot, p-value or $R^2$?
+%
+%\section{Appendix: What do Turk Workers Pick, $R^2$ or $p$-value?} What do people pick in a lineup plot, p-value or $R^2$?
 To address this issue we obtain the approximate theoretical relationship between $R^2$ and the power of the classical hypothesis test.
@@
 For a sample of size $n$ this gives us
-\begin{eqnarray*}
-Y_i-\bar{Y}& = & \beta_0+\beta_1X_i+\epsilon_i - \beta_0 - \beta_1 \bar{X}- \bar{\epsilon} \\
-          & = & \beta_1(X_i-\bar{X})+(\epsilon_i-\bar{\epsilon})
-\end{eqnarray*}
-Now 
-\begin{eqnarray*}
-X_i-\bar{X}& = & X_i - \frac1n (X_1 + X_2 + ... + X_i + .....+ X_n) \\
-          & = & X_i - \frac1n X_i - \frac1n \sum_{j \neq i}{X_j}\\
-          & = & (1-\frac1n)X_i - \frac1n \sum_{j \neq i}{X_j}
-\end{eqnarray*}
-
-Thus we have 
-\begin{eqnarray*}
-E(X_i-\bar{X})^2 & = & (1-\frac1n)EX_i^2 - \left( \frac1n \right )^2 (n-1) EX_j^2 \\
-                 & = & (1-\frac1n)^2+ \frac{n-1}{n^2}\\
-                 & = & \frac{n-1}{n}
-\end{eqnarray*}
-
-Similarly we have
-
-\begin{eqnarray*}
-E(\epsilon_i-\bar{\epsilon})^2 & = & (1-\frac1n)E\epsilon_i^2 - \left( \frac1n \right )^2 (n-1) E\epsilon_j^2 \\
-                 & = & \left((1-\frac1n)^2+ \frac{n-1}{n^2} \right) \sigma^2 \\
-                 & = & \frac{n-1}{n}\sigma^2
-\end{eqnarray*}
-Finally we have expected total sum of square (SST) as
-\begin{eqnarray*}
-E\sum_i{(Y_i-\bar{Y})^2} & = & \sum_i E(Y_i-\bar{Y})^2=\sum_i \left [ \beta_1^2 E(X_i-\bar{X})^2 + E(\epsilon_i-\bar{\epsilon})^2 \right] \\
-                 & = & \sum_i\left[ \beta_1^2 \frac{n-1}{n}+  \sigma^2 \frac{n-1}{n}\right]\\
-                 & = & (n-1)(\sigma^2+\beta_1^2)
-\end{eqnarray*}
-
-We know $E(MSE|X) = \sigma^2$ or $E(SSE/n-2)|X = \sigma^2$ which gives the expected residual or error sum of square as $$E \sum_i (Y_i-\hat Y_i)^2=(n-2)\sigma^2$$
-Thus we have the expected regression sum of squares $SSR =  (n-1)(\sigma^2+\beta_1^2) - (n-2)\sigma^2 = (n-1) \beta_1^2+\sigma^2$ This gives $$R^2=\frac{(n-1) \beta_1^2+\sigma^2}{ (n-1)(\sigma^2+\beta_1^2)}$$
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.3}{\includegraphics{scatter_plot_beta_4.pdf}}
-       \caption{Scatter plot of data generated for $\beta_0$=6, $\beta_1$=4, sample size $n =300$ and $\sigma = 12$.
+%\begin{eqnarray*}
+%Y_i-\bar{Y}& = & \beta_0+\beta_1X_i+\epsilon_i - \beta_0 - \beta_1 \bar{X}- \bar{\epsilon} \\
+%          & = & \beta_1(X_i-\bar{X})+(\epsilon_i-\bar{\epsilon})
+%\end{eqnarray*}
+%Now 
+%\begin{eqnarray*}
+%X_i-\bar{X}& = & X_i - \frac1n (X_1 + X_2 + ... + X_i + .....+ X_n) \\
+%          & = & X_i - \frac1n X_i - \frac1n \sum_{j \neq i}{X_j}\\
+%          & = & (1-\frac1n)X_i - \frac1n \sum_{j \neq i}{X_j}
+%\end{eqnarray*}
+%
+%Thus we have 
+%\begin{eqnarray*}
+%E(X_i-\bar{X})^2 & = & (1-\frac1n)EX_i^2 - \left( \frac1n \right )^2 (n-1) EX_j^2 \\
+%                 & = & (1-\frac1n)^2+ \frac{n-1}{n^2}\\
+%                 & = & \frac{n-1}{n}
+%\end{eqnarray*}
+%
+%Similarly we have 
+%
+%\begin{eqnarray*}
+%E(\epsilon_i-\bar{\epsilon})^2 & = & (1-\frac1n)E\epsilon_i^2 - \left( \frac1n \right )^2 (n-1) E\epsilon_j^2 \\
+%                 & = & \left((1-\frac1n)^2+ \frac{n-1}{n^2} \right) \sigma^2 \\
+%                 & = & \frac{n-1}{n}\sigma^2
+%\end{eqnarray*}
+%Finally we have expected total sum of square (SST) as
+%\begin{eqnarray*}
+%E\sum_i{(Y_i-\bar{Y})^2} & = & \sum_i E(Y_i-\bar{Y})^2=\sum_i \left [ \beta_1^2 E(X_i-\bar{X})^2 + E(\epsilon_i-\bar{\epsilon})^2 \right] \\
+%                 & = & \sum_i\left[ \beta_1^2 \frac{n-1}{n}+  \sigma^2 \frac{n-1}{n}\right]\\
+%                 & = & (n-1)(\sigma^2+\beta_1^2)
+%\end{eqnarray*}
+%
+%We know $E(MSE|X) = \sigma^2$ or $E(SSE/n-2)|X = \sigma^2$ which gives the expected residual or error sum of square as $$E \sum_i (Y_i-\hat Y_i)^2=(n-2)\sigma^2$$
+%Thus we have the expected regression sum of squares $SSR =  (n-1)(\sigma^2+\beta_1^2) - (n-2)\sigma^2 = (n-1) \beta_1^2+\sigma^2$ This gives $$R^2=\frac{(n-1) \beta_1^2+\sigma^2}{ (n-1)(\sigma^2+\beta_1^2)}$$
+%
+%
+%\begin{figure}[hbtp]
+%   \centering
+%       \scalebox{.3}{\includegraphics{scatter_plot_beta_4.pdf}}
+%       \caption{Scatter plot of data generated for $\beta_0$=6, $\beta_1$=4, sample size $n =300$ and $\sigma = 12$.
 $R^2$ for this data was obtained as 0.1309 showing that the model could not successfully explain the variation in $Y$.
@@
 So, Can we conclude that $R^2$ does not have any effect in deciding whether $H_0: \beta_1=0$ should be rejected or not?}
-       \label{fig:plot_beta_4}
-\end{figure}
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.35}{\includegraphics{power_300_12.pdf}}
-       \caption{Power curve and $R^2$ values for sample size $n =300$ and $\sigma = 12$. Notice that for a small value of $R^2$ (0.1) the power is almost 1.}
-       \label{fig:power_rsq}
-\end{figure}
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.35}{\includegraphics{rsquare_contour.pdf}}
-       \scalebox{.35}{\includegraphics{rsquare_beta_sigma.pdf}}
-       \caption{Contour and surface plots of $R^2$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
-       \label{fig:contour_rsq}
-\end{figure}
-
-\begin{figure}[hbtp]
-   \centering
-       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines.pdf}}
-       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines1.pdf}}       
-       \caption{Relationship of $R^2$ with $\sigma$ and $\beta$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
-       \label{fig:rsq}
-\end{figure}
+%       \label{fig:plot_beta_4}
+%\end{figure}
+%
+%
+%\begin{figure}[hbtp]
+%   \centering
+%       \scalebox{.35}{\includegraphics{power_300_12.pdf}}
+%       \caption{Power curve and $R^2$ values for sample size $n =300$ and $\sigma = 12$. Notice that for a small value of $R^2$ (0.1) the power is almost 1.}
+%       \label{fig:power_rsq}
+%\end{figure}
+%
+%
+%\begin{figure}[hbtp]
+%   \centering
+%       \scalebox{.35}{\includegraphics{rsquare_contour.pdf}}
+%       \scalebox{.35}{\includegraphics{rsquare_beta_sigma.pdf}}
+%       \caption{Contour and surface plots of $R^2$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
+%       \label{fig:contour_rsq}
+%\end{figure}
+%
+%\begin{figure}[hbtp]
+%   \centering
+%       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines.pdf}}
+%       \scalebox{.35}{\includegraphics{rsquare_beta_sigma_lines1.pdf}}       
+%       \caption{Relationship of $R^2$ with $\sigma$ and $\beta$ for sample size $n =300$. The values for $R^2$ goes down sharply with $\sigma$ and $\beta$.}
+%       \label{fig:rsq}
+%\end{figure}
+%
 

### 2013-06-14 paper_turk.tex
some typos

@@
 
-There have been some advancements in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols.
+There have been some advancements in visual statistical inference since it was first introduced by \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols.
 In visual statistical inference the test statistics is a plot of the observed data.
@@
 
-The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and in some scenerios even better.
+The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and in some scenarios even better.
 But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.
@@
 \subsection{Selecting Parameter to Simulate Lineup} The first consideration for a simulation experiment is to fix the parameters of the model of interest.
-The very first consideration is the sample size.
+
+%The very first consideration is the sample size.
 Other parameters depends on the model of interest.
@@
 
-\subsection{Procedure to Simulate Data Plot} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from model of interest for prespecified parameters.
+\subsection{Procedure to Simulate Data Plot} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from model of interest for pre-specified parameters.
 We call this data set observed data.
-While the effect of the natural variability of this data set could be contolled by taking the replication of few samples, it is desirable to study whether we can reduce this variability alternatively.
+While the effect of the natural variability of this data set could be controlled by taking the replication of few samples, it is desirable to study whether we can reduce this variability alternatively.
 The main reason is to minimize the cost.

### 2013-06-18 paper_turk.tex
plan for a turk task

@@
 One good option is to recruit people from online workplace like Amazon Mechanical Turk (MTurk).
-It has the facilities to create online task that would allow people to evaluate lineups and get paid.
+It provides features to create online task that allow people to evaluate lineups and get paid.
 MTurk is designed for simple and easy tasks.
-The technical design of the underlying experiment for visual inference may be complex and the tools available to design this from MTurk is just too simple.
-In this paper we describe how to design MTurk experiments, present an alternative way to conduct the survey on lineups by designing a separate web application and getting turk worker do their job from this web site.
+The technical design of the underlying experiment for lineup evaluation may be complex and the tools available to design this from MTurk is just too simple.
+In this paper we present the design of MTurk experiments for lineup evaluation, provide an alternative way to conduct the survey on lineups by developing a separate web application and getting turk worker do their job from that web site.
 The web site is now hosted on the Iowa State University public domain and has been in use for multiple experiments \citep{majumder:turk}.
@@
 Getting results from this web site is very convenient and secure.
+
+{\bf Keywords: \sf statistical graphics, lineup, Amazon Mechanical Turk, visual inference, visualization, Crowdsourcing, Human Intelligence.}
 
@@
 
-The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and in some scenarios even better.
-But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.
+\cite{majumder:2013}  further developed visual inference by refining the terminologies and providing the methods of obtaining the power.
+it is revealed that visual test power can be as good as the best available conventional test and in some scenarios even better.
+This work establishes the validity of lineup protocol to be used as a tool for statistical testing.
+In the situations where no conventional test exists, visual inference can be the only inferential procedure without compromising a lot in power because of its non-parametric nature and few assumptions.
 
 These developments open up a whole new area of statistical research where lineups need to be evaluated by human observer.
-There are some reasons a researcher needs to evaluate lineups.
-One is to assess the power of the visual test \citep{heike:2012} for different visual test statistics.
-The another reason would be to make decision based on the lineup, i.e., to use lineup protocol in practical application \citep{niladri:2012}.
-Other reasons could be to present the results of the conventional test with visual tools such as lineup.
+For small scale or day to day research it is possible to have people around to get the lineups evaluated.
+But sometimes it is needed to have many observers to evaluate lineups.
+For example, to assess the power of the visual test for different visual test statistics \cite{heike:2012} recruited human observers to evaluate lineups.
+\cite{niladri:2012} used lineup protocol in practical applications.
+Other reasons to evaluate lineups are to present the results of the conventional test with visual tools such as lineup.
 
@@
 Section \ref{sec:turk_exp} presents the details description of an experiment with lineups and things to consider before a turk task.
-Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not possible through MTurk.
+Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not be possible through MTurk.
 Section \ref{sec:turk_task} describes how to create an MTurk task, mange workers and process payments.
@@
 
-\subsection{Sample size estimation} For a given proportion $p$ we want to have margin of error (ME) to be 0.1.
-Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$ Now from the theoretical power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the sample size required for that specific combinations of parameter.
+\subsection{Sample size estimation} By sample size we mean the number of evaluations per lineup.
+It is different than number of people who evaluates lineup.
+If multiple lineups are evaluated by a person, sample size will be larger than number of people recruited from MTurk.
+
+To have an idea how many evaluations are required for a lineup one approach can be to have a prior idea of proportion correct for the lineup.
+For a given proportion $p$ we want to have margin of error (ME) to be 0.1.
+Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$
+
+%Now from the theoretical power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the sample size required for that specific combinations of parameter.
 We collect data such that each of the parameter combinations in the table \ref{tbl:experiment_params} has approximately the estimated sample size that we calculated here.
@@
 
-\subsection{Planing the Turk Task}
-Question to ask
+\subsection{Plan for a Turk Task} \label{sec:task_plan} To make a good use of MTurk crowd source, it is important to split any big project into small pieces or Task.
+To present each task for the workers to do, a Human Intelligence Task or HIT needs to be designed which includes crisp and clear instructions of the task, descriptions of specific input and output desired and payment information.
+To design a HIT for lineups to be evaluated we need to consider the following issues.
 
-Whether reasoning would be collected or not
+\begin{itemize}
 
-Multiple or single response
+\item {\bf IRB approval:} Since this is a human subject experiment proper approval has to be taken from Institutional Review Board or IRB.
+This approval includes how the task will be performed, how the anonymity of the subjects will be maintained etc.
+For this we plan to have a consent form which the MTurk workers have to agree before participating the experiment.
+The consent form is approved by IRB.
 
-Test plot added or not
+\item {\bf Lineup question:} Each lineup should be presented with a question that the worker has to answer.
+The question needs to be clear and technical word should be removed as the MTurk workers may not be aware of those terms.
+The question is important for lineups as well.
+Very common question to evaluate a lineup is ``Which plot is the most different?".
+But for complicated studies the question may be quite different \citep{majumder:socio}.
 
-Training needed or not
+\item {\bf Data input:} For lineup experiments data input means mainly the lineups that are going to be presented for evaluations.
+Lineups may be presented in some sequence or completely at random.
+We need to decide whether a test lineup will be included or not in the pool of lineups going to be presented.
+Some other inputs may accompany with each lineup.
+Those include lineup question, how many lineups to be evaluated by the worker etc.
+Anything that the worker will see changing with each lineup is considered as data input to the worker.
+For different experimental needs this input may be different.
+For example, one may decide to let the worker know if each evaluation made is correct or wrong right after the feedback.
+This is an input for the worker.
 
-Feedback given after every evaluation or not
+\item {\bf Data output:} This means the data collected from the MTurk workers.
+That includes mainly the response on lineup question.
+Single or multiple responses can be requested for each lineup.
+Other optional data that may be collected are as follows;
 
-How many lineups to show
+\begin{enumerate}
+\item Demographic information of the observer
+\item Reasons for choice
+\item Confidence levels of the response provided
+\item Location information
+\item Time of the evaluation
+\end{enumerate}
 
-Are the lineups randomly selected?
+\item {\bf Payment:} Payment plays an important role on data quality and how fast the data can be collected.
+It depends on how many lineups are being evaluated by a worker, how much time it may require to finish the task or how hard the task is in general.
+
+%Whether reasoning would be collected or not
+%
+%Multiple or single response
+%
+%Test plot added or not
+%
+%Training needed or not
+%
+%Feedback given after every evaluation or not
+%
+%How many lineups to show
+%
+%Are the lineups randomly selected?
+
+\end{itemize}
 
@@
 
-The information collected from each individual is shown in Table \ref{tbl:data_info}.
-Data received from each individual are automatically saved in a secured mysql server maintained by the department of statistics, Iowa state university.
+The default information that the system is designed to collect from each individual is shown in Table \ref{tbl:data_info}.
+Data received from each individual will be automatically saved in a secured mysql server.
 
@@
 
-Turk workers are usually small payee workers.
-There several issues related to the payment of their effort.
-These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.
+Turk workers are usually small payee workers. There are several issues related to the payment of their effort. These are briefly discussed in the following section.
+
+% and we intend to work more on this as we progress through this dissertation work.
 
 \subsection{Creating Task for Lineup Evaluation} Task description, number of people to recruit, time allowed to finish the task, specify the qualification needed, setting the duration of the task, offering the pay per task.
+The task needs to be created as per the task plan described in Section \ref{sec:task_plan}.
 
-\subsection{Accepting or Rejecting the Task} In our design we keep a test lineup plot which is very easy to evaluate.
-The general criteria may be to reject payment when workers do not get that easy test lineup plot.
-Our experience suggest that there are workers who did not get that test plot but their overall success rate is very high.
+\subsection{Accepting or Rejecting the Task} As per design we keep a test lineup plot which is very easy to evaluate.
+The general rule may be to reject payment when workers do not get that easy test lineup plot.
+Our experience suggests that there are workers who do not get that test plot but their overall success rate is very high.
 So depending on only one criteria the payment should not be made.
-These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.
 
-\subsection{Processing Payment}Amazon Mechanical Turk suggest that each worker gets \$6/hour as wage.
-Thus we need to estimate how much time a tusk may take to complete and based on that we have to specify the payment for each task.
-Our experience indicates that a better payment lures more serious workers who usually provide cleaner data which is more reliable.
-We may study this issue while we do multiple turk experiments.
+%These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.
 
-\subsection{Managing Worker} pay bonus, appreciate worker by sending email, block worker etc.
+\subsection{Payment for the Worker}Amazon Mechanical Turk suggests that each worker gets \$6/hour as wage.
+Thus we need to estimate how much time a task may take to complete and based on that we have to specify the payment for each task.
+Our experience indicates that a better payment brings more serious workers who usually provide cleaner data which is more reliable.
+
+%We may study this issue while we do multiple turk experiments.
+
+\subsection{Managing Worker} Pay bonus, appreciate worker by sending email, block worker etc.
 
@@
 
-\subsection{Selection Bias} Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did.
+\subsection{Selection Bias}
+
+%Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did.
 In this section we intend to analyze to what extent this selection bias has occurred and how we can adjust for this.
@@
 \section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated.
-The online application design provides flexibility to control how the multiple lineups would be presented to an observer.
+The online application design provides features to control how the multiple lineups can be presented to an observer.
 Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot.
@@
 
-One of the main features of the web application is that it produces simple task for the worker who are used to doing so from MTurk but still provides many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement.
+One of the main features of the web application is that it produces simple task for the worker but still retains many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement.
 The design of this application allows recruiting people from any source not necessarily just from MTurk.
@@
 The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their need and run the MTurk experiments as part of their research that involves lineups.
-This would save lot of time which researcher can use focusing on their actual research.
 This will also help lineup protocol to be used frequently since it will provide an ease of its use in making inferential decisions.

### 2013-06-19 paper_turk.tex
Procedure to Simulate Data Plot

@@
 %\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
-\usepackage{graphicx}
+\usepackage{graphicx, amsmath}
 \usepackage{url}
@@
 
-If a lineup is already created from observed data, the web application presented in Section \ref{sec:web_application} can be used to evaluate it.
-In this scenario we do not need to design an experiment.
+If a lineup is created from actual observed data, the web application presented in Section \ref{sec:web_application} can be used to evaluate it.
+In that case we do not need to design a simulation experiment.
 This section will be useful when a simulation experiment is needed to examine different plot types as test statistics and compare the power of visual test \citep{majumder:2013}.
 To examine the effectiveness of certain plots in displaying the data one might want to design an experiment with lineup \citep{heike:2012}.
-In any cases, two major considerations are choice of parameters to simulate lineup and number of people needed to be recruited to evaluate a lineup.
+In any cases, two major considerations are choice of parameters to simulate lineup and number of people needed to evaluate a lineup.
 
-\subsection{Selecting Parameter to Simulate Lineup} The first consideration for a simulation experiment is to fix the parameters of the model of interest.
+\subsection{Selecting Parameter to Simulate Lineup} \label{sec:parameter_selection} In any experimental design we need to have some control.
+For a simulation experiment with lineup, this refers to the parameter related to a lineup.
+This depends on what the purpose of the experiment is.
+For example, to compare the power of a parametric test one may fix the parameter specified by alternative hypothesis and generate data from that model.
+This data can be considered as the observed data.
+A lineup can be created by placing this observed data plot on a lineup where rest of the data plots come from the model specified by the null model \citep{majumder:2013}.
+
+In addition to the hypothesized parameter of interest, other parameters that may need to be fixed include sample sizes, variability in the data, error structure etc.
+These parameters produces the effect sizes and are responsible for any detectable signal in the lineup.
+Thus for a simulation study a range of effects sizes need to be considered.
+It is a little bit tricky to decide what exact effect sizes are appropriate.
+For example in \cite{majumder:2013} the parameters were chosen so that they produce a smoother power curve of a conventional test.
+But in general this depends on what the researchers may want to test and control in an experimental study.
 
@@
 We call this data set observed data.
-While the effect of the natural variability of this data set could be controlled by taking the replication of few samples, it is desirable to study whether we can reduce this variability alternatively.
-The main reason is to minimize the cost.
-To make sure that the observed data set truly represents model of interest we are considering three approaches.
-One is Kolomogorov test statistic approach and the other two approaches are quantiles of p values and closeness of estimated parameters to the true parameters.
-These three approaches are discussed below.\\
+Every time we do that we get a new set of observed data which may produce a parameter very different than the actual parameter specified to generate the data.
+But it is important to have a observed data closely representing the parameters chosen since other null plots will be compared to this data plot in a lineup.
+One solution to this is to take some replications of lineups for the same effect size.
 
-{\bf Kolomogorov test statistic approach:} In this approach we simulate 1000 data sets and obtain Kolmogorov test statistic for each set of data as below.
+While the effect of the natural variability of the observed data set can be controlled by taking the replication of few samples, it is desirable to study whether we can reduce this variability further to some extent.
+For this we pick the example of a simple linear regression model and examines how the data plot can be generated that best represent the specified parameter.
+Consider a linear regression model
+\begin{equation} \label{eqn:turk_model} 
+Y_i = \beta_0 + \beta X  + \epsilon_i 
+\end{equation}
+where $\epsilon_i \stackrel{iid}{ \sim } N(0,\sigma^2)$, $i=1,2, .., n$.
+The covariate $X$ can be continuous or discrete.
+As discussed in Section \ref{sec:parameter_selection} we specify the parameters sample size $n$=300, regression slope $\beta$=3 and error standard deviation $\sigma$=12 to simulate observed data.
+
+To make sure that the observed data set truly represents the Model \eqref{eqn:turk_model} we suggest three approaches.
+One is Kolomogorov test statistic approach and the other two approaches are quantiles of $p$-values and closeness of estimated parameters to the true parameters.
+To illustrate the three approaches we used Model \eqref{eqn:turk_model} as an example but the idea can be extended to any situation.
+The three approaches are discussed below.
+\\
+
+{\bf Kolomogorov test statistic approach:} In this approach we simulate 1000 data sets from Model \eqref{eqn:turk_model}  and obtain Kolmogorov test statistic for each set of data as below.
 $$D_n=\sup_x |F_n(x)-F(x)|$$ where $F_n(x)=\frac1n \sum_{i=1}^n I_{X_i\le x}$ be the empirical distribution function of fitted residuals, $I_{X_i\le x}$ be the indicator function equal to 1 if $X_i\le x$ and equal to 0 otherwise and $F(x)$ be the cumulative function of normal with mean zero(0) and variance $\sigma^2$.
-We then keep the data set that has minimum value for Kolmogorov test statistic.
-For replication purpose we can generate three observed data sets in similar way.\\
+We keep the data set that has minimum value for Kolmogorov test statistic since for this data set $F_n(x)$ should be the closest to the desired normal model.
+\\
 
-{\bf Quantiles of p-value approach:} With any data set we generate there is a p-value associated with testing $H_0: \beta=0$.
-In this approach we generate 1000 data sets from the model of interest and obtain p-values associated with $H_0: \beta=0$ for each data set after fitting the same model.
-Then we construct blocks of p-value such as (0.0-$q_{33}$), ($q_{33}$-$q_{66}$), ($q_{66}$-1) where $q_i$ is the $i$th percentile in the distribution of the p-values.
-We then randomly select three data sets that have corresponding p-values in the above quantile range.
-As an example the distribution  of p-values in 1000 simulated data sets for $n$=300, $\beta$=3 and $\sigma$=12 is shown in figure \ref{fig:dist_pvalue}.
-Notice that if we like to have three replications of plots, we will have observed data sets with smaller p-values as the distribution is highly right skewed as well as the 33th and 66th percentiles of p-values are 0.0101 and 0.077 respectively.
-So, another option may be to take the mid points of those quantile ranges and pick the data sets that have those p-values.\\
+{\bf Quantiles of $p$-value approach:} For a simulated observed data set we can obtain the $p$-value associated to testing $H_0: \beta=0$.
+The distribution of $p$-value is uniform under null hypothesis but under alternative it has a right skewed distribution.
+Figure~\ref{fig:dist_pvalue} shows the distribution  of $p$-values for sample size $n$=300, regression slope $\beta$=3 and error standard deviation $\sigma$=12.
+If we generate a data set randomly there is a 21\% chance that the data will show a $p$-value of 0.25 or more even though we generated data set with non-zero $\beta=3$.
+We need to make sure that the simulated data does not come from this extreme end.
+On top of that we want some replication so that this extreme effect can be controlled at some level.
+For this example we intend to pick three replications.
 
@@
    \centering
-       \scalebox{.3}{\includegraphics{dist_pvalue.pdf}}
-       \caption{Distribution of p-values for $n$=300, $\beta$=3 and $\sigma$=12.}
+       \scalebox{.6}{\includegraphics{dist_pvalue.pdf}}
+       \caption{Distribution of $p$-values for $n$=300, $\beta$=3 and $\sigma$=12.}
        \label{fig:dist_pvalue}
@@
 
-{\bf Closeness of estimated parameters:} When we simulate a data set from the model of interest and again fit the same model with the data set we do not get the parameters estimates same as what we fixed while simulation.
-It depends on what the standard errors of the parameter estimates are.
-In our experimental setting we some times have very different estimates for small parameter values(such as one may get estimated value of 0.5 for true $\beta=3$).
-In this approach we pick the data set that shows most close estimates of parameters compared to true parameter values.\\
+In this approach we generate 1000 data sets from the model of interest and obtain $p$-values for each data set after fitting the same model.
+We construct 3 blocks of $p$-values such as (0.0-$q_{33}$), ($q_{33}$-$q_{66}$), ($q_{66}$-1) where $q_i$ is the $i$th percentile in the distribution of the $p$-values.
+We randomly select three data sets that have corresponding $p$-values in the above quantile range.
+Notice that if we like to have three replications of plots, we will have observed data sets with smaller $p$-values as the distribution is highly right skewed as well as the 33th and 66th percentiles of p-values are 0.0101 and 0.077 respectively.
+So, another option may be to take the mid points of those quantile ranges and pick the data sets that have those p-values.
+\\
+
+{\bf Closeness of estimated parameters:} When we simulate a data set from the Model \eqref{eqn:turk_model} and fit the model to the data set again, we do not get the parameters estimates same as what we fixed while simulation.
+For example, we obtained a parameter estimates of 0.5 for true $\beta=3$.
+We want a data set where the parameter is closed to our fixed slope $\beta=3$.
+In this approach we generate 1000 data sets and pick the data set that shows most close estimates of parameters compared to true parameter values.
 
@@
 Kolmogorov method does not necessarily make sure that estimated parameters are close to the true parameters.
-On the other hand closeness of estimated parameters does not make sure that p value is small enough when we should reject the null hypothesis.
-Only the quantiles approach seems reasonable as it has much control over p-values and it gives similar data sets that has closest parameter estimates.
-So we used the quantiles of p-value approach in section \ref{sec:simulate_plot} to obtain three replicated sample of observed data sets for a particular parameter settings.\\
+On the other hand closeness of estimated parameters does not make sure that $p$-value is small enough when we should reject the null hypothesis.
+Only the quantiles approach seems reasonable as it has much control over $p$-values and it gives similar data sets that has closest parameter estimates.
+So we suggest the quantiles of $p$-value approach to generate observed data with specific effect size.
 
@@
 To present each task for the workers to do, a Human Intelligence Task or HIT needs to be designed which includes crisp and clear instructions of the task, descriptions of specific input and output desired and payment information.
-To design a HIT for lineups to be evaluated we need to consider the following issues.
+To design a HIT for lineups to be evaluated we need to consider the following issues;
 
@@
 \item Demographic information of the observer
-\item Reasons for choice
-\item Confidence levels of the response provided
+\item Supplementary information such as reasons or confidence levels of the response provided
 \item Location information

### 2013-06-19 R/turk_paper.R

@@ -100,6 +100,49 @@ sa <- ddply(dat,.(age), summarize,
 users <- read.csv("../data/turk_users.csv", header=T)
 
 
+# ================================================================
+# Distribution of p-value
+# These codes generate the distribution of p-value and compute the
+# expected power of visual test as well. Last modified by Mahbub
+
+n <- 300
+beta <- 3
+sigma <- 12
+
+ncp <- beta* sqrt(n)/(2*sigma) # refer to documentation gmail (xbar=1/2 here)
+
+#Density of the absolute value of a noncentral
+#t random variable with df degrees of freedom
+#and noncentrality parameter ncp.
+
+f.abs.t=function(t,df,ncp=0){
+  (t>0)*dt(t,df=df,ncp=ncp)+dt(-t,df=df,ncp=ncp)
+}
+
+#Density of the p-value from a t-test 
+#when the noncentrality parameter is ncp
+#and the degrees of freedom are df.
+
+f=function(p,df,ncp=0)
+{
+  tt=qt(1-p/2,df=df)
+  f.abs.t(tt,df=df,ncp=ncp)/f.abs.t(tt,df=df)
+}
+
+#Example: Density of p-value for t-test with
+#df=8 and ncp=2.
+df <- n-2 # since 2 parameters in the regression model
+
+
+p=seq(0.01,1,by=.01)
+y=f(p,df=df,ncp=ncp)
+#plot(p,y,type="l",ylim=c(0,max(y)))
+
+library(ggplot2)
+qplot(p,y,geom="line",ylim=c(0,max(y))) +xlab("p-value") +ylab("density")
+ggsave("../images/dist_pvalue.pdf", height=4, width=4)
+
+
 # ------------ description of coded variables in the data -----------
 
 ## gender 1 = male 

### 2013-06-19 paper_turk.tex
test and training lineup

@@
 
-%Now from the theoretical power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the sample size required for that specific combinations of parameter.
-We collect data such that each of the parameter combinations in the table \ref{tbl:experiment_params} has approximately the estimated sample size that we calculated here.
+If we do not have any prior idea of proportion of correct or power, we need to rely on the power of similar conventional test.
+This can be assumed to be the power or proportion correct for that lineup.
+Other ways of having an estimate of sample size can be very specific to the problem of interest and should be dealt with the requirement of the problem.
 
-\subsection{Test and Training Lineup} How many test lineup?
+\subsection{Test and Training Lineup} Some lineups should be presented to the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment.
+It is important to setup this properly.
+The training lineups should be easy and feedback should be provided right after the feedback received.
+The purpose is to give them an idea how the actual task would look like.
 
-How to setup training, randomized or sequential selection of lineup for training.
+The another way can be to make this training mandatory to participate the experiment.
+The MTurk worker should have certain proportion of correct responses on these training lineups to allow them to participate.
+This is often practiced in MTurk task and the workers are very familiar with this approach.
+In MTurk language it is called the qualification of the worker.
+Thus to design a MTurk task it is important to set an standard qualification of the worker.
 
+Other things that needs to be considered include number of training lineups, how the lineups should be shown.
+Training should not take much longer.
+Two or three lineups can provide enough training.
+The training lineups should be easy to evaluate and they should be randomly selected from a very small number of lineups.
+That may produce repetition which may help the MTurk workers to retest their skill on the lineup the might have a wrong selection before.
+
+There should be a test lineup when the workers evaluate multiple lineups in actual experiment.
+This test lineup can be used to process payment and detect any unusual responses.
+The test lineup should be super easy to evaluate so that anyone can detect the data plot without much effort.
+
+It is helpful if some example lineups are presented with the experimental description.
 Example lineup on the homepage should be of size three or four so that more than one lineup can be placed on the homepage.
+This helps the worker decide whether they are willing to participate the experiment at all.
 

### 2013-06-20 paper_turk.tex
sample size updates

@@
 To make sure that the observed data set truly represents the Model \eqref{eqn:turk_model} we suggest three approaches.
-One is Kolomogorov test statistic approach and the other two approaches are quantiles of $p$-values and closeness of estimated parameters to the true parameters.
+One is Kolmogorov test statistic approach and the other two approaches are quantiles of $p$-values and closeness of estimated parameters to the true parameters.
 To illustrate the three approaches we used Model \eqref{eqn:turk_model} as an example but the idea can be extended to any situation.
@@
 
-{\bf Kolomogorov test statistic approach:} In this approach we simulate 1000 data sets from Model \eqref{eqn:turk_model}  and obtain Kolmogorov test statistic for each set of data as below.
+{\bf Kolmogorov test statistic approach:} In this approach we simulate 1000 data sets from Model \eqref{eqn:turk_model}  and obtain Kolmogorov test statistic for each set of data as below.
 $$D_n=\sup_x |F_n(x)-F(x)|$$ where $F_n(x)=\frac1n \sum_{i=1}^n I_{X_i\le x}$ be the empirical distribution function of fitted residuals, $I_{X_i\le x}$ be the indicator function equal to 1 if $X_i\le x$ and equal to 0 otherwise and $F(x)$ be the cumulative function of normal with mean zero(0) and variance $\sigma^2$.
@@
 In this approach we generate 1000 data sets and pick the data set that shows most close estimates of parameters compared to true parameter values.
+We do this three times to obtain three replications of the data.
 
@@
 
-\subsection{Sample size estimation} By sample size we mean the number of evaluations per lineup.
-It is different than number of people who evaluates lineup.
+\subsection{Sample size estimation} For any experiment it is important to determine the sample size.
+It is not only related to time and cost of the experiment but also the validity of the results depends on it.
+In simulation experiment with lineup the sample size means the number of evaluations per lineup.
+It is different than the number of people who evaluates lineup.
 If multiple lineups are evaluated by a person, sample size will be larger than number of people recruited from MTurk.
+For example, if a lineup needs to be evaluated 20 times, we need at least 20 persons since each person does not see the same lineup more than once.
+This will also enable us to get 10 lineups evaluated if all of these 20 people evaluate 10 lineups each.
+But all the lineups don't require same number of evaluations.
+For easy or difficult lineups fewer evaluations are needed.
 
-To have an idea how many evaluations are required for a lineup one approach can be to have a prior idea of proportion correct for the lineup.
+One approach to assess number of evaluations that are required for a lineup is to have a prior idea of proportion correct for the that lineup.
 For a given proportion $p$ we want to have margin of error (ME) to be 0.1.
@@
 
-If we do not have any prior idea of proportion of correct or power, we need to rely on the power of similar conventional test.
+If we do not have any prior idea of proportion of correct or power, we may rely on the power of a similar conventional test if available.
 This can be assumed to be the power or proportion correct for that lineup.
@@
 It is important to setup this properly.
-The training lineups should be easy and feedback should be provided right after the feedback received.
+The training lineups should be easy and feedback should be provided right after the response is received.
 The purpose is to give them an idea how the actual task would look like.
 
-The another way can be to make this training mandatory to participate the experiment.
+The another option is to make this training mandatory to participate the experiment.
 The MTurk worker should have certain proportion of correct responses on these training lineups to allow them to participate.
@@
 In MTurk language it is called the qualification of the worker.
-Thus to design a MTurk task it is important to set an standard qualification of the worker.
+Thus to design a MTurk task it is important to fix a standard qualification of the worker.
 
@@
 
-\item {\bf Lineup question:} Each lineup should be presented with a question that the worker has to answer.
-The question needs to be clear and technical word should be removed as the MTurk workers may not be aware of those terms.
+\item {\bf Lineup question:} Each lineup should be presented with a question that the worker is asked to answer.
+The question needs to be clear and technical words should be removed as the MTurk workers may not be aware of those terms.
 The question is important for lineups as well.
@@
 
-\section{Managing Turk Task}\label{sec:turk_task}
+\section{Managing Turk Task}\label{sec:turk_task} \cite{turk} Mechanical Turk website provides various features that are helpful to maintain and organize the task and manage the workers.
+Creating, posting, accepting or rejecting tasks and processing payment are done from the MTurk system.
+It is also possible to screen out workers as per need.
+For example, none will be interested to recruit people who have bad reputation of getting the work done properly.
+This can be obtained from each worker's previous work history of total number of accepted task out of total number of submitted task.
+The web application we developed is for presenting lineups in a way required by the experiment design and collecting data.
+To get people to the web application we need to design a turk task in MTurk system.
 
-Turk workers are usually small payee workers. There are several issues related to the payment of their effort. These are briefly discussed in the following section.
+%Turk workers are usually small payee workers. There are several issues related to the payment of their effort. These are briefly discussed in the following section.
 

### 2013-06-20 R/turk_paper.R

@@ -139,7 +139,8 @@ y=f(p,df=df,ncp=ncp)
 #plot(p,y,type="l",ylim=c(0,max(y)))
 
 library(ggplot2)
-qplot(p,y,geom="line",ylim=c(0,max(y))) +xlab("p-value") +ylab("density")
+qplot(p,y,geom="line",ylim=c(0,max(y))) +xlab("p-value") +ylab("density")+
+  theme_bw() + theme(panel.grid = element_blank())
 ggsave("../images/dist_pvalue.pdf", height=4, width=4)
 
 

### 2013-06-20 paper_turk.tex
creating task

@@
 Creating, posting, accepting or rejecting tasks and processing payment are done from the MTurk system.
-It is also possible to screen out workers as per need.
+It is also possible to screen out workers as needed.
 For example, none will be interested to recruit people who have bad reputation of getting the work done properly.
-This can be obtained from each worker's previous work history of total number of accepted task out of total number of submitted task.
+This information can be obtained from each worker's previous work history of total number of accepted task out of total number of submitted task.
 The web application we developed is for presenting lineups in a way required by the experiment design and collecting data.
@@
 
-\subsection{Creating Task for Lineup Evaluation} Task description, number of people to recruit, time allowed to finish the task, specify the qualification needed, setting the duration of the task, offering the pay per task.
-The task needs to be created as per the task plan described in Section \ref{sec:task_plan}.
+\subsection{Creating Task for Lineup Evaluation} To create a MTurk task some parameters have to be specified.
+The task descriptions need to be as simple as possible.
+This description makes the first impression about the task along with the amount of money to be paid for each task.
+Once the worker agrees to do the task they may come to the web site designed for lineup evaluation.
+Thus it is important to provide them with enough information so that they don't have to spend much time after coming to the web application.
+Some other parameters that need to be specified are discussed below.
+
+\begin{itemize}
+
+\item The number of worker to recruit has to be provided so that the turk task is live until specific number of people do the task.
+This is related to the sample size we intend to collect on each lineup.
+
+\item Time allowed to finish each task has to be specified.
+Once a specific time period is set up the task will be expired after that time and the worker can't be submit it anymore.
+The worker has to finish the task by that time period.
+
+\item Qualifications needed to view and perform the task may be specified so that only desired participants can do the task.
+It depends on the population of interest as per the experimental design.
+For example one may only allow workers who have a history of doing at least 100 tasks and out of which a specific percent of tasks have been approved by other recruiters.
+
+\item {\bf Duration of the experiment:} The duration of each experiment is a period of time set so that the task is not available after that time period no matter whether all the required number of workers have participated or not.
+
+\item {\bf Redirect to new web:} The MTurk worker should be informed clearly that they will be redirect to a new website from where they will provide feedback.
+The whole task including the instruction and procedure in the web application presented as per the task plan described in Section \ref{sec:task_plan}.
+
+\end{itemize}
 
@@
 
-\subsection{Data Cleaning} Some suggestion about data cleaning based on experimental evidence. What to expect from turk data.
+\subsection{Data Cleaning} Data cleaning is different than accepting and rejecting the task.
+There may be some tasks for which payment is provided but yet the tasks may need to be excluded from the study.
+Some suggestion about data cleaning based on experimental evidence.
+What to expect from turk data.
 

### 2013-06-20 paper_turk.tex
creating task

@@
 
-\item {\bf Duration of the experiment:} The duration of each experiment is a period of time set so that the task is not available after that time period no matter whether all the required number of workers have participated or not.
+\item Duration of the task is the period of time the task is available for workers to do.
+If the time period is over the task will not be available no matter whether all the required number of workers have participated or not.
+This duration is important as each payment has to be finalized by this time period.
+Otherwise, all the workers will be paid automatically after this time period no matter if the the task is accepted or rejected.
+Some times it is helpful to set up a longer duration and see how long it takes before all the tasks get completed.
 
-\item {\bf Redirect to new web:} The MTurk worker should be informed clearly that they will be redirect to a new website from where they will provide feedback.
-The whole task including the instruction and procedure in the web application presented as per the task plan described in Section \ref{sec:task_plan}.
+\item Finally, the workers are redirected to the web site designed for lineup evaluation.
+MTurk workers should be informed clearly that they will be redirected to a new website from where they will provide feedback.
+The whole task including the instructions and procedures in the web application should be presented as per the task plan described in Section \ref{sec:task_plan}.
 

### 2013-06-20 R/turk_paper.R
distribution of p-value

@@ -139,8 +139,9 @@ y=f(p,df=df,ncp=ncp)
 #plot(p,y,type="l",ylim=c(0,max(y)))
 
 library(ggplot2)
-qplot(p,y,geom="line",ylim=c(0,max(y))) +xlab("p-value") +ylab("density")+
-  theme_bw() + theme(panel.grid = element_blank())
+qplot(p,y,geom="line",ylim=c(0,max(y))) +xlab("p-value") +ylab("density") +
+  theme_bw() 
+#+ theme(panel.grid = element_blank())
 ggsave("../images/dist_pvalue.pdf", height=4, width=4)
 
 

### 2013-06-21 paper_turk.tex
accepting or rejecting the task

@@
 It depends on how many lineups are being evaluated by a worker, how much time it may require to finish the task or how hard the task is in general.
+The MTurk convention is to pay as per an hourly rate of \$6.
+But some times it may be more or less depending on the task type.
+For some easy tasks it may take longer time which will reduce the pay rate by hour.
+Other tasks which are difficult but can be done very fast will have a increase payment rate.
 
@@
 
-\subsection{Accepting or Rejecting the Task} As per design we keep a test lineup plot which is very easy to evaluate.
-The general rule may be to reject payment when workers do not get that easy test lineup plot.
-Our experience suggests that there are workers who do not get that test plot but their overall success rate is very high.
-So depending on only one criteria the payment should not be made.
+\subsection{Accepting or Rejecting the Task} There is no hard and fast rule to follow while accepting or rejecting the tasks submitted by the MTurk workers.
+Since MTurk task are very simple and payment amount is very small the general convention is to pay every worker who submitted the task properly as instructed.
+The task should not be rejected based on the quality of work unless it prominently demonstrates that the task was not performed properly and irrelevant or garbage data were provided.
+It is very unusual to get garbage data from MTurk workers since they are well aware that this conduct may harm their reputation as a worker.
+So, proper caution needs to be taken while rejecting a task.
+Some times may happen that the workers provided crap data unintentionally.
+In that case we recommend to accept the task and pay for trying the task.
 
+It is very difficult to detect whether a worker is giving data by properly inspecting the lineup or just at random.
+This can be monitored by putting a test lineup which is very easy to evaluate.
+The worker can be informed that there will be a test lineup which need to be correctly evaluated to make sure the task is accepted.
+This may prevent worker giving random data and it is easier to accept or reject tasks based on this criteria.
+
+There may be mistakes made by the worker such as giving a wrong ID or a invalid input even though the whole task is properly done as instructed.
+In this case the task should be accepted and payment should be made.
+This encourages the workers and they appreciate the recruiters sincerity and provide good feedbacks.
+This does not happen frequently if qualified workers are recruited such as who had at least a certain number of percentage of tasks approved previously.
+
+Other criteria to accept or reject the tasks may be more complex based on the experimental needs.
+For example one may accept the task if certain percentage of the easy lineups are correctly evaluated.
+This criteria can be used if multiple number of easy lineups are shown for evaluation.
+For example if there are 3 easy lineups and none of them were correctly evaluated it is most likely that the feedbacks were provided randomly.
+Some times it may happen that out of 10 lineups 3 were correctly evaluated but all the three easy lineups were wrongly evaluated.
+In that case the payment should be made since it is very unlikely that out of 10 lineups a total of 3 lineups would be correctly evaluated by just random response.
 %These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.
 
-\subsection{Payment for the Worker}Amazon Mechanical Turk suggests that each worker gets \$6/hour as wage.
+The payment of the workers is directly associated with the rejection of the work.
+If the task is not accepted the payment to the worker is denied and reasons for rejecting the tasks should be clear so that the worker doesn't get confused.
+
+%\subsection{Payment for the Worker}Amazon Mechanical Turk suggests that each worker gets \$6/hour as wage.
 Thus we need to estimate how much time a task may take to complete and based on that we have to specify the payment for each task.
@@
 
-\subsection{Managing Worker} Pay bonus, appreciate worker by sending email, block worker etc.
+\subsection{Managing Worker} Accepting the task and processing the payment in a timely manner may make a good impression for the task they just did.
+This is helpful for the recruiter's reputation so that in future the recruiter can get the job done faster.
+Since the MTurk worker will always  prefer the tasks posted by a good recruiter.
+Besides this we provide some good worker management strategy as below.
+
+\begin{itemize}
+
+\item Pay bonus
+
+\item Appreciate work
+
+\item Reply query email promptly
+
+\item Block workers if necessary
+
+ \end{itemize}
 
@@
 
-Time of the task may recruit from a specific geographical location
+There is always a concern of selection biases with any online study.
+First of all in online study only those who use internet can participate.
+For a turk experiment the pool of participants even shrinks further to those who work in MTurk system.
+
+Other biases may be due to the time the task is posted online, setting up specific qualification or even payment amount.
+A task which is posted at noon in central time in USA is less likely to be seen from Indian region since that is the midnight in that area.
+This may produce an artificial filter to the data which may come only from certain geographical location.
+If a specific qualification of the task is required not all the workers are able to view and perform that task.
+Also, if payment amount is very small many worker may not even review the task.
+
+While selection bias is very important for some experimental study it is not much of an issue for experiment with lineups.
+If we examine the diversity of the participants in \ref{majumder:turk} we see that the turk data provide data from a very diverse population.
+Moreover it is observed in XXX that diversity is not much important for lineups as the human factors do not have any practical impact on the probability of correctly identifying the data plot in the lineup.
+
+ may recruit from a specific geographical location
 

### 2013-06-21 paper_turk.tex
selection bias

@@
 This table also contains the codes provided to the workers once they finish the experiment.
-For the implementation of the web application we used MySQL database located on a local server.
 
@@
 \end{figure}
+
+The primary key in feedback table is produced by nick\_name and pic\_id since no workers are allowed to provide multiple feedbacks on the same lineup.
+In all other tables the first field names shown in Figure~\ref{fig:turk_database_design} are the primary keys.
+For the implementation of the web application we used MySQL database located on a local server.
 
@@
 \begin{table}[hbtp]
-\caption{Information Collected from Each Individual}
+\caption{Default information the web application collects from each individual}
 \centering 
@@
 
+Since the experiment is based on online participations and related to monetary affairs, it is important to maintain certain security for the data collection.
+The attempt to provide random data or irrelevant information as well as harmful actions need to be prevented.
 Some cautious attempts are taken to add security to the data.
@@
 To prevent missing information and invalid input JavaScripts are used.
+Most of the cases options or combo boxes are used instead of free text boxes to avoid invalid input.
+This also made the task easy to perform and convenient for the workers.
 For controlling some flow of the work such as showing various messages, JavaScripts are used as well.
@@
 
-\item Pay bonus
+\item Not all the workers put the same effort while doing the task.
+Some workers spend much time and perform the task sincerely and follow the instructions very carefully.
+That effort is observable in their responses and time taken for each evaluations as well as from the textual feedbacks such as writing choice reasons in details.
+We recommend paying bonus to those workers in addition to the regular payment.
 
-\item Appreciate work
+\item If a work is not worth paying bonus payment we still recommend to appreciate each work.
+Even when the task gets rejected a proper explanation of rejection along with an appreciation for at least trying to participate the experiment is very useful for a recruiter's good image.
 
-\item Reply query email promptly
+\item Some workers may email to learn more about the experiment.
+Some times they may face technical troubles which needs to be taken care of promptly.
+A timely communication with worker is necessary and emails should be responded as  promptly as possible.
+It is important as they can report any trouble to IRB which may create unpleasant issues with the human subject experiment.
 
-\item Block workers if necessary
+\item It is recommended to reject the task if it is not submitted as requirement.
+Some times this may produce dispute and the workers may become angry and demand payment.
+We recommend to be strict to the decision and for any further administrative control there is an option to block the worker if necessary.
+After all this is a work place and it is expected that the worker maintain the work place environment.
 
@@
 
-While selection bias is very important for some experimental study it is not much of an issue for experiment with lineups.
-If we examine the diversity of the participants in \ref{majumder:turk} we see that the turk data provide data from a very diverse population.
-Moreover it is observed in XXX that diversity is not much important for lineups as the human factors do not have any practical impact on the probability of correctly identifying the data plot in the lineup.
+While selection bias may influence the results of some experimental study it is not much of an issue for experiment with lineups.
+In terms of demographic factors and geographic location MTurk provides much diversity in the participants as we see in \cite{majumder:socio}.
+Moreover it is observed that the human factors do not have any practical impact on the probability of correctly identifying the data plot in the lineup.
 
- may recruit from a specific geographical location
+% may recruit from a specific geographical location
 
-Setting up qualification may allow certain workers to do the task
+%Setting up qualification may allow certain workers to do the task
 
-Payment amount may affect the duration of the experiment which may avoid diversity in the geographical locations.
+%Payment amount may affect the duration of the experiment which may avoid diversity in the geographical locations.
 

### 2013-06-22 paper_turk.tex
introduction reviewed

@@
 The web site is now hosted on the Iowa State University public domain and has been in use for multiple experiments \citep{majumder:turk}.
-It turns out to be a very efficient way of getting lineups evaluated by online observers.
-Getting results from this web site is very convenient and secure.
+It provides multiple features that makes it convenient to get lineups evaluated by online observers and obtain data in a secure way.
 
@@
 
-There have been some advancements in visual statistical inference since it was first introduced by \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols.
+There have been some advancements in visual statistical inference since it was first introduced by \cite{buja:2009}.
+They  proposed lineup protocol that allows testing the significance of findings using statistical graphics.
 In visual statistical inference the test statistics is a plot of the observed data.
 This plot is placed randomly in a layout of plots called lineup.
-The rest of the plots in the lineups are generated from the model specified by the null hypothesis.
+The rest of the plots, called null plots, in the lineups are generated from the model specified by the null hypothesis.
 A human observer is asked to evaluate the lineup.
-If the observer detects the actual plot in the lineup, the null hypothesis is rejected.
+If the observer can detect the actual plot in the lineup, the null hypothesis is rejected.
 
@@
 Can you find which of these plots show the steepest slope?
-The rest of the plots or the null plots are generated based on the hypothesis that the slope is zero.
-If the observed scatterplot is detected that indicates that observed plot is different from null plot and hence the null hypothesis is rejected.
+The null plots are generated based on the hypothesis that the slope is zero.
+If the observed scatterplot is detected that indicates that observed plot is different from the null plots and hence the null hypothesis is rejected.
 
@@
 
-\cite{majumder:2013}  further developed visual inference by refining the terminologies and providing the methods of obtaining the power.
+\cite{majumder:2013}  further developed visual inference by refining the terminologies and providing the methods of obtaining the power of the visual test.
 it is revealed that visual test power can be as good as the best available conventional test and in some scenarios even better.
@@
 
-These developments open up a whole new area of statistical research where lineups need to be evaluated by human observer.
+These developments open up a new area of statistical research where lineups need to be evaluated by human observer.
 For small scale or day to day research it is possible to have people around to get the lineups evaluated.
@@
 \cite{niladri:2012} used lineup protocol in practical applications.
-Other reasons to evaluate lineups are to present the results of the conventional test with visual tools such as lineup.
+Other reasons to evaluate lineups may be to present the results of the conventional test with visual tools such as lineup.
 
@@
 The power of visual test can be obtained theoretically under some assumptions on individual behavior which was evident from experimental studies \citep{majumder:2013}.
-In general it is hard to obtain explicitly with a mathematical formula since it is very much dependent on individual observation.
-One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation.
+In general it is hard to obtain explicitly with a mathematical formula since it is very much dependent on human observation.
+One approach to estimate the power is to recruit observers to evaluate lineups generated with some known effect sizes.
+The proportion of correct evaluation can be used as an estimate of the power for that effect size.
 Individual differences in the abilities of correct evaluations of lineup were observed.
-But Observer's education levels do not seem to have significant effect on performances.
-Thus it is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.
+Thus it is desirable to get observers as diverse as possible.
+
+%without being much concerned about the observers' formal training about statistical graphics.
 
@@
 Cost, time, data qualities and convenience are some of the issues that need to be dealt with.
-Fortunately, we can use the services of Amazon Mechanical Turk web site for this.
+Fortunately, we can use the services of Amazon Mechanical Turk web site for this which is discussed in the following section.
 
@@
 
-\cite{turk} Mechanical Turk  or MTurk is an online work place where people from around the world can perform some tasks and get paid.
-Usually tasks are very simple and no specialized training is required.
+\cite{turk} Mechanical Turk  or MTurk is an online work place where people from around the world can perform tasks and get paid.
+Usually tasks are very simple and no specialized training is necessary.
 Being a human is the main requirement.
 Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters' need.
-The tasks are designed such that it does not take much time to complete.
+The tasks are designed to be done in a very short time.
 Humans are still better than computers in performing these types of tasks.
 The the amount of money paid for each task is very small as well.
-Figure~\ref{fig:amazon_task} shows an MTurk task where an observer is asked to select from some given options based on a picture.
+Figure~\ref{fig:amazon_task} shows an MTurk task where an observer is asked to select an option based on a picture.
 
@@
 
-It is very fast, cheap and reliable to recruit people from MTurk.
+It is very cheap and reliable to recruit people from MTurk and the results can be obtained very fast.
 It allows distributing works to the thousands of workers around the world.
-Thats why it is getting very popular among the researchers who perform human subject experiment.
 The another benefit is that a very diverse pool of subjects can be recruited which is otherwise very hard to obtain for a study.
@@
 
+%It is also getting very popular among the researchers who perform human subject experiment.
+
 Because of its convenience it is getting popular for scientific research study as well.
@@
 
+The simplicity of the MTurk task is the main factor for its popularity.
 Figure \ref{fig:amazon_task} shows how simple an MTurk task could be.
@@
 Moreover, It is convenient if the lineup is clickable so that selection of plot can be made by mouse click.
-All these are done by creating a web application.
-The following section discusses this in details.
+To create an MTurk task that has all these flexibilities, a web application needs to be created.
+The following section discusses how the system would work.
 
@@
 
-There are two options to run the web application; one is to run it inside MTurk system using their API and the other is to develop a new web site.
+Once a web application is created, there are two options to run it; one is to run it inside MTurk system using their API and the other is to develop a new web site separate from MTurk.
 For additional control we picked the second option and planned to separate this application from MTurk system and designed our own web site to run the application.
@@
 
-MTurk will provide workers who are used to doing simple task.
+MTurk provides workers who usually do the simple tasks available for them.
 Thus, for lineups to be evaluated a simple task needs to be created through MTurk.
-But People who need to make statistical decision based on lineup will need a system that can provide an easy solution to this challenge.
+This may be a challenge for the researchers who want to make statistical decisions based on lineups or need to study the power of visual tests.
+They need a system that can provide an easy solution to this challenge while giving them flexibilities how they want to present the lineups.
 This paper provides a complete solution to this.
-This paper is organized the way a researcher may work with lineup and like to get feedback data from the observer.
-Section \ref{sec:turk_exp} presents the details description of an experiment with lineups and things to consider before a turk task.
+It is organized the way a researcher may work with the experiments related to lineups and like to get feedback data from the observer.
+Section \ref{sec:turk_exp} presents the detailed description of an experiment with lineups and things to consider while creating a turk task.
 Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not be possible through MTurk.
@@
 
-To prevent missing information and invalid input JavaScripts are used.
+To prevent missing information and invalid input client side controlled is applied using JavaScripts.
 Most of the cases options or combo boxes are used instead of free text boxes to avoid invalid input.
@@
 
-\section{Turk Data Quality} \label{sec:turk_data}
+\section{Turk Experiment Data} \label{sec:turk_data}
 
-In this section we intend to analyze the performance of the experiments we did using Amazon Mechanical turk.
-We have feed back data for the similar plots from both turk workers as well as from the people who regularly participates in the graphics group meeting of our department.
-We consider later participants as more knowledgeable and trained in seeing pattern in statistical plots.
-We can use these data to evaluate the performance of the general participants from around the world.
+We have performed 10 different experiments using the web application described in Section~\ref{sec:web_application}.
+Table~\ref{tbl:mturk} presents the tasks and payment details of all the 10 experiments.
+Experiment 1 was the first experiment and the largest number of tasks were rejected in that experiment.
+But this experiment provides valuable information about how to modify the web site to avoid invalid input and missing information.
+Thus in the later experiments we did not see a lot of tasks to get rejected.
 
@@
 \centering
-\scalebox{0.9}{
+\scalebox{0.85}{
 \begin{tabular}{rlrrrrrrr}
@@
 
+The hourly payment rates shown in Table~\ref{tbl:mturk} are based on the time periods beginning from the times the tasks were accepted by the worker to the time they were submitted to the MTurk system.
+It is different from the time taken to actually evaluate the lineups.
+Since in between the workers need to go to the web application, get the codes after they finish the tasks and finally put the code to MTurk system.
+The pay rate is almost similar for all the experiment except for experiment 2.
+The payment was decided based on the MTurk standard of \$6 per hour and we can see that for experiment 2.
+Based on the experiment 1 and 2, they payment for each task was fixed to \$1, but in practice, it appears to be much less than that.
+It is because, workers spent long time in between lineups.
+
+%In this section we intend to analyze the performance of the experiments we did using Amazon Mechanical turk.
+We have feed back data for the similar plots from both turk workers as well as from the people who regularly participates in the graphics group meeting of our department.
+We consider later participants as more knowledgeable and trained in seeing pattern in statistical plots.
+We can use these data to evaluate the performance of the general participants from around the world.
+
+The duration of an experiment to finish depends on the time it was posted and the number of interested workers available on that time.
+It also depends on how attractive the experiment is in terms of appearance and payment.
+Even though the payment was similar for all the experiments, ee observed some experiments were finished much faster than others.
+Experiment 8 took long time to finish which is about 77 hours for 100 tasks while experiment 7 took only 4.86 hours to finish 100 task.
+
+Figure~\ref{fig:task_duration} shows the comparative durations of time for 100 tasks in each of the experiment.
+Even though experiment 8 (sine illusion) took longer to finish it got the least number of rejected tasks.
+
 \begin{figure}[htbp] 
@@
 There may be some tasks for which payment is provided but yet the tasks may need to be excluded from the study.
-Some suggestion about data cleaning based on experimental evidence.
-What to expect from turk data.
+It is because there may be some participants who did not put in a best effort to identify the data plot in the lineup, but just randomly picked a plot to maximize their 'winnings'.
+We present following six suggestions about cleaning data from turk experiments where each worker evaluates multiple lineups.
 
-\subsection{Diversity in the Data} Demographics, geographical locations, academic diversity
+\begin{enumerate}
+\item {\bf include all participants} and their evaluations
+\item exclude all participants' evaluations, who did {\bf not} share their {\bf demographic information} (age, gender education level -- all three pieces of information are either missing or all present).
+\item exclude participants' records, if {\bf none of the evaluations}  correctly identified the data plot -- every participant was shown a range of `easy' lineups.
+\item include participants' records, if   {\bf at least 20 percent} of the evaluations are {\bf correct}  -- based on ten evaluations per participants, two correct evaluations are significant evidence against a person just guessing
+\item include participants' records, if at least {\bf 50\% of all very easy lineups are correct} 
+\item use easy lineups as {\bf reference charts}: sample one easy lineup from a person's records.
+If that lineup is evaluated {\bf correctly}, include all (other) lineups of that person, otherwise exclude all lineup evaluations by this participant.
+\end{enumerate}
+
+These screening criteria may be applied based on the specific design of the study and experimental evidence. For example \cite{majumder:2013} used criteria 6 to clean the data.
+
+%Amazon Mechanical Turk data suffers from the problem that some participants are trying to 'game' the system, because they are being paid for their efforts, not much by the standards of the US minimum wage, but enough to encourage honest efforts.
+in our situation, these are participants who did not put in a best effort to identify the data plot, but just randomly picked a plot to maximize their 'winnings'.
+In order to avoid using those results, we are comparing six different screening methods for excluded participants from the data analysis.
+There are six suggested approach to clean the data.
+They are
+
+%\subsection{Diversity in the Data} Demographics, geographical locations, academic diversity
 

### 2013-06-22 paper_turk.tex
experiment design

@@
 In that case we do not need to design a simulation experiment.
-This section will be useful when a simulation experiment is needed to examine different plot types as test statistics and compare the power of visual test \citep{majumder:2013}.
-To examine the effectiveness of certain plots in displaying the data one might want to design an experiment with lineup \citep{heike:2012}.
+This section will be useful when a simulation experiment is needed to examine different visual test statistics and compare the power \citep{majumder:2013}.
+To examine the effectiveness of certain plots in displaying the data one may want to design an experiment with lineup \citep{heike:2012}.
 In any cases, two major considerations are choice of parameters to simulate lineup and number of people needed to evaluate a lineup.
@@
 This data can be considered as the observed data.
-A lineup can be created by placing this observed data plot on a lineup where rest of the data plots come from the model specified by the null model \citep{majumder:2013}.
+A lineup can be created by placing this observed data plot in a layout where rest of the data plots come from the model specified by the null model \citep{majumder:2013}.
 
@@
 We need to make sure that the simulated data does not come from this extreme end.
-On top of that we want some replication so that this extreme effect can be controlled at some level.
+Additionally, we want some replications so that this extreme effect can be controlled at some level.
 For this example we intend to pick three replications.
@@
 Notice that if we like to have three replications of plots, we will have observed data sets with smaller $p$-values as the distribution is highly right skewed as well as the 33th and 66th percentiles of p-values are 0.0101 and 0.077 respectively.
-So, another option may be to take the mid points of those quantile ranges and pick the data sets that have those p-values.
+So, another option may be to take the mid points of those quantile ranges and pick the data sets that produce those p-values.
 \\
@@
 
-All of these three approaches discussed above has some problems.
+All of these three approaches discussed above have some problems.
 Kolmogorov method does not necessarily make sure that estimated parameters are close to the true parameters.
@@
 
-\subsection{Test and Training Lineup} Some lineups should be presented to the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment.
+\subsection{Test and Training Lineup} Some lineups should be displayed for the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment.
 It is important to setup this properly.
@@
 The purpose is to give them an idea how the actual task would look like.
+The worker may or may not like to try the training lineups.
 
@@
 
-Other things that needs to be considered include number of training lineups, how the lineups should be shown.
+Other things that needs to be considered include number of training lineups and how the lineups should be shown.
 Training should not take much longer.
@@
 The training lineups should be easy to evaluate and they should be randomly selected from a very small number of lineups.
-That may produce repetition which may help the MTurk workers to retest their skill on the lineup the might have a wrong selection before.
+That may produce repetition which may help the MTurk workers to retest their skills on the lineup they might have a wrong selection before.
 
@@
 It is helpful if some example lineups are presented with the experimental description.
-Example lineup on the homepage should be of size three or four so that more than one lineup can be placed on the homepage.
+Example lineup does not have to be of the size similar to the actual lineup.
+it can be of size three or four so that more than one lineup can be placed on a page for demonstration of the task.
 This helps the worker decide whether they are willing to participate the experiment at all.
 
-\subsection{Plan for a Turk Task} \label{sec:task_plan} To make a good use of MTurk crowd source, it is important to split any big project into small pieces or Task.
+\subsection{Plan for a Turk Task} \label{sec:task_plan} To make a good use of MTurk crowd source, it is important to split any big project into small pieces or Tasks.
 To present each task for the workers to do, a Human Intelligence Task or HIT needs to be designed which includes crisp and clear instructions of the task, descriptions of specific input and output desired and payment information.
@@
 
-\item {\bf Data input:} For lineup experiments data input means mainly the lineups that are going to be presented for evaluations.
+\item {\bf Data input:} For lineup experiments input data  mainly refer to the lineups that are going to be presented for evaluations.
 Lineups may be presented in some sequence or completely at random.
@@
 For different experimental needs this input may be different.
-For example, one may decide to let the worker know if each evaluation made is correct or wrong right after the feedback.
+For example, one may decide to let the worker know if each evaluation made is correct or wrong after the feedback has been submitted.
 This is an input for the worker.
 
-\item {\bf Data output:} This means the data collected from the MTurk workers.
+\item {\bf Data output:} This means the data to be collected from the MTurk workers.
 That includes mainly the response on lineup question.

### 2013-06-22 paper_turk.tex
web application reviewed

@@
 This feature can be opted out easily if not necessary.
-The worker has to provide their turk ID and for next evaluation they don't have to type it again.
+The workers have to provide their turk ID and for next evaluation they don't have to type it again.
 This allows the worker give feedback using only mouse click.
@@
 
-The homepage of the web displays detailed explanation on how they can perform the task of evaluating the lineups.
+The homepage of the web displays detailed explanation on how one can perform the task of evaluating the lineups.
 Several examples with possible answers are provided.
@@
 It is also possible to screen out workers as needed.
-For example, none will be interested to recruit people who have bad reputation of getting the work done properly.
+For example, none will be interested to recruit people who have a very bad reputation.
 This information can be obtained from each worker's previous work history of total number of accepted task out of total number of submitted task.
-The web application we developed is for presenting lineups in a way required by the experiment design and collecting data.
+The web application we developed is for presenting lineups in a flexible way the researcher may want  as per the experimental design and collecting data.
 To get people to the web application we need to design a turk task in MTurk system.

### 2013-06-22 paper_turk.tex
last review before submission

@@
    \includegraphics[width=6.5in]{plot_turk2_100_450_12_3.png} 
-   \caption{A lineup of 20 scatter plots with least square line overlaid. Which of these plots shows the steepest slope?.}
+   \caption{A lineup of 20 scatter plots with least square line overlaid. Which of these plots shows the steepest slope? Answer to this question can be found at the end of conclusion.}
    \label{fig:lineup_turk}
@@
 
-\item The number of worker to recruit has to be provided so that the turk task is live until specific number of people do the task.
-This is related to the sample size we intend to collect on each lineup.
+\item The number of worker to recruit has to be provided so that the turk task remain open until specific number of people do the task.
+This is related to the sample size of the data we intend to collect on each lineup.
 
 \item Time allowed to finish each task has to be specified.
-Once a specific time period is set up the task will be expired after that time and the worker can't be submit it anymore.
-The worker has to finish the task by that time period.
+Once a specific time period is set up the task will be expired after that time and the worker can't submit it anymore.
+The worker has to finish the task by that time period once he or she agrees to do the task.
 
@@
 This duration is important as each payment has to be finalized by this time period.
-Otherwise, all the workers will be paid automatically after this time period no matter if the the task is accepted or rejected.
+Otherwise, all the workers will be paid automatically after this time period no matter whether the the task is accepted or rejected.
 Some times it is helpful to set up a longer duration and see how long it takes before all the tasks get completed.
@@
 Since MTurk task are very simple and payment amount is very small the general convention is to pay every worker who submitted the task properly as instructed.
-The task should not be rejected based on the quality of work unless it prominently demonstrates that the task was not performed properly and irrelevant or garbage data were provided.
+The task should not be rejected based on the quality of work unless it clearly demonstrates that the task was not performed properly and irrelevant or garbage data were provided.
 It is very unusual to get garbage data from MTurk workers since they are well aware that this conduct may harm their reputation as a worker.
 So, proper caution needs to be taken while rejecting a task.
-Some times may happen that the workers provided crap data unintentionally.
+Some times it may happen that the workers provided invalid data unintentionally.
 In that case we recommend to accept the task and pay for trying the task.
@@
 For example if there are 3 easy lineups and none of them were correctly evaluated it is most likely that the feedbacks were provided randomly.
-Some times it may happen that out of 10 lineups 3 were correctly evaluated but all the three easy lineups were wrongly evaluated.
+Some times it may happen that out of 10 lineups 3 difficult lineups were correctly evaluated but all the three easy lineups were wrongly evaluated.
 In that case the payment should be made since it is very unlikely that out of 10 lineups a total of 3 lineups would be correctly evaluated by just random response.
@@
 
-\subsection{Managing Worker} Accepting the task and processing the payment in a timely manner may make a good impression for the task they just did.
+\subsection{Managing Worker} Accepting the task and processing the payment in a timely manner may make a good impression about the task and the recruiter.
 This is helpful for the recruiter's reputation so that in future the recruiter can get the job done faster.
@@
 It also depends on how attractive the experiment is in terms of appearance and payment.
-Even though the payment was similar for all the experiments, ee observed some experiments were finished much faster than others.
+Even though the payment was similar for all the experiments, we observed some experiments were finished much faster than others.
 Experiment 8 took long time to finish which is about 77 hours for 100 tasks while experiment 7 took only 4.86 hours to finish 100 task.
@@
 While selection bias may influence the results of some experimental study it is not much of an issue for experiment with lineups.
-In terms of demographic factors and geographic location MTurk provides much diversity in the participants as we see in \cite{majumder:socio}.
+In terms of demographic factors and geographic location MTurk provides much diversity in the participants as studied by \cite{majumder:socio}.
 Moreover it is observed that the human factors do not have any practical impact on the probability of correctly identifying the data plot in the lineup.
@@
 This also made the multiple plot selection from a lineup easier and convenient.
-Multiple online experiments are done using this web application and result suggests that the application worked as planned.
+The web site is used for multiple online experiments.
 
@@
 We also intend to set up a web application for public use where researcher can put their lineup for online evaluation.
-The observer can be recruited from MTurk or any other source including local lab participants.
+The observer can be recruited from MTurk or any other sources including local lab participants.
+
+\paragraph{Answer to the question in Figure~\ref{fig:lineup_turk} is 2.}
 

### 2013-07-06 paper_turk.tex
reviwerd upto the end of section 2.3 (sample size estimatin)

@@
 The web site is now hosted on the Iowa State University public domain and has been in use for multiple experiments \citep{majumder:turk}.
-It provides multiple features that makes it convenient to get lineups evaluated by online observers and obtain data in a secure way.
+It provides multiple features that make it convenient to get lineups evaluated by online observers and obtain data in a secure way.
 
@@
 
-There have been some advancements in visual statistical inference since it was first introduced by \cite{buja:2009}.
+There have been some advancements in visual statistical inference since the concept was first introduced by \cite{buja:2009}.
 They  proposed lineup protocol that allows testing the significance of findings using statistical graphics.
@@
 This plot is placed randomly in a layout of plots called lineup.
-The rest of the plots, called null plots, in the lineups are generated from the model specified by the null hypothesis.
+The rest of the plots, called null plots, in the lineups are generated using the data simulated from the model specified by the null hypothesis.
 A human observer is asked to evaluate the lineup.
@@
 The null plots are generated based on the hypothesis that the slope is zero.
-If the observed scatterplot is detected that indicates that observed plot is different from the null plots and hence the null hypothesis is rejected.
+If the observed scatterplot is detected, it indicates that observed plot is different from the null plots and hence provides evidence against the null hypothesis.
 
@@
 
-\cite{majumder:2013}  further developed visual inference by refining the terminologies and providing the methods of obtaining the power of the visual test.
-it is revealed that visual test power can be as good as the best available conventional test and in some scenarios even better.
+\cite{majumder:2013}  further developed visual statistical inference by refining the terminologies, presenting the ways to compute $p$-values associated with the visual test and providing the methods of obtaining the power of the test.
+It is revealed that the power of visual test  can be as good as that of the best available conventional test and in some scenarios even better.
 This work establishes the validity of lineup protocol to be used as a tool for statistical testing.
-In the situations where no conventional test exists, visual inference can be the only inferential procedure without compromising a lot in power because of its non-parametric nature and few assumptions.
+In the situations where no conventional test exists, visual inference can be the only inferential procedure that does not compromise a lot on power because of its non-parametric nature and few assumptions.
 
@@
 We may need to show a random sample of lineups from a pool of many lineups automatically.
-The questions the observer would answer while examining the lineup can be different based on different lineup.
-Moreover, It is convenient if the lineup is clickable so that selection of plot can be made by mouse click.
+The questions the observer would answer while examining the lineup can be different based on different lineups.
+Moreover, It is convenient if the lineup is clickable so that selection of plot can be made by the mouse click.
 To create an MTurk task that has all these flexibilities, a web application needs to be created.
@@
 For additional control we picked the second option and planned to separate this application from MTurk system and designed our own web site to run the application.
-It enables to display the lineups to the observers with a lot of flexibilities.
+It enables us to display the lineups to the observers with a lot of flexibilities.
 As an added benefit the data can be directly saved in a local database server instead of getting it from MTurk.
@@
 Figure \ref{fig:turk_work_flow} shows how the plan works.
-First an MTurk task is created for the workers to see and decide whether they want to do the task based on the parameters like payment amount, estimated time the task may take to finish, how hard the task seems to be etc.
+First an MTurk task is created for the workers to review and decide whether they want to do the task based on the parameters like payment amount, estimated time the task may take to finish and how hard the task seems to be etc.
 Workers are informed that the task has to be done outside the MTurk system from another web site.
 Once the workers accept the task they are redirected to our web site where multiple lineups are shown for evaluations.
-After the required number of evaluations has been received, a code is generated which the workers has to submit back in MTurk system to complete the task.
+After the required number of evaluations has been received, a code is generated which the workers need to submit back in MTurk system to complete the task.
 The code is matched with the code in our database to process payment through MTurk system.
@@
 
-If a lineup is created from actual observed data, the web application presented in Section \ref{sec:web_application} can be used to evaluate it.
+If a lineup is created from the actual observed data, the web application presented in Section \ref{sec:web_application} can be used to get it evaluated.
 In that case we do not need to design a simulation experiment.
@@
 To examine the effectiveness of certain plots in displaying the data one may want to design an experiment with lineup \citep{heike:2012}.
-In any cases, two major considerations are choice of parameters to simulate lineup and number of people needed to evaluate a lineup.
+In any cases, the two major considerations are the choice of parameters to simulate lineups and number of people needed to evaluate a lineup.
 
 \subsection{Selecting Parameter to Simulate Lineup} \label{sec:parameter_selection} In any experimental design we need to have some control.
-For a simulation experiment with lineup, this refers to the parameter related to a lineup.
+For a simulation experiment with lineup, this refers to the parameters related to a lineup.
 This depends on what the purpose of the experiment is.
@@
 In addition to the hypothesized parameter of interest, other parameters that may need to be fixed include sample sizes, variability in the data, error structure etc.
-These parameters produces the effect sizes and are responsible for any detectable signal in the lineup.
+These parameters produce the effect sizes and are responsible for any detectable signal in the lineup.
 Thus for a simulation study a range of effects sizes need to be considered.
@@
 
-\subsection{Procedure to Simulate Data Plot} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from model of interest for pre-specified parameters.
+\subsection{Procedure to Simulate Data Plot} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from the model of interest with pre-specified parameters.
 We call this data set observed data.
-Every time we do that we get a new set of observed data which may produce a parameter very different than the actual parameter specified to generate the data.
-But it is important to have a observed data closely representing the parameters chosen since other null plots will be compared to this data plot in a lineup.
+Every time we do that we get a new set of observed data which may produce an estimated parameter very different than the actual parameter specified to generate the data.
+But it is important to have an observed data closely representing the parameters chosen since other null plots will be compared to this data plot in a lineup.
 One solution to this is to take some replications of lineups for the same effect size.
@@
 While the effect of the natural variability of the observed data set can be controlled by taking the replication of few samples, it is desirable to study whether we can reduce this variability further to some extent.
-For this we pick the example of a simple linear regression model and examines how the data plot can be generated that best represent the specified parameter.
+For this we pick the example of a simple linear regression model and examines how the data plot can be generated that best represents the specified parameter.
 Consider a linear regression model
@@
 
-{\bf Quantiles of $p$-value approach:} For a simulated observed data set we can obtain the $p$-value associated to testing $H_0: \beta=0$.
+{\bf Quantiles of $p$-value approach:} For a simulated observed data set we can obtain the $p$-value associated with testing $H_0: \beta=0$.
 The distribution of $p$-value is uniform under null hypothesis but under alternative it has a right skewed distribution.
@@
        \scalebox{.6}{\includegraphics{dist_pvalue.pdf}}
-       \caption{Distribution of $p$-values for $n$=300, $\beta$=3 and $\sigma$=12.}
+       \caption{Distribution of $p$-values under alternative hypothesis ($H_1: \beta$=3) for sample size $n$=300 and error standard deviation $\sigma$=12.}
        \label{fig:dist_pvalue}
@@
 {\bf Closeness of estimated parameters:} When we simulate a data set from the Model \eqref{eqn:turk_model} and fit the model to the data set again, we do not get the parameters estimates same as what we fixed while simulation.
-For example, we obtained a parameter estimates of 0.5 for true $\beta=3$.
+For example, with a simulated observed data we obtained a parameter estimates of 0.5 for true $\beta=3$.
 We want a data set where the parameter is closed to our fixed slope $\beta=3$.
@@
 \subsection{Sample size estimation} For any experiment it is important to determine the sample size.
-It is not only related to time and cost of the experiment but also the validity of the results depends on it.
+It is not only related to time and cost of the experiment but also associated with the validity of the results.
 In simulation experiment with lineup the sample size means the number of evaluations per lineup.
@@
 
-One approach to assess number of evaluations that are required for a lineup is to have a prior idea of proportion correct for the that lineup.
-For a given proportion $p$ we want to have margin of error (ME) to be 0.1.
+One approach to assess number of evaluations that are required for a lineup is to have a prior idea of proportion correct responses for the that lineup.
+For a given proportion $p$ we want to have margin of error (ME) to be at most 0.05.
 Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$
@@
 This can be assumed to be the power or proportion correct for that lineup.
-Other ways of having an estimate of sample size can be very specific to the problem of interest and should be dealt with the requirement of the problem.
+Other ways of having an estimate of sample size can be very specific to the problem of interest and should be computed as required by the specific problem.
 

### 2013-07-22 paper_turk.tex
reviewed upto section 3 (web application)

@@
 
-\subsection{Test and Training Lineup} Some lineups should be displayed for the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment.
+\subsection{Test and Training Lineup} It is desirable that some lineups be displayed to the MTurk workers so that they can become familiar with the experimental environment before they participate the actual experiment.
 It is important to setup this properly.
-The training lineups should be easy and feedback should be provided right after the response is received.
+These training lineups should be easy and feedback should be provided right after the response is received.
 The purpose is to give them an idea how the actual task would look like.
-The worker may or may not like to try the training lineups.
+The workers may or may not opt for trying the training lineups.
 
-The another option is to make this training mandatory to participate the experiment.
-The MTurk worker should have certain proportion of correct responses on these training lineups to allow them to participate.
+Another option is to make this training mandatory to participate the experiment.
+The MTurk workers should have certain proportion of correct responses on these training lineups to be allowed to participate.
 This is often practiced in MTurk task and the workers are very familiar with this approach.
@@
 
-Other things that needs to be considered include number of training lineups and how the lineups should be shown.
+Other things that need to be considered include number of training lineups and how the lineups should be shown.
 Training should not take much longer.
 Two or three lineups can provide enough training.
-The training lineups should be easy to evaluate and they should be randomly selected from a very small number of lineups.
+The training lineups can be randomly selected from a very small number of lineups.
 That may produce repetition which may help the MTurk workers to retest their skills on the lineup they might have a wrong selection before.
@@
 For this we plan to have a consent form which the MTurk workers have to agree before participating the experiment.
-The consent form is approved by IRB.
+The consent form needs to be approved by IRB.
 
@@
 
-\item {\bf Data input:} For lineup experiments input data  mainly refer to the lineups that are going to be presented for evaluations.
+\item {\bf Data input:} For lineup experiments input data mainly refer to the information about lineups that are going to be presented for evaluations.
 Lineups may be presented in some sequence or completely at random.
@@
 But some times it may be more or less depending on the task type.
-For some easy tasks it may take longer time which will reduce the pay rate by hour.
+For some easy tasks it may require longer time to evaluate reducing the pay rate by hour.
 Other tasks which are difficult but can be done very fast will have a increase payment rate.

### 2013-07-22 paper_turk.tex
upto section 4 (managing turk task)

@@
 Section \ref{sec:turk_exp} presents the detailed description of an experiment with lineups and things to consider while creating a turk task.
-Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not be possible through MTurk.
+Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not be possible through MTurk system.
 Section \ref{sec:turk_task} describes how to create an MTurk task, mange workers and process payments.
@@
 A web site is developed to get lineups evaluated by human observers \citep{majumder:turk}.
-It provides all the features needed for a simulation experiment with lineups but yet remains simple for the online workers.
+It provides all the features needed for a simulation experiment with lineups but yet remains simple enough for the online workers to provide feedbacks.
 This section describes the technical details of the site.
@@
 The web application is built using server side scripting language PHP embedded in HTML.
-JavaScript is used to control the client side work flow such as preventing missing information, showing messages etc.
+JavaScript is used to control the client side work flow such as preventing missing information, showing instructional messages etc.
 MySQL database is used to store data for dynamic presentation of lineup and recording observer feedbacks.
-The application also records the ip address of the observer's machine and the time of each display of lineup and its evaluation.
+The application also records the ip address of the observer's machine and the times at which each lineup is displayed and evaluation is received.
 
@@
 If needed multiple selection of plots can be allowed, order of selection and deselection can be recorded with time taken for each action.
-Thats what we meant by saying it is complex in design.
+That is what we meant by saying it is complex in design.
 
@@
 This works as an incentive for the worker to work more enthusiastically.
-To ensure the payment, the turk workers have to provide some information using this form.}
+To ensure the payment, the turk workers have to provide their demographic information using this form.}
        \label{fig:turk_web_feedback}
@@
 These lineups are randomly selected from a pool of lineups designed for evaluations.
-The algorithm for how the lineups should be selected to show and what would be the order of display is implemented in the form shown in Figure \ref{fig:turk_web}.
+The algorithm of how the lineups should be selected to show and what would be the order of display is implemented in the form shown in Figure \ref{fig:turk_web}.
 Also there is a check for invalid or missing information which is implemented using javascript.
@@
 In all other tables the first field names shown in Figure~\ref{fig:turk_database_design} are the primary keys.
-For the implementation of the web application we used MySQL database located on a local server.
+For the implementation of the web application we used MySQL database located on a local server securely accessible from public locations.
 
@@
 
-To prevent missing information and invalid input client side controlled is applied using JavaScripts.
+To prevent missing information and invalid input client side control is applied using JavaScripts.
 Most of the cases options or combo boxes are used instead of free text boxes to avoid invalid input.

### 2013-07-22 paper_turk.tex
upto accepting and rejecting (4.2)

@@
 \section{Managing Turk Task}\label{sec:turk_task} \cite{turk} Mechanical Turk website provides various features that are helpful to maintain and organize the task and manage the workers.
-Creating, posting, accepting or rejecting tasks and processing payment are done from the MTurk system.
+Creating, posting, accepting or rejecting tasks and processing payment can be done from the MTurk system.
 It is also possible to screen out workers as needed.
@@
 
-\item The number of worker to recruit has to be provided so that the turk task remain open until specific number of people do the task.
+\item The number of workers to recruit has to be provided so that the turk task remains open until some specific number of people do the task.
 This is related to the sample size of the data we intend to collect on each lineup.

### 2013-07-23 paper_turk.tex
finished review

@@
 
-\item It is recommended to reject the task if it is not submitted as requirement.
-Some times this may produce dispute and the workers may become angry and demand payment.
+\item It is recommended to reject the task if it is not submitted as required.
+Some times this may produce dispute and the workers may become upset and still demand payment.
 We recommend to be strict to the decision and for any further administrative control there is an option to block the worker if necessary.
@@
 Experiment 1 was the first experiment and the largest number of tasks were rejected in that experiment.
-But this experiment provides valuable information about how to modify the web site to avoid invalid input and missing information.
+But this experiment provides valuable information about how to upgrade the web site to avoid invalid input and missing information.
 Thus in the later experiments we did not see a lot of tasks to get rejected.
@@
 The pay rate is almost similar for all the experiment except for experiment 2.
-The payment was decided based on the MTurk standard of \$6 per hour and we can see that for experiment 2.
-Based on the experiment 1 and 2, they payment for each task was fixed to \$1, but in practice, it appears to be much less than that.
+The payment amount was decided based on the MTurk standard of \$6 per hour and we can see that for experiment 2.
+Based on the experiment 1 and 2, the payment for each task was fixed to \$1, but in practice, it appears to be much less than that.
 It is because, workers spent long time in between lineups.
@@
 
-Figure~\ref{fig:task_duration} shows the comparative durations of time for 100 tasks in each of the experiment.
+Figure~\ref{fig:task_duration} shows the comparative durations of time for 100 tasks in each of the experiments.
 Even though experiment 8 (sine illusion) took longer to finish it got the least number of rejected tasks.
@@
 Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot.
-This also made the multiple plot selection from a lineup easier and convenient.
+This also made the multiple plot selections from a lineup easier and convenient.
 The web site is used for multiple online experiments.
@@
 
-The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their need and run the MTurk experiments as part of their research that involves lineups.
-This will also help lineup protocol to be used frequently since it will provide an ease of its use in making inferential decisions.
+The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their needs and run the MTurk experiments as part of their research that involves lineups.
+This will also help lineup protocol to be used frequently in making inferential decisions since it will provide the required flexibilities and convenience.
 
